---
title: "All Plotting functions"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
knitr::opts_chunk$set(
                      comment = "#>",
                      message=FALSE, 
                      warning=FALSE,
                      #fig.retina = 2, 
                      fig.width = 8,
                      fig.asp = 0.618,
                     # fig.align = "center",
                     # dev = "ragg_png",
                      out.width = "90%"
)
unlink(".RData")
library(testthat)
library(ggplot2)
library(tidyverse)
library(scales)
library(unhcrthemes)
# library(extrafont) 
# font_import()
# loadfonts()
# font_install('fontcm')
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```




# Country Questions

## Plot Population type per year

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-plot_ctr_population_type_per_year}
#' Graph of population type per year
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#'
#' @export
#'
#'

plot_ctr_population_type_per_year <- function(year = 2022,
                                              lag = 5, 
                                     country_asylum_iso3c = country_asylum_iso3c,
                                     pop_type = Population.type
                                     ) {
  



  cols_poptype <- c("Asylum seekers" = "#18375F",
                    "Refugees" = "#0072BC",
                    #"Venezuelans Displaced Abroad" = "#EF4A60", 
                    "Other people in need of international protection" = "#EF4A60", 
                    "Others of Concern to UNHCR" = "#999999",
                    "Internally displaced persons" = "#00B398",
                    "Stateless Persons" = "#E1CC0D")
  
  
  df <- unhcrdatapackage::end_year_population_totals_long  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year >= ( year - lag),  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
                  Population.type %in% pop_type #### Parameter
    )  |>  
    group_by(Year, CountryAsylumName, Population.type.label)  |> 
    summarise(Value = sum(Value, na.rm = TRUE)) |> 
    ungroup()
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()
  
  year_breaks <- diff(range(df$Year)) + 1 
  
  p <- ggplot(df) +
    geom_col(aes(x = Year, y = Value, fill = Population.type.label),
             width = 0.7) +
    geom_text(aes(x = Year, 
                  y = Value, 
                  color = Population.type.label, 
                  label = label_number( accuracy = 1,
                                   scale_cut = cut_short_scale())(Value)),
              position = position_stack(vjust = 0.5),
              show.legend = FALSE,
              size = 5) +
    scale_color_manual(values = c("#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF")) +
    scale_fill_manual(values = cols_poptype,
                      drop = TRUE,
                      limits = force) +
    scale_x_continuous(breaks = scales::breaks_pretty(n = year_breaks)) +
    scale_y_continuous(expand = expansion(c(0, 0.1))) +
    labs(title = paste0(CountryAsylum_name_text, ": Population type per year"), 
         subtitle = "Number of people (thousand)",
         caption = "Source: UNHCR.org/refugee-statistics") +
    theme_unhcr(grid = FALSE, axis = "x", 
                axis_title = FALSE, axis_text = "x",
              font_size = 14) +
    stat_summary(fun = sum, aes(x = Year,
                                y = Value, 
                                label = scales::label_number( accuracy = 1,
                                                       scale_cut = cut_short_scale())(..y..), 
                                group = Year), 
                 geom = "text", size = 5,
                 vjust = -0.5) +
    theme(legend.direction = "vertical",
          legend.key.size = unit(0.8, 'cm'),
          text = element_text(size = 20),
          plot.subtitle=element_text(size=19),
          plot.title = element_text(size=23),
          plot.caption = element_text(size=13))
  
  return(p) # print(p)
  }
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples-plot_ctr_population_type_per_year, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_per_year(year = 2022,
                                              lag = 5,
                         country_asylum_iso3c = "PAN",
                          pop_type = c("REF", 
                                       "ASY", 
                                       "OIP", 
                                       "OOC",
                                       "STA",
                                       "IDP" )
                  )
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-plot_ctr_population_type_per_year}


```



## Plot Main country of origin  in one specific country - Absolute value


```{r function-plot_ctr_population_type_abs}
#' Main country of origin - Absolute value
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY,   OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_population_type_abs <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                       #VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <- 
  unhcrdatapackage::end_year_population_totals  |> 
  filter(CountryAsylumCode != "UKN",
                !is.na(CountryAsylumCode),
                (Year == year | Year == year -1),  #### Parameter
                CountryAsylumCode == country_asylum_iso3c, #### Parameter
  )  |>  
  select(Year, CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
  group_by(Year, CountryAsylumName, CountryOriginName) |>
  filter(!!sym(pop_type) != 0) |>
  mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
  ungroup() |>
  group_by(CountryAsylumName, CountryOriginName) |> 
  arrange(Year) |>
  mutate(diff_pop_type_value = label_percent( accuracy = 1.1,
                                             trim = FALSE) (((pop_type_value-lag(pop_type_value))/lag(pop_type_value)))  ) |> 
  ungroup() |>
  filter(Year == year) |> 
  mutate(
    origin_data_prot = forcats::fct_lump_n(
      f = CountryOriginName,
      n = top_n_countries,  #### Parameter
      w = pop_type_value,
      other_level = 'Other nationalities',
      ties.method = "last"
    )
  ) |>
  mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                            'Other nationalities'),
                diff_pop_type_value = case_when(origin_data_prot == 'Other nationalities' ~ "",
                                                TRUE ~ diff_pop_type_value)) |>
  group_by(CountryAsylumName, diff_pop_type_value, origin_data_prot) |>
  summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
  ungroup() |> 
  arrange(desc(pop_type_value)) |>
  filter(pop_type_value != 0L) |>
  mutate(
    origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
    origin_data_prot =  suppressWarnings(
      case_when(
        origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                         "Other nationalities",
                                                                         after = 0),
        TRUE ~ origin_data_prot
      )
    ),
    perc = label_percent(
      accuracy = 1,
      trim = TRUE
    )(  pop_type_value / sum(pop_type_value))
  )

CountryAsylum_name_text <- df |> 
  distinct(CountryAsylumName) |> 
  pull()


p <-  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                           scale_cut = cut_short_scale())(pop_type_value)
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(pop_type_value)),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  geom_text( # positive diff percentage label
    data = subset(df, with(df, !grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.8,
    vjust = 0.5,
    colour = "grey",
    size = 4
  ) +
  geom_text( # negative diff percentage label
    data = subset(df, with(df, grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.5,
    vjust = 0.5,
    colour = "#0472bc",
    size = 4
  ) +
  geom_text( #increase triangle
    data = subset(df, with(df, !grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9650),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0bb498",
    size = 7
  ) +
  geom_text( #decrease triangle
    data = subset(df, with(df, grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9660),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0472bc",
    size = 7
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = paste0("Top",  top_n_countries, " Countries of Origin"),
                         x = "Number of People",
       caption = "Source: UNHCR.org/refugee-statistics") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
  theme_unhcr(grid = FALSE, axis = "y", 
              axis_title = FALSE, axis_text = "y",
              font_size = 14) +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_abs, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 4,
                    pop_type = "REF"
                    ) 

## Same with 9 top countries and asylum seekers included
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 9,
                    pop_type = "REF"
                    ) 

```

```{r tests-plot_ctr_population_type_abs}

```



## Plot Main country of origin in one specific country - Percentage


```{r function-plot_ctr_population_type_perc}
#' Main country of origin - Percentage
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_population_type_perc <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                      # VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <-  
    unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
    )  |>  
    select(CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
    group_by(CountryAsylumName, CountryOriginName) |>
    filter(!!sym(pop_type) != 0) |>
    mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
    ungroup() |>
    mutate(
      origin_data_prot = forcats::fct_lump_n(
        f = CountryOriginName,
        n = top_n_countries,  #### Parameter
        w = pop_type_value,
        other_level = 'Other nationalities',
        ties.method = "last"
      )
    ) |>
    mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                              'Other nationalities')) |>
    group_by(CountryAsylumName,origin_data_prot) |>
    summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
    ungroup() |> 
    arrange(desc(pop_type_value)) |>
    filter(pop_type_value != 0L) |>
    mutate(
      origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
      origin_data_prot =  suppressWarnings(
        case_when(
          origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                           "Other nationalities",
                                                                           after = 0),
          TRUE ~ origin_data_prot
        )
      ),
      perc = label_percent(
        accuracy = 1,
        trim = FALSE )( pop_type_value / sum(pop_type_value))
    )
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()



p <- 
  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = paste0("Top",  top_n_countries, " Countries of Origin"),
       x = "Percentage",
       caption = "Source: UNHCR.org/refugee-statistics") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
 theme_unhcr(grid = FALSE, axis = "y", 
             axis_title = FALSE, axis_text = "y",
              font_size = 14) +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_perc, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_perc(year = 2021,
                    country_asylum_iso3c = "BRA",
                    top_n_countries = 9,
                    pop_type = "REF"  ) 

plot_ctr_population_type_perc(year = 2021,
                    country_asylum_iso3c = "BRA",
                    top_n_countries = 9,
                    pop_type = "ASY"  ) 
```

```{r tests-plot_ctr_population_type_perc}

```


## Plot Increases and Decreases in Population Groups


```{r function-plot_ctr_diff_in_pop_groups}
#' Increases and Decreases in Population Groups
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer  gather separate spread
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_diff_in_pop_groups <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type
) {



  diff_perc <- function(x){
    x = as.numeric((x - lag(x))/lag(x)) + 0
    
  }
  
  
  df <- unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  (Year == year-1 | Year == year),  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    group_by(Year, CountryAsylumName) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() |> 
    arrange(Year) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName) |> 
    summarise(across(where(is.numeric), 
                                   list(diffabs = diff,
                                        diffperc = diff_perc),
                                   .names = "{.col}_{.fn}")) |> 
    ungroup() |> 
    slice(2) 
  
  df <- replace(df, is.na(df), 0)
  
  df <- df |> 
    tidyr::gather(v, value, REF_diffabs:OIP_diffperc) |> 
    tidyr::separate(v, c("pop_type", "value_type"), sep = "\\_") |> 
    tidyr::spread(key = value_type, value = value) 


  df <- df |>         
    mutate(diffper = label_percent(  accuracy = 1,  trim = FALSE) (diffperc))
  
  
  p <- df |> 
    filter(pop_type %in% pop_type) |>
    ggplot() +
    geom_col(aes(x = pop_type, 
                 y = diffabs,
                 fill = pop_type),
             width = 0.8) +
    scale_fill_manual(
      values = c("ASY" = "#18375F",
                 "REF" = "#0072BC",
                 "OIP" = "#EF4A60", 
                 #"VDA" = "#EF4A60", 
                 "OOC" = "#999999",
                 "IDP" = "#00B398",
                 "STA" = "#E1CC0D"),
      drop= TRUE, limits = force, guide="none"    ) +
    scale_x_discrete(labels= c("ASY" = "Asylum seekers",
                               "REF" = "Refugees",
                               #"VDA" = "Venezuelans Displaced\nAbroad", ,
                               "OIP" = "Other people in need\n of international protection", 
                               "OOC" = "Others of Concern\nto UNHCR",
                               "IDP" = "Internally Displaced\nPersons",
                               "STA" = "Stateless Persons"),
                     drop = TRUE,
                     limits = force) +
    
    ## Adding labels with conditionned positions...
    
    geom_text(  data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(x = pop_type,
          y = diffabs,
          label = label_number(accuracy = 1,
                              scale_cut = cut_short_scale())(diffabs) ),
      vjust = -0.5 , colour = "black", size = 5   ) +
    
    geom_text( data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(  x = pop_type,
            y = diffabs,
            label = diffper   ),
      vjust = -2.0 ,      colour = "black",      size = 5  ) +
    
    geom_text( data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(  x = pop_type,
            y = diffabs,
            label = label_number(accuracy = 1,
                             scale_cut = cut_short_scale())(diffabs) ),
      vjust = 2.7 ,   colour = "white",   size = 5  ) + 
    
    geom_text(  data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(x = pop_type,
          y = diffabs,
          label = diffper   ),
      vjust = 1.2 ,   colour = "white",   size = 5    ) + 
    
    
  geom_text( data = subset(df, diffabs < 0/ 1.5),
    aes(  x = pop_type,
         y = diffabs,
         label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(diffabs)),
    vjust =  1.2, colour = "black", size = 5  ) +
    
  geom_text( data = subset(df, diffabs < 0  / 1.5),
      aes( x = pop_type,
           y = diffabs,
          label = diffper),
      vjust = 2.7,  colour = "black",  size = 5  ) +
    
  geom_hline(yintercept = 0, color = "black") +
  
  labs(title = paste0(df |> 
                      distinct(CountryAsylumName) |> 
                      pull(), 
                      ": Increases and Decreases in Population Groups | ",
                      year-1,
                      "-",
                      year),
         subtitle = "Number of people and percentage",
         caption = "Source: UNHCR.org/refugee-statistics")  + 
   theme_unhcr(grid = FALSE, axis = "x",
                axis_title = FALSE, axis_text = "x",
                font_size = 14) +
   theme(axis.line.x = element_line(color="white"),
          axis.text.x = element_text(size=10))
    
  # geom_text(
  #   data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #   aes(
  #     x = pop_type,
  #     y = diffabs,
  #     label = label_number(accuracy = 1,
  #                                  scale_cut = cut_short_scale())(diffabs)
  #   ),
  #   vjust = -2.0 ,
  #   colour = "white",
  #   size = 5
  # )  +
  #   geom_text(
  #     data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #     aes(
  #       x = pop_type,
  #       y = diffabs,
  #       label = diffper
  #     ),
  #     vjust = -0.5 ,
  #     colour = "white",
  #     size = 5
  #   ) +

  
  return(p) # print(p)
}
```

```{r examples-plot_ctr_diff_in_pop_groups, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_diff_in_pop_groups(year = 2022,
                            country_asylum_iso3c = "ARG",
                            pop_type = c("REF", "ASY")
         )

```

```{r tests-plot_ctr_diff_in_pop_groups}

```




## Plot Main Destination from  one specific country 


```{r function-plot_ctr_destination}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_origin_iso3c Character value with the ISO-3 character code of the Country of Origin
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_destination <- function(year = 2021,
                                 country_origin_iso3c = country_origin_iso3c,
                                 pop_type = pop_type) {



     ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_origin_iso3c ) |> 
               select(ctryname) |> 
                pull()
  
Destination <- left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))  |>
  filter(CountryOriginCode  == country_origin_iso3c  & 
                 Year == year &
                Population.type  %in% as.vector(pop_type)  )  |>  
   mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
         CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
         CountryAsylumName = str_replace(CountryAsylumName, "United States of America", "USA"),
         CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) |> 
   
   group_by( CountryAsylumName) |>
   summarise(DisplacedAcrossBorders = sum(Value) )  |>
   mutate( DisplacedAcrossBordersRound =  ifelse(DisplacedAcrossBorders > 1000, 
                            paste(label_number( accuracy = .1,
                                   scale_cut = cut_short_scale())(DisplacedAcrossBorders)),
                            as.character(DisplacedAcrossBorders) ) ) |>
   arrange(desc(DisplacedAcrossBorders)) |>
   head(10) |>
   filter(DisplacedAcrossBorders >0)

if( nrow(Destination) ==  0 ){
  p <- paste0("There\'s no recorded countries of destination for ",country_origin_iso3c )
  
} else {


#Make plot
p <- ggplot(Destination, aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), ## Reordering country by Value
                           y = DisplacedAcrossBorders)) +
  geom_bar(stat = "identity", 
           position = "identity", 
           fill = "#0072bc") + # here we configure that it will be bar chart+
## Format axis number
  scale_y_continuous( labels = label_number(scale_cut = cut_short_scale())) + 
  
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data = subset(Destination, DisplacedAcrossBorders < max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              #family = "Lato", 
              size = 4   ) +  

  geom_label( data = subset(Destination, DisplacedAcrossBorders >= max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              # family = "Lato", 
              size = 4   ) +   
  # Add `coord_flip()` to make your vertical bars horizontal:
  coord_flip() + 
  
  ## and the chart labels
  labs(title = paste0("What are the main destinations for Forcibly Displaced People?" ),
       
       subtitle = paste0("Top Destination Countries | as of ",year, " for population from ", ctrylabel ), 
       x = "",
       y = "",
       caption = "Source: UNHCR Population Statistics Database.\n Forced Displacement includes Refugees, Asylum Seekers and Other in Need of International Protection.") +
    
  # Style  
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
  
  
  }
  return(p) # print(p)
}

```

```{r examples-plot_ctr_destination, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_destination(year = 2021,
                     country_origin_iso3c = "COL",
                     pop_type = c("REF", "ASY")
         )

```
    
## Plot Tree Map of Categories

```{r function-plot_ctr_treemap}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line 
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_treemap <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {


   ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()

  datatree <-  unhcrdatapackage::end_year_population_totals_long  |> 
    filter(Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName,  Population.type, 
                    Population.type.label, Population.type.label.short) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() 
  
  p <- ggplot(datatree, 
       aes(area = Value, 
           fill = Population.type,
           label = paste0(round(100*Value/sum(Value),1), 
                          "%\n", 
                          Population.type.label))) +
         treemapify::geom_treemap() +
         treemapify::geom_treemap_text(colour = "white",
                           place = "centre", size = 25) +
         scale_fill_manual( values = c(   "IDP" = "#00B398",
                                         # "VDA"="#EF4A60",
                                          "OIP"="#EF4A60",
                                          "ASY" = "#18375F",
                                          "REF" = "#0072BC",
                                          "OOC" ="#8395b9",
                                          "STA"="#E1CC0D")) +
         
      theme_unhcr(font_size = 14,
                  grid = "Y", 
                  axis = "x", 
                  axis_title = "y", 
                  legend = FALSE) +
         theme(legend.position = "none") +
         ## and the chart labels
         labs(title = paste0("Population of Concern in ",  ctrylabel),
              subtitle = paste0("As of ", year, ", a total of ", format(round(sum(datatree$Value), -3),  big.mark=","), " Individuals"),
              x = "",
              y = "",
              caption = "Source: UNHCR.org/refugee-statistics")  

   return(p)
}

```
    
```{r examples-plot_ctr_treemap, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_treemap(year = 2021,
                            country_asylum_iso3c = "USA",
                            pop_type = c("REF", "ASY")
         )

```    
    


## Plot Age Pyramid

```{r function-plot_ctr_pyramid}
#' Population Pyramid
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace str_detect
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_ctr_pyramid <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {

   ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()

  
    demographics1 <- unhcrdatapackage::demographics |>
                     left_join( unhcrdatapackage::reference |> 
                                         select(UNHCRBureau, iso_3),  
                                       by = c("CountryAsylumCode" = "iso_3")) |> 
                     filter(CountryAsylumCode  == country_asylum_iso3c &
                                 Year == year-1 &
                                 Population.type  %in% as.vector(pop_type) ) |>
      
                      mutate ( totGen = FemaleTotal +MaleTotal,
                                 totbreak = Female04 + Female511 + Female1217 + 
                                            Female1859 + Female60ormore + FemaleUnknown +
                                            Male04 + Male511 + Male1217 + Male1859 +
                                            Male60ormore + MaleUnknown,
                                 
                                 hasbreak = ifelse(Total - totGen == 0, "yes", "no" ))


    if ( nrow(demographics1) ==  0 ){
     info <-  paste0("There\'s no recorded Gender disaggregation for Forcibly Displaced People across Borders in ", ctrylabel )
     p <- ggplot() +  annotate("text",  x = 1, y = 1, size = 12,  
                                        label = info ) +  theme_void() 
      
    } else {
    
      tot <- format( sum(demographics1$Total) ,  big.mark=",")
      totprop <-   format( round( sum(demographics1$totGen) / 
          sum(demographics1$Total )  *100,1),  big.mark=",")  
      
            if (totprop == 0 ) {
              info <- paste0("There\'s no recorded Gender disaggregation for \n all of the ",tot, " persons in ", ctrylabel  )
              p <- ggplot() +  annotate("text",  x = 1, y = 1, size = 12,  
                                        label = info ) +  theme_void() 
              
              
            } else {
              #names(demographics)
              pyramid <-  demographics1[ demographics1$Year == max(demographics1$Year),
                                        c(
                                            "Female04",
                                            "Female511",
                                            "Female1217",
                                            "Female1859",
                                            "Female60ormore",
                                            "FemaleUnknown",
                                           # "FemaleTotal",
                                            "Male04",
                                            "Male511",
                                            "Male1217",
                                            "Male1859",
                                            "Male60ormore",
                                            "MaleUnknown"#,
                                           # "MaleTotal"       
                                           )]  
              
              pyramid2 <- data.frame(lapply(pyramid, function(x) { as.numeric( gsub("NA", "0", x)) })) |>
                pivot_longer(
                  cols = Female04:MaleUnknown,
                  names_to = "Class",
                  values_to = "Sum",
                  values_drop_na = TRUE
                ) 
              
              pyramid3 <- as.data.frame(aggregate(pyramid2$Sum,
                                                        by = list(pyramid2$Class#, pyramid2$REGION_UN
                                                                  ),
                                                        sum))
              names(pyramid3)[1] <- "Class"
              names(pyramid3)[2] <- "Count"
              
              pyramid3 <- pyramid3 |> 
                mutate(gender = case_when(str_detect(Class, "Male") ~ "Male",
                                          str_detect(Class, "Female") ~ "Female")) |> 
                mutate(age = case_when(str_detect(Class, "04") ~ "0-4",
                                       str_detect(Class, "511") ~ "5-11",
                                       str_detect(Class, "1217") ~ "12-17",
                                       str_detect(Class, "1859") ~ "18-59",
                                       str_detect(Class, "60") ~ "60+",
                                       str_detect(Class, "Unknown") ~ "Unknown")) 
              
              pyramid3$pc <- pyramid3$Count / sum(pyramid3$Count) * 100
              pyramid3$age <- factor(pyramid3$age, levels = c("0-4", "5-11",  "12-17",  "18-59", "60+", "Unknown"))
              
              p <- ggplot(pyramid3, aes(x = age, 
                                   fill = gender,
                                    y = ifelse(test = gender == "Female",
                                          yes = -pc, no = pc)) ) + 
                geom_bar(stat = "identity") +
                geom_label(aes(x = age,
                               y = ifelse(test = gender == "Female",
                                          yes = -pc -5 , no = pc),
                              label =  paste0(format(round(pc, 1),  big.mark=","),"%") 
                              ),
                           hjust = 0,
                           vjust = 0.5,
                           colour = "black",
                           fill = NA,
                           label.size = NA,
                          # family = "Lato",
                           size = 4) +
                scale_y_continuous(labels = abs, limits = max(pyramid3$pc) * c(-1,1)) +
                labs(title = paste0("Population Pyramid for Forcibly Displaced People" ),
                     
                     subtitle = paste0("As of ", year, 
                                       ", gender disaggregation is available for ", totprop, " % of the ",tot,
                                       " individuals in", ctrylabel),
                     x = "", 
                     y = "Percent of population",
                     caption =  "Source: UNHCR.org/refugee-statistics.\n Forced Displacement includes Refugees, Asylum Seekers and Other in Need of International Protection.") +
                scale_colour_manual(values = c("#126db4","#01ab91"), # based on Asia Report
                                    aesthetics = c("colour", "fill")) +
                coord_flip() +
                theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
                theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
                          panel.grid.major.y = element_blank())
              
             
           }
    }
  
   return(p)
}
```

    
```{r examples-plot_ctr_pyramid, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_pyramid(year = 2021,
                country_asylum_iso3c = "FRA",
                pop_type =   "ASY")

``` 


    
## Plot Refugee Recognition rate
    
```{r function-plot_ctr_recognition}
#' Display A Chart with Refugee Recognition Rater
#' 
#' In the absence of an internationally agreed methodology for calculating recognition rates,
#'  UNHCR uses two rates to compute the proportion of refugee claims accepted during the year: 
#'  
#'   * The Refugee Recognition Rate divides the number of asylum-seekers granted Convention refugee
#'   status by the total number of accepted (Convention and, where relevant, complementary 
#'   protection) and rejected cases. 
#'   
#'   * The Total Recognition Rate divides the number of asylum-seekers granted Convention
#'    refugee status and complementary form of protection by the total number
#'    of accepted (Convention and, where relevant, complementary protection) and
#'     rejected cases. Non-substantive decisions are, to the extent possible, 
#'     excluded from both calculations. For the purpose of international comparability, 
#'     UNHCR only uses these two recognition rates and does not report nationally
#'      calculated rates.
#'      
#'      See https://www.unhcr.org/4ce531e09.pdf
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param measure this can be either:
#'            * RefugeeRecognitionRate 
#'            * TotalRecognitionRate
#' @param order_by this can be either:
#'            * Recognized  
#'            * ComplementaryProtection  
#'            * TotalDecided 
#'            
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty pretty_breaks
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr  scale_fill_unhcr_d
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_ctr_recognition <- function(year = 2022,
                                 country_asylum_iso3c  ,
                                 top_n_countries = 10, 
                                 measure = "RefugeeRecognitionRate",
                                 order_by = "TotalDecided" ){
   
   ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()
   
  
   measurelabel <- dplyr::case_when( measure == "RefugeeRecognitionRate"  ~ "Refugee Recognition Rate", 
                                     measure == "TotalRecognitionRate"  ~ "Total Recognition Rate")
   
   order_bylabel <- dplyr::case_when( order_by == "Recognized"  ~ "Recognized Refugee Status Decisions", 
                       order_by == "ComplementaryProtection"  ~ "Complementary Protection Decisions",
                       order_by == "TotalDecided"  ~ "Total Decision (independently of the outcome)")

  topOrigin <-  unhcrdatapackage::asylum_decisions %>%
  filter( CountryAsylumCode == country_asylum_iso3c &
            Year == year) %>% 
  ## the below is change - DecisionsAveragePersonsPerCase- is just indicative... so no need to use it to m
 # mutate(DecisionsAveragePersonsPerCase = map_dbl(DecisionsAveragePersonsPerCase, ~replace_na(max(as.numeric(.), 1), 1))) %>%
  mutate(DecisionsAveragePersonsPerCase = 1 ) %>%
  group_by(CountryOriginName) %>% 
  summarize(Recognized = sum(Recognized * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            ComplementaryProtection = sum(ComplementaryProtection * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            TotalDecided = sum(TotalDecided * DecisionsAveragePersonsPerCase, na.rm = TRUE)) %>%
  mutate(RefugeeRecognitionRate = (Recognized ) / TotalDecided,
         TotalRecognitionRate = (Recognized + ComplementaryProtection) / TotalDecided) %>%
  # filter(TotalDecided  != 0) %>%
  # filter(TotalDecided  > 1000)  %>%
  mutate(CountryOriginName = str_replace(CountryOriginName, " \\(Bolivarian Republic of\\)", ""))

topOrigin1 <-  topOrigin  %>%
  mutate( measured = .data[[measure]])  %>%
  mutate( order_by = .data[[order_by]])  %>%
  arrange(desc(order_by)) %>%
  head(top_n_countries)   
 
 
  
 
rsdorigin <- ggplot(topOrigin1, aes(y = measured, 
             x = reorder(CountryOriginName, measured))) +
  #scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale())) + ## Format axis number
  scale_y_continuous( label =  scales::label_percent( accuray = 0, suffix = "%") ) +

  #facet_grid(.~ ctry_asy) +  
  geom_bar( stat ="identity", fill = "#0072bc") +
  coord_flip() +
#  geom_hline(yintercept = 0, size = 1.1, colour = "#333333")   +
  labs( title = paste0(measurelabel, " | ", year, " in ", ctrylabel),
        caption = 'Source: UNHCR.org/refugee-statistics ',
       subtitle = paste0( "For top ", top_n_countries, " Countries of Origin ordered by ", order_bylabel ),
       x = " ", 
       y = " " ) +
  theme_unhcr( grid = "Y",
               axis = "x",  axis_title = "" ,
              font_size = 10 ) + 
  theme(#axis.text.x = element_blank(),
    # legend.position = "none",
    
    panel.grid.major.x = element_line(color = "#cbcbcb"), 
    panel.grid.major.y = element_blank()) ### changing grid line that should appear) 


  return(rsdorigin)

    
}
```
  
```{r example-plot_ctr_recognition}
plot_ctr_recognition(year = 2022,
                     country_asylum_iso3c = "USA",
                        top_n_countries = 10, 
                        measure = "RefugeeRecognitionRate",
                                 order_by = "TotalDecided" )
```
  
```{r tests-plot_ctr_recognition}
# test_that("plot_ctr_recognition works", {   expect_true(inherits(plot_ctr_recognition, "function")) })
```
  
    
## Asylum Applications & Decision over time


```{r function-plot_ctr_asylum}
#' Asylum Applications & Decision over time
#' 
#' This charts allow to visualize trends in terms of asylum applications, decision and refugee status recognition
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param lag Number of year to used as comparison base
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty pretty_breaks
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr  scale_fill_unhcr_d
#' 
#' @return a ggplot2 object
#' 
#' @export

plot_ctr_asylum <- function(year = 2022,
                            country_asylum_iso3c = country_asylum_iso3, 
                            lag = 10){
    
     ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()
  
    apps <- unhcrdatapackage::asylum_applications|>
          filter(CountryAsylumCode == country_asylum_iso3c )|>
          group_by(Year, CountryAsylumCode) |>
         summarize (NumberApplications = sum(NumberApplications , na.rm= TRUE) )

    decs <- unhcrdatapackage::asylum_decisions |>
          filter(CountryAsylumCode == country_asylum_iso3c ) |>
          group_by(Year, CountryAsylumCode) |>
         summarize (Recognized = sum(Recognized , na.rm= TRUE),
                  ComplementaryProtection = sum( ComplementaryProtection , na.rm= TRUE),
                  OtherwiseClosed = sum(OtherwiseClosed , na.rm= TRUE),
                  Rejected = sum(Rejected , na.rm= TRUE),
                  TotalDecided = sum(TotalDecided , na.rm= TRUE))

    
 data <- dplyr::inner_join(apps, decs) |>   # names(data)
         dplyr::filter( Year >= (year - lag)) |>
         dplyr::select( Year,  NumberApplications, Recognized, TotalDecided ) |>
         tidyr::pivot_longer( 
              cols = NumberApplications:TotalDecided,
              names_to = "AsylumStage",
              values_to = "Total",
              values_drop_na = TRUE
            )
 # levels(as.factor(data$AsylumStage))
 data$AsylumStage <- dplyr::recode (data$AsylumStage, "NumberApplications"= "Total Number of Applications",
                                            "TotalDecided" = "Total Number of Decisions",
                                             "Recognized" = "Number of Refugee Status Recognition Decisions")
  data$AsylumStage <- factor(data$AsylumStage, levels = c("Total Number of Applications",
                                                          "Total Number of Decisions",
                                                          "Number of Refugee Status Recognition Decisions"))
 
 p <- ggplot(data,
             aes(x= Year, y = Total, fill = AsylumStage)) +
     geom_bar(stat = "identity", position = "dodge", width = 0.8 ) + 
     scale_fill_unhcr_d(palette = "pal_unhcr") +
    # scale_fill_manual(values = c( "#FAAB18", "#0072bc", "#FEEB18")) +  
     scale_x_continuous(breaks = pretty_breaks(10)) +
    # scale_x_discrete(guide = guide_axis(check.overlap = TRUE)) +
     scale_y_continuous( label = scales::label_number(accuracy = 1, scale_cut = cut_short_scale()))+ ## Format axis number
     labs(title = paste0( " Asylum Applications & Decisions | ", ctrylabel, " " ,  (year-lag) ," - ", year),
       subtitle = paste0( "Note that under certain circumstance, one person may have more than one applications "), 
       x="",
       y ="",
       caption = "Source: UNHCR.org/refugee-statistics") + 
     theme_unhcr(font_size = 14, ## Insert UNHCR Style
                 grid = "X" #, 
                #  axis = "Y", 
                #  axis_title = TRUE, 
                # axis_text = "Y" 
                )  +
     theme(panel.grid.major.y = element_line(color = "#cbcbcb"), 
           panel.grid.major.x = element_blank()) ### changing grid line that should appear
  
  return(p)

  
  
      
}
```
  
```{r example-plot_ctr_asylum}
plot_ctr_asylum(year = 2022,
                country_asylum_iso3c = "ECU", 
                            lag = 10)
```
  
```{r tests-plot_ctr_asylum}
#test_that("plot_ctr_asylum works", {   expect_true(inherits(plot_ctr_asylum, "function")) })
```
  

## Average Asylum Processing Time
    
```{r function-plot_ctr_processing_time}
#' Plot Average processing time (in days) from registration to first instance asylum decision
#' 
#' This indicator measures the average number of days from the date of completion of registration of the asylum application to the date of notification of first instance asylum decision for all persons who were notified of a first instance RSD/asylum decision during the reporting period. 
#' Status determination procedures are a core protection function and the principle mechanism through which international protection needs of Persons of Concern may be determined in accordance with the key provisions of the 1951 Convention and 1967 Protocol relating to the Status of Refugees, the 1954 Convention relating to the Status of Stateless Persons, or relevant regional refugee protection instruments. Status determination procedures are therefore central to the full and effective enjoyment of the universal right to seek and enjoy asylum and the specific rights guaranteed by the above instruments.
#' A prolonged waiting period during the status determination procedure is an important indicator of the state of efficiency, fairness, adaptability integrity and hence, overall quality of the national asylum or, depending on the context, UNHCR Mandate RSD procedure, including the timeliness and effectiveness of the overall protection response in the country 
#'  (RBM Outcome Indicator 2.1) - see https://intranet.unhcr.org/content/dam/unhcr/intranet/protection-operations/compass/en/guidance/3/coreindicatorsmetadata/2.0%20Core%20Indicator%20Metadata%2004%2010%202021.pdf#page=67
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_ctr_processing_time <- function(year = 2022,
                              country_asylum_iso3c = country_asylum_iso3){
    
  
#   library(tidyverse)
# library(lubridate)
# library(jsonlite)
#   country_asylum_iso3c <- "CHL" # iso3 code
# 
#     apps <- unhcrdatapackage::asylum_applications|>
#           filter(CountryAsylumCode == country_asylum_iso3c )|>
#           group_by(Year, CountryAsylumCode, 
#                    CountryAsylumName, ProcedureType, 
#                    ProcedureName, ApplicationTypeCode, ApplicationType) |>
#          summarize (NumberApplications = sum(NumberApplications , na.rm= TRUE) ) 
#     
#   # coa <-   "CHL"
#     
#   ## Equivalent to this API - call 
# # apps1 <- fromJSON(glue::glue("https://api.unhcr.org/population/v1/asylum-applications/?limit=100&dataset=asylum-applications&displayType=totals&yearFrom=1951&yearTo=2022&coa={coa}&columns%5B%5D=procedure_type&columns%5B%5D=app_type&columns%5B%5D=app_pc&columns%5B%5D=app_size&columns%5B%5D=dec_level&columns%5B%5D=applied"))$items |>  as_tibble()
# 
#   decs <- unhcrdatapackage::asylum_decisions |>
#           filter(CountryAsylumCode == country_asylum_iso3c ) |>
#           group_by(Year, CountryAsylumCode, 
#                    CountryAsylumName, ProcedureType, 
#                    ProcedureName, DecisionTypeCode, DecisionTypeName) |>
#          summarize (Recognized = sum(Recognized , na.rm= TRUE),
#                   ComplementaryProtection = sum( ComplementaryProtection , na.rm= TRUE),
#                   OtherwiseClosed = sum(OtherwiseClosed , na.rm= TRUE),
#                   Rejected = sum(Rejected , na.rm= TRUE),
#                   TotalDecided = sum(TotalDecided , na.rm= TRUE)) 
  
  ## Equivalent to this API - call 
 # decs1 <- fromJSON(glue::glue("https://api.unhcr.org/population/v1/asylum-decisions/?limit=100&dataset=asylum-decisions&displayType=totals&yearFrom=1951&yearTo=2022&coa={coa}&columns%5B%5D=procedure_type&columns%5B%5D=dec_level&columns%5B%5D=dec_pc&columns%5B%5D=dec_recognized&columns%5B%5D=dec_other&columns%5B%5D=dec_rejected&columns%5B%5D=dec_closed&columns%5B%5D=dec_total"))$items |> as_tibble() 

# data <- 
#   left_join(apps |> filter(ProcedureLevel == "FI"),
#             decs |> filter(DecisionTypeCode == "FI")) |> 
#   arrange(year) |> 
#   mutate(across(c(NumberApplications, 
#                   TotalDecided), 
#                 replace_na, 0)) |> 
#   transmute(year = if_else(year == last(year), 
#                            year+.5, 
#                            year+1), # MYSR correction
#             apps = cumsum(NumberApplications), 
#             decs = cumsum(TotalDecided))
# 
# idx <- detect_index(data$apps, ~.<last(data$decs), .dir = "backward")
# 
# t <- date_decimal(data$year[idx] + (last(data$decs) - data$apps[idx]) / (data$apps[idx+1] - data$apps[idx]))
# 
# stat <- interval(t, make_date(2022, 6, 30)) / days()
# 
# data <- data |> 
#   pivot_longer(-Year, names_to = "flow", values_to = "n") 
# 
# p <- data |> 
#   ggplot(aes(year, n, fill = flow)) + 
#   geom_area(position = "identity") +
#   annotate("segment", 
#            x = decimal_date(t), 
#            y = last(data$decs), 
#            xend = last(data$year), 
#            yend = last(data$decs)) +
#   annotate("text", 
#            x = 2020,
#            y = last(data$decs), 
#            vjust = -.5,
#            label = glue::glue("{round(stat)} days")) +
#   scale_y_continuous(labels = scales::label_comma()) +
#   scale_fill_manual(labels = c(decs = "Decisions",
#                                apps = "Applications"),
#                     values = c(decs = "#0072BC",
#                                apps = "#FAEB00"),
#                     name = NULL) +
#   labs(title = "Average processing time (in days) from registration to first instance asylum decision",
#        subtitle = glue::glue("{first(apps$coa_name)}, {year}"),
#        x = NULL, 
#        y = "Cumulative total") +
#   guides(fill = guide_legend(reverse = TRUE)) +
#   theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
#   theme(legend.position = "right")
#   
# return(p)
  
}
```
  
```{r example-plot_ctr_processing_time}
# plot_ctr_processing_time(year = 2022,
#                               country_asylum_iso3c = "CHL")
```
  
```{r tests-plot_ctr_processing_time}
#test_that("plot_ctr_processing_time works", { expect_true(inherits(plot_ctr_processing_time, "function")) })
```
 
 
## Asylum Processing
    
```{r function-plot_ctr_process}
#' Title
#' 
#' Description#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom  ggforce geom_parallel_sets geom_parallel_sets_axes  
#'                  geom_parallel_sets_labels gather_set_data
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export 
plot_ctr_process <- function(year = 2022,
                              country_asylum_iso3c ){
  
  
  linksDecision.Ori.Procedure <- unhcrdatapackage::asylum_decisions_long %>% 
  filter( Year == year  & 
            CountryAsylumCode  == country_asylum_iso3c ) %>% 
  ## Group small records under other
  mutate(CountryOriginName = forcats::fct_lump_prop(CountryOriginName, prop = .01, w = Value)) %>% 
  mutate(CountryOriginName = str_replace(CountryOriginName, " \\(Bolivarian Republic of\\)", "")) %>% 
  ## Calculate grouped value for Origin to procedure..
  group_by(CountryOriginName, ProcedureName ) %>%
  summarise(value = sum(Value) ) %>%
  ## Rename variable
  rename(source = CountryOriginName) %>%
  rename(target = ProcedureName) 

linksDecision.Procedure.Type <- unhcrdatapackage::asylum_decisions_long %>%
  filter(Year == year   & CountryAsylumCode  == country_asylum_iso3c ) %>% 
  ## Group small records under other
  ## Calculate grouped value for Origin to procedure..
  group_by(ProcedureName, DecisionTypeName ) %>%
  summarise(value = sum(Value) ) %>%
  ## Rename variable
  rename(source = ProcedureName) %>%
  rename(target = DecisionTypeName) 

linksDecision.Type.Output <- unhcrdatapackage::asylum_decisions_long %>%
  filter(Year == year   & CountryAsylumCode  == country_asylum_iso3c ) %>% 
  ## Group small records under other
  ## Calculate grouped value for Origin to procedure..
  group_by(DecisionTypeName,Decision.output ) %>%
  summarise(value = sum(Value) ) %>%
  ## Rename variable
  rename(source = DecisionTypeName) %>%
  rename(target = Decision.output)

 

linksallDecision <- rbind(linksDecision.Ori.Procedure,
                  linksDecision.Procedure.Type,
                  linksDecision.Type.Output )



#  reshape2::melt(Titanic) |>
#  ggforce::gather_set_data(  1:4) |>
# # Use nudge_x to offset and hjust = 0 to left-justify label
# ggplot( aes(x, id = id, split = y, value = value)) +
#   ggforce::geom_parallel_sets(aes(fill = Sex), alpha = 0.3, axis.width = 0.1) +
#   ggforce::geom_parallel_sets_axes(axis.width = 0.1) +
#   ggforce::geom_parallel_sets_labels(colour = 'red', angle = 0, nudge_x = 0.1, hjust = 0)

    
  ## summarize data
flow_table <- linksallDecision %>%
  count(source, target) %>%  # get counts 
  ggforce::gather_set_data(x = c("source", "target")) %>%     # change format for plotting
  mutate(x = fct_relevel(x, c("source", "target"))  # set startcause as first level
          )


## plot your dataset 
  ## on the x axis is the start and end causes
  ## gather_set_data generates an ID for each possible combination
  ## splitting by y gives the possible start/end combos
  ## value as n gives it as counts (could also be changed to proportion)
ggplot(flow_table, 
       aes(x, 
          id = id, 
          split = y, 
          value = n)) +
  ## colour lines by sex 
  ggforce::geom_parallel_sets( #aes(fill = sex),
                     alpha = 0.5,
                     axis.width = 0.2) +
  ## fill in the label boxes grey
  ggforce::geom_parallel_sets_axes(axis.width = 0.15,
                          fill = "grey80", 
                          color = "grey80") +
  ## change text colour and angle (needs to be adjusted)
  ggforce::geom_parallel_sets_labels(color = "black",
                            angle = 0,
                            size = 5) +
  ## adjusted y and x axes (probably needs more vertical space)
  scale_x_discrete(name = NULL, 
                   expand = c(0, 0.2)) + 
  ## remove axis labels
  theme(
    title = element_text(size = 26),
    text = element_text(size = 26),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.y = element_blank(),
    panel.background = element_blank(),
    legend.position = "bottom",                    # move legend to bottom
    legend.title = element_blank(),                # remove title
  )
  
  
}
```
  
```{r example-plot_ctr_process}
plot_ctr_process(year = 2022,   country_asylum_iso3c = "CHL")
```
  
```{r tests-plot_ctr_process}
# test_that("plot_ctr_process works", {   expect_true(inherits(plot_ctr_process, "function")) })
```
    

## Plot Solution Over time 
    
```{r function-plot_ctr_solution}
#' Plotting solutions within a country
#' 
#' As part of UNHCR standard approach, there are mostly 3 types of durable solutions for Refugees:
#'  - Voluntary Repatriation in origin country 
#'  - Naturalization in the host country
#'  - Resettlement in a third country 
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'
 
plot_ctr_solution <- function(year = 2021,
                              lag = 10,
                              country_asylum_iso3c = country_asylum_iso3c,
                              pop_type = pop_type){
  
    ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()
  
  
    Solution <- unhcrdatapackage::solutions_long  %>%
                dplyr::left_join(y= unhcrdatapackage::reference, 
                               by = c("CountryAsylumCode" = "iso_3")) %>%
      
              filter(CountryAsylumCode  == country_asylum_iso3c & 
                      Year > (year - lag) &
                      Solution.type.label != "IDP returns" ) %>%
              mutate(Year = as.factor(Year) ) %>%
              group_by(Year, Solution.type.label ) %>%
              summarise(Value2 = sum(Value) )  %>%
              mutate( valabel =  ifelse(Value2 > 1000, 
                                       paste(scales::label_number_si(accuracy = 0.1)(Value2)),
                                       as.character(Value2)) )   

    
    ncat <- ifelse( nlevels(as.factor(Solution$Solution.type.label)) %in% c(2,4), 2,3)
    #levels(as.factor(solutions_long.asy$Solution.type.label))
    Solution$Solution.type.label <- factor(Solution$Solution.type.label,
                                                     levels = c("Naturalisation", 
                                                                "Resettlement arrivals",
                                                                "Refugee returns",
                                                                "IDP returns" )) 



if( nrow(Solution) ==  0 ){
   p <- paste0("There\'s no recorded solutions in ", country_asylum_iso3c )
  
} else {
  

#Make plot
p <- ggplot(Solution, aes(x = Year, y = Value2  )) + 
  geom_bar(stat = "identity", 
           position = "identity", 
           fill = "#0072bc" ) + # here we configure that it will be bar chart
 # scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale())) + ## Format axis number
  
  scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()))+

  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+
  #xlim(c(year-lag, year +1)) +
  facet_wrap( vars(Solution.type.label ), ncol = ncat) +
  #geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
  theme(panel.grid.major.y  = element_line(color = "#cbcbcb"), 
        panel.grid.major.x  = element_blank(), 
        panel.grid.minor = element_blank()) + ### changing grid line that should appear
  ## and the chart labels
  labs(title = "What are the trends in terms of Solutions?",
       subtitle = paste0("Data for Forcibly Displaced People across Borders as of ", year, " filtered for ", ctrylabel ), 
       x = "",
       y = "",
       caption = "Source: UNHCR.org/refugee-statistics.\n Forced Displacement includes Refugees, Asylum Seekers and Other in Need of International Protection.")

}
    
return(p)
}
```
  
```{r example-plot_ctr_solution}
plot_ctr_solution(year = 2021,
                  country_asylum_iso3c= "UGA",
                  pop_type = c("REF", "ASY"))
```
  
```{r tests-plot_ctr_solution}
#test_that("plot_ctr_solution works", {expect_true(inherits(plot_ctr_solution, "function")) })
```
  




    
## Plot Ratio Refugee Migrant
    
```{r function-plot_ctr_disp_migrant}
#' Plotting ratio Refugee/Asylum seekers vs Migrant within a country
#' 
#' This plot is created to provide an overview of the magnitude of immigration in relation to foreced displacement in a country. The vertical axis display the proportion of the migrants 
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text geom_point scale_size coord_cartesian
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom wbstats  wb 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @importFrom viridis scale_fill_viridis
#' 
#' @return a ggplot2 object
#' 
#' @export
#'
plot_ctr_disp_migrant <- function(year = 2021,
                              country_asylum_iso3c = country_asylum_iso3c,
                              pop_type = pop_type){
  
  ctrylabel <- unhcrdatapackage::reference |> 
                 filter(iso_3 == country_asylum_iso3c ) |> 
               select(ctryname) |> 
                pull()
  
  
  wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL", "NY.GDP.MKTP.CD", "NY.GDP.PCAP.CD", "NY.GNP.PCAP.CD"),
             
               country = c( country_asylum_iso3c )  ,         
               startdate = 1990, 
               enddate = 2022, 
               return_wide = TRUE)
      # Renaming variables for further matching
      names(wb_data)[1] <- "iso_3"
      names(wb_data)[2] <- "Year"
      wb_data$Year <- as.numeric(wb_data$Year)

  
  displaced <- left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                               y= unhcrdatapackage::reference, 
                               by = c("CountryAsylumCode" = "iso_3")) %>%
              filter(Population.type  %in% pop_type) %>%
              filter(CountryAsylumCode == country_asylum_iso3c) %>%
              filter( Year == max(Year) ) %>%
              mutate( iso_3 = CountryOriginCode) %>% 
              group_by(Year, iso_3,CountryOriginName, UNHCRBureau, hcr_subregion, INCOME_GRP) %>%
              summarise(Asylum_Refugee_in = sum(Value) )  %>%
              filter( iso_3 != "UKN") %>%
              arrange( desc(Asylum_Refugee_in)) %>%
              head(10)%>%
              as.data.frame()
  
  thiscode <- unhcrdatapackage::reference |>
                filter(iso_3 == country_asylum_iso3c) |>
                 select(M49_code) |>
                 pull()

  migrant <-  left_join( x= unhcrdatapackage::migrants, 
                               y= unhcrdatapackage::reference, 
                               by = c("CountryOriginM49" = "M49_code")) %>%
              filter(CountryDestinationM49 == thiscode) %>%
              group_by(Year, iso_3,CountryOriginName, UNHCRBureau, hcr_subregion, INCOME_GRP) %>%
              summarise(Immigrant = sum(Value) ) %>%
              mutate( shareOrgin = (Immigrant / sum(Immigrant))*100 ) %>%
              filter( Year == 2020 ) %>%
              as.data.frame() %>%
              mutate( Year = as.numeric(Year) ) %>%
              mutate( shareOrgin =  round(Immigrant / sum(Immigrant),3)*100 )

#str(migrant)
#str(displaced)

thismigProfile <-  migrant  %>%
  dplyr::full_join( displaced[ ,c("Asylum_Refugee_in","iso_3" )], by = c("iso_3")) %>%
  dplyr::left_join(  wb_data, by = c("Year","iso_3")) %>%
  ## Calculate a few ration
  mutate( ratioAsylum_Refugee_in = (Asylum_Refugee_in / SP.POP.TOTL)*100,
          ratioImmigrant = (Immigrant / SP.POP.TOTL)*100,
          ratioAsylum_Immigrant = (Asylum_Refugee_in / Immigrant)*100)  %>%
  arrange( desc(Asylum_Refugee_in)) %>%
  head(10)


if( nrow(displaced) ==  0 ){
     info  <- paste0("There\'s no recorded Forcibly Displaced People across Borders in ",ctrylabel )
     p <- ggplot() +  annotate("text",  x = 1, y = 1, size = 12,  
                                        label = info ) +  theme_void() 
  
} else {

p <- ggplot(thismigProfile,
       aes(x= ratioAsylum_Immigrant, 
           y= shareOrgin/100, 
           size= Asylum_Refugee_in/100, 
           #fill= INCOME_GRP,
           label = iso_3)) +
  geom_point(alpha=0.5, 
             shape=21, 
             color="black",
             fill = "#0072BC") +
  scale_size(range = c(.1, 24), guide= "none", ## Do not show Legend
             name="# of Forcibly Displaced People") +
  #viridis::scale_fill_viridis(discrete=TRUE,  name="Country Income Classification") +
  scale_x_continuous(labels = scales::label_percent(accuracy = .1)) +
  scale_y_continuous(labels = scales::label_percent(accuracy = .1)) +
  # facet_wrap( vars(Year ), ncol = 2) +
  coord_cartesian(clip = "off") +
  ggrepel::geom_label_repel(box.padding = 0.5,
                            size =4,
                            # max.overlaps = 2 
                            fill = "white", 
                            xlim = c(-Inf, Inf), 
                            ylim = c(-Inf, Inf)) + 
  labs(title = paste0("Share of Forcibly Displaced People within all Migrants in ", ctrylabel  ) ,
       subtitle = "This chart provides insights on the relative weight of Forced Displacement for countries generating such type of displacement. \n The size of the circle represents the number of Refugees, Asylum Seekers and oher in need of International Protection ", 
       y = "Share of immigrants from the country in relation with all immigrants",  #shareOrgin, 
       x ="Share of migration in relation with forced displacement for each country",  # ratioAsylum_Immigrant, 
       caption = "Source: UNHCR.org/refugee-statistics (includes REF +ASY+OIP in calculation) & UNDESA Migrant Stock as of 2020.\n Only main top 10 countries ( or less depending on data availibility) linked to Forced Displaced across Borders are presented.") +
  theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
  theme(legend.position="bottom", 
        panel.grid.major.y  = element_line(color = "#cbcbcb"), 
        panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.minor = element_blank())   ### changing grid line that should appear
  
}

return(p)
    
}
```
  
```{r example-plot_ctr_disp_migrant}
plot_ctr_disp_migrant(year = 20212,
                    country_asylum_iso3c = "BRA" )
```
  
```{r tests-plot_ctr_disp_migrant}
#test_that("plot_ctr_disp_migrant works", {   expect_true(inherits(plot_ctr_disp_migrant, "function")) })
```
  
    
    
--- 

# Regional Questions




## Population group in the region  
    
```{r function-plot_reg_treemap}
#' Population group in the region  
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom scales label_percent
#' @importFrom treemapify geom_treemap geom_treemap_text
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return plot a ggplot2 object 
#' 
#' @export

plot_reg_treemap <- function(year = 2022,  
                             region = "Americas",
                             pop_type = c("REF", "ASY", "IDP", "OIP", "STA", "OOC")){
  
  ## Comparison of Refugees
## Filter popdata for the country report

datatree <-   dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
  dplyr::filter( Year == year  ) %>%
  dplyr::filter( Population.type %in% pop_type  ) %>%
 # dplyr::filter( Year == year | Year == (year -1) ) %>%
  dplyr::select(Year, UNHCRBureau ,Population.type, Population.type.label, Value) %>%
  dplyr::group_by( Year, UNHCRBureau, Population.type.label , Population.type ) %>%
  dplyr::summarise(Value = sum( Value, na.rm = TRUE))  %>%
  dplyr::ungroup(Year, UNHCRBureau ,Population.type, Population.type.label)  %>%
  dplyr::mutate(  freq = scales::label_percent( accuracy= .1, suffix = "%")(Value / sum(Value)) ) %>%
  dplyr::filter(UNHCRBureau  == region   )   %>%
  dplyr::mutate(  freqinReg = scales::label_percent( accuracy= .1, suffix = "%") (Value / sum(Value)) )  
 
## Treemapify
p <- ggplot(datatree, 
       aes(area = Value, 
           fill = Population.type, 
           label = paste0(freqinReg, "\n", Population.type.label)  )) +
  treemapify::geom_treemap() +
  treemapify::geom_treemap_text(colour = "white",
                    place = "centre", size = 15) +
 # scale_fill_viridis_c() +
  scale_fill_manual( values = c(   "IDP" = "#00B398",
                                     "OIP"="#EF4A60",
                                     "ASY" = "#18375F",
                                     "REF" = "#0072BC",
                                     "OOC" ="#8395b9",
                                     "STA"="#E1CC0D",
                                     "HCO"="#1b9e77")) +
  unhcrthemes::theme_unhcr(font_size = 22)  + ## Insert UNHCR Style
  theme(legend.position = "none") +
  ## and the chart labels
  labs(title = paste0("Population of Concern & Affected Host Communities in ", region),
        subtitle = paste0("As of   ",  year, ", a total of ", format(round(sum(datatree$Value), -3),  big.mark=","), " Individuals"),
       x = "",
       y = "",
       caption = "Source: UNHCR.org/refugee-statistics")
 
 return(p)
    
}
```
  
```{r example-plot_reg_treemap}
plot_reg_treemap(year = 2022,  region = "Americas")
```
  
```{r tests-plot_reg_treemap}
#test_that("plot_reg_treemap works", {   expect_true(inherits(plot_reg_treemap, "function")) })
```
  

## Plot World Comparison

    
```{r function-plot_reg_share}
#' A simple chart to compare a population group between the Region and the rest of the world
#' 
#' Simple treemap charts to do the comparison
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom scales label_percent
#' @importFrom stringr str_wrap
#' @importFrom treemapify geom_treemap geom_treemap_text
#' @importFrom unhcrthemes theme_unhcr scale_fill_unhcr_d
#' 
#' @return plot a ggplot2 object 
#' 
#' @export

plot_reg_share <- function(year = 2022,  
                             region = "Americas",
                             pop_type = "REF"){
  
 pop_typelabel <-   dplyr::case_when( 
           pop_type == "REF"  ~  "Refugees",
            pop_type=="IDP"   ~ "Internally displaced persons",
            pop_type=="ASY"   ~ "Asylum seekers",
            pop_type=="OOC"   ~ "Others of concern to UNHCR",
            pop_type=="STA"   ~ "Stateless Persons",
            pop_type=="OIP"   ~ "Other people in need of international protection",
            pop_type=="HCO"   ~ "Host community" )
    
    

datatree <-   dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
  dplyr::filter( Year == year  ) %>%
  dplyr::filter( Population.type %in% pop_type  ) %>%
 # dplyr::filter( Year == year | Year == (year -1) ) %>%
  dplyr::select(Year, UNHCRBureau ,Population.type, Population.type.label, Value) %>%
    dplyr::mutate(Compare = ifelse(UNHCRBureau == region, region, "Rest of the World")) %>%
  dplyr::group_by( Year, Compare, Population.type.label , Population.type ) %>%
  dplyr::summarise(Value = sum( Value, na.rm = TRUE))  %>%
  dplyr::ungroup(Year, Compare ,Population.type, Population.type.label)  %>%
  dplyr::mutate(  freq = scales::label_percent( accuracy= .1, suffix = "%")(Value / sum(Value)) ) 
 
## Treemapify
p <- ggplot(datatree, 
       aes(area = Value, 
           fill = Compare, 
           label = paste0(  format(round(datatree$Value, -3),  big.mark=",") , "\n in ", Compare )  )) +
  treemapify::geom_treemap() +
  treemapify::geom_treemap_text(colour = "white",
                    place = "centre", size = 15) +
  scale_fill_unhcr_d(palette = "pal_unhcr") +
  unhcrthemes::theme_unhcr(font_size = 22)  + ## Insert UNHCR Style
  theme(legend.position = "none") +
  ## and the chart labels
  labs(title = paste0("Share of ", pop_typelabel , " within ", region),
        subtitle = stringr::str_wrap(paste0("As of ",  year,
                          ", about ",
                          datatree |> filter( Compare == region) |> select(freq) |> pull(), 
                          " of that global population category are hosted in the region"), 80),
       x = "",
       y = "",
       caption = "Source: UNHCR.org/refugee-statistics")
 
 return(p)
    
}
```
  
```{r example-plot_reg_share}
plot_reg_share(year = 2022,  
                             region = "Americas",
                             pop_type = "REF")
plot_reg_share(year = 2022,  
                             region = "Americas",
                             pop_type = "ASY")
plot_reg_share(year = 2022,  
                             region = "Americas",
                             pop_type = "OIP")
plot_reg_share(year = 2022,  
                             region = "Americas",
                             pop_type = "IDP")
plot_reg_share(year = 2022,  
                             region = "Americas",
                             pop_type = "STA")
```
  
```{r tests-plot_reg_share}
# test_that("plot_reg_share works", {   expect_true(inherits(plot_reg_share, "function")) })
```
  

## Evolution Over Time  
    
```{r function-plot_reg_evolution}
#' Evolution over time 
#' 
#' Display evoluation over time for specific population group (one or many) and 
#' defined number of years (lag)
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param lag Number of year to used as comparison base 
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY,   OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual
#'              scale_colour_manual 
#'             geom_text geom_line
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom stringr str_replace  
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty pretty_breaks
#' @importFrom unhcrthemes theme_unhcr unhcr_pal
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_reg_evolution <- function(year = 2022,
                              lag = 5,
                              region,
                              pop_type =  c( "REF", "IDP", "ASY", "OOC", "STA", "OIP"
                                             #"HCO"
                                             ) ){
  
  allpop <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                              y= unhcrdatapackage::reference, 
                              by = c("CountryAsylumCode" = "iso_3")) %>% 
              dplyr::filter(Population.type   %in%  pop_type & 
                              Year >=  (year - lag) &
                              UNHCRBureau  == region )|> 
              dplyr::group_by(Year) |> 
              dplyr::summarise(Value = sum(Value, na.rm = TRUE))
  
  p <-  ggplot(allpop) + 
    geom_line(aes(  x = Year, 
                    y = Value  ),
              size = 1,
              color = unhcr_pal(n = 1, "pal_blue")) +
  geom_text( aes(x = Year,
                 y = Value, 
                 label = label_number(scale_cut = cut_short_scale(), accuracy=1)(Value)),
             vjust = -1, 
             size = 4 ) +
  labs(
    title = paste0( region, ": People of Concern | ", (year - lag), "-", year),
    y = "Number of people",
    caption = "Source: UNHCR.org/refugee-statistics" ) +
  scale_x_continuous(breaks = pretty_breaks(n =7)) +
  scale_y_continuous(
    expand = expansion(c(0, 0.1)),
    breaks = pretty_breaks(n = 4),
    labels = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()),
    limits = c(0, 20 * 1e6)
  ) +
  theme_unhcr( grid = "Y",
               axis = "x",  axis_title = "" ,
              font_size = 14 )
  
  return(p)
    
}
```
  
```{r example-plot_reg_evolution}
plot_reg_evolution(year = 2021,
                   lag = 5,
                   region = "Asia",
                   pop_type =  c( "REF", "IDP", "ASY", "OOC", "STA", "OIP"))
```
  
```{r tests-plot_reg_evolution}
t# est_that("plot_reg_evolution works", {  expect_true(inherits(plot_reg_evolution, "function")) })
```
  
 
## Plot Evolution of Population type per year
    
```{r function-plot_reg_population_type_per_year}
#' Display evolution of different population type over years
#' 
#' Summary of Evolution
#'  
#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' 
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#'
#' @export
#'
#'

plot_reg_population_type_per_year <- function(year = 2022,
                                              lag = 5,
                                     region,
                                     pop_type =  c("REF", "ASY", "IDP", "OIP", "STA", "OOC") ) {
  

  df <- unhcrdatapackage::end_year_population_totals_long  |> 
        dplyr::left_join( unhcrdatapackage::reference |> 
                      dplyr::select(coa_region = `UNHCRBureau`, iso_3), 
                      by = c("CountryAsylumCode" = "iso_3")) |> 
  dplyr::filter(coa_region == region &
               Year >= (year - lag)  & 
              Population.type %in% pop_type ) |>
    
    
    group_by(Year, coa_region, Population.type, Population.type.label)  |> 
    summarise(Value = sum(Value, na.rm = TRUE)) |> 
    ungroup()
  

  
  year_breaks <- diff(range(df$Year)) + 1 
  
  p <- ggplot(df) +
    geom_col(aes(x = Year, y = Value, fill = Population.type.label ),
             width = 0.7) +
    # geom_text(aes(x = Year, 
    #               y = Value, 
    #               color = Population.type.label, 
    #               label = label_number( accuracy = 1,
    #                                scale_cut = cut_short_scale())(Value)),
    #           position = position_stack(vjust = 0.5),
    #           show.legend = FALSE,
    #           size = 5) +
    
     scale_fill_manual( values = c(   "Internally displaced persons" = "#00B398",
                                     "Other people in need of international protection"="#EF4A60",
                                     "Asylum seekers"= "#18375F",
                                     "Refugees" = "#0072BC",
                                     "Others of concern to UNHCR" ="#8395b9",
                                     "Stateless Persons"="#E1CC0D",
                                     "Host community"="#1b9e77")) +
    scale_x_continuous(breaks = scales::breaks_pretty(n = year_breaks)) +
     scale_y_continuous(expand = expansion(c(0, 0.1))) +
    labs(title = paste0(region, ": Population type per year"), 
         subtitle = "Number of people (thousand)",
         caption = "Source: UNHCR.org/refugee-statistics") +
    theme_unhcr(grid = FALSE, axis = "x", 
                axis_title = FALSE, axis_text = "x",
              font_size = 14) +
    stat_summary(fun = sum, aes(x = Year,
                                y = Value,
                                label = scales::label_number( accuracy = 1,
                                                       scale_cut = cut_short_scale())(..y..),
                                group = Year),
                 geom = "text", size = 5,
                 vjust = -0.5) +
    theme(legend.direction = "vertical",
          legend.key.size = unit(0.8, 'cm'),
          text = element_text(size = 20),
          plot.subtitle=element_text(size=19),
          plot.title = element_text(size=23),
          plot.caption = element_text(size=13))
  
  return(p) # print(p)    
}
```
  
```{r example-plot_reg_population_type_per_year}
plot_reg_population_type_per_year(year = 2022,
                                              lag = 5,
                                     region  = "Americas",
                                     pop_type =   c("REF", "ASY", "IDP", "OIP", "STA", "OOC") )
```
  
```{r tests-plot_reg_population_type_per_year}
# test_that("plot_reg_population_type_per_year works", {   expect_true(inherits(plot_reg_population_type_per_year, "function")) })
```
  

## Plot Population Origin-Destination within the region 
    
```{r function-plot_reg_origin_dest}
#' Plot Population Origin-Destination within the region 
#' 
#' Chord diagram showing Origin destination see - https://jokergoo.github.io/circlize_book/book/
#' 

#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join summarize
#'               
#' @importFrom tidyr replace_na
#' @importFrom circlize chordDiagram circos.track circos.text CELL_META
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return plot a ggplot2 object 
#' 
#' @export
plot_reg_origin_dest <- function(year = 2022,  region = "Americas"){
   


chords <- end_year_population_totals |>
  dplyr::left_join( unhcrdatapackage::reference |> 
                      dplyr::select(coa_region = `UNHCRBureau`, iso_3),  by = c("CountryAsylumCode" = "iso_3")) |> 
  dplyr::filter(coa_region == region &
           Year == year) |> 
  dplyr::mutate(across(REF:OIP, ~ tidyr::replace_na(as.numeric(.), 0)),
         total = REF + ASY + OIP, #+ IDP  + STA + OOC,
         # Lump together factor levels into "other"
         CountryAsylumName = forcats::fct_lump_prop(CountryAsylumName, prop = .02, w = total),
         CountryOriginName = forcats::fct_lump_prop(CountryOriginName, prop = .02, w = total)) |> 
   dplyr::group_by(CountryOriginName, CountryAsylumName) |>
   dplyr::summarize(total = sum(total), .groups = "drop")  |>
# CountryOriginName = fct_recode(CountryOriginName, "Other" = "China")
  dplyr::mutate(CountryOriginName = stringr::str_replace(CountryOriginName, " \\(Bolivarian Republic of\\)", ""),
        CountryAsylumName = stringr::str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
        CountryOriginName = stringr::str_replace(CountryOriginName, " \\(Plurinational State of\\)", ""),
        CountryAsylumName = stringr::str_replace(CountryAsylumName, " \\(Plurinational State of\\)", ""),
        CountryOriginName = stringr::str_replace(CountryOriginName, "United States of America", "USA"),
        CountryAsylumName = stringr::str_replace(CountryAsylumName, "United States of America", "USA"))

circlize::chordDiagram(chords,
                       self.link = 1,
                      # grid.col = colorRampPalette(RColorBrewer::brewer.pal(11, "Paired"))(15),
                       annotationTrack = "grid" ,
                     # preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(chords))))),
                      preAllocateTracks = 1.6
)

circlize::circos.track(track.index = 1,
                        panel.fun = function(x, y) {
                             circlize::circos.text(circlize::CELL_META$xcenter,
                                                   circlize::CELL_META$ylim[1],
                                                   circlize::CELL_META$sector.index,
                                                   facing = "clockwise",
                                                   niceFacing = TRUE,
                                                   adj = c(0, 0.5))
                           },
                           bg.border = NA) # here set bg.border to NA is important


title(main = "Movement of Forcibly Displaced Population", 
      sub = paste0("In ", region, " as of ", year),
      cex.main = 1.5)

  
     return(invisible(NULL))
  
    
}
```
  
```{r example-plot_reg_origin_dest}
plot_reg_origin_dest(year = 2022,  region = "Asia")
```
  
```{r tests-plot_reg_origin_dest}
#test_that("plot_reg_origin_dest works", {   expect_true(inherits(plot_reg_origin_dest, "function")) })
```
  


## Plot Main country of Asylum in the Region


```{r function-plot_reg_population_type_abs}
#' Main country of origin - Absolute value
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY,   OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
#'

plot_reg_population_type_abs <- function(year = 2022,
                                          region = "Americas",
                                          top_n_countries = 9,
                                          pop_type = "REF" ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                       #VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  labelcat <- dplyr::case_when( pop_type == "ASY"  ~ "Asylum seekers", 
                       pop_type == "REF"  ~ "Refugees",
                       pop_type == "OIP"  ~ "Other people in need of international protection", 
                       pop_type == "OOC"  ~ "Others of Concern to UNHCR", 
                       pop_type == "IDP"  ~ "Internally displaced persons", 
                       pop_type == "STA"  ~ "Stateless Persons")
  colorlab <- dplyr::case_when( pop_type == "ASY"  ~ "#18375F", 
                       pop_type == "REF"  ~ "#0072BC",
                       pop_type == "OIP"  ~ "#EF4A60", 
                       pop_type == "OOC"  ~ "#999999", 
                       pop_type == "IDP"  ~ "#00B398", 
                       pop_type == "STA"  ~ "#E1CC0D")
  
  
  df <- end_year_population_totals_long |>
       dplyr::left_join( unhcrdatapackage::reference |> 
       dplyr::select(coa_region = `UNHCRBureau`, iso_3),  by = c("CountryAsylumCode" = "iso_3")) |> 
       dplyr::filter(coa_region == region &
                       (Year == year | Year == year -1) &
                       Population.type %in% pop_type ) |> 
      dplyr::select(Year, CountryAsylumName,Value) |>
      dplyr::group_by(Year, CountryAsylumName) |>
      dplyr::summarise(Value = sum(Value, na.rm=TRUE)) |> 
      dplyr::ungroup() |>
      dplyr::group_by(CountryAsylumName) |> 
      dplyr::arrange(Year) |>
      dplyr::mutate(diff_pop_type_value = scales::label_percent(accuracy = 1.1,
                                                          trim = FALSE  ) (((Value - lag(Value))/lag(Value) ) )) |> 
      dplyr::ungroup() |>
      dplyr::filter(Year == year) |> 
      dplyr::arrange(desc(Value))  |> 
      head(top_n_countries)


p <-  ggplot(df) +
  geom_col(aes(x = reorder(CountryAsylumName, Value), 
               y = Value),
           fill = colorlab ,
           width = 0.8) +
  coord_flip() + 
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, Value < max(Value) / 1.5),
    aes(
      y = Value,
      x = reorder(CountryAsylumName, Value),
      label = label_number(accuracy = 1,
                           scale_cut = cut_short_scale())(Value)
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5   ) +
  geom_text(
    data = subset(df, Value >= max(Value) / 1.5),
    aes(
      y = Value,
      x = reorder(CountryAsylumName, Value),
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(Value)),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  geom_text( # positive diff percentage label
    data = subset(df, with(df, !grepl('-', diff_pop_type_value))),
    aes(
      y = Value,
      x = reorder(CountryAsylumName, Value),
      label = diff_pop_type_value
    ),
    hjust = -2.8,
    vjust = 0.5,
    colour = "grey",
    size = 4
  ) +
  geom_text( # negative diff percentage label
    data = subset(df, with(df, grepl('-', diff_pop_type_value))),
    aes(
      y = Value,
      x = reorder(CountryAsylumName, Value),
      label = diff_pop_type_value
    ),
    hjust = -2.5,
    vjust = 0.5,
    colour = "#0472bc",
    size = 4
  ) +
  labs(title = paste0("Main Host Countries for ", labelcat ," | ",  year, " in ", region),
       subtitle = paste0("Number of people for top ", top_n_countries, " countries in the region"),
       caption = "Source: UNHCR.org/refugee-statistics") +
  scale_y_continuous(expand = expansion(c(0, 0.1))) +
  theme_unhcr(font_size = 14,
              grid = FALSE, 
              axis = "y", 
              axis_title = FALSE, 
              axis_text = "y") +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))

  return(p) # print(p)
  }
```

```{r examples-plot_reg_population_type_abs, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
plot_reg_population_type_abs(year = 2022,
                              region = "Americas",
                              top_n_countries = 5,
                              pop_type = "REF"
                              ) 

plot_reg_population_type_abs(year = 2022,
                              region = "Americas",
                              top_n_countries = 5,
                              pop_type = "ASY"
                              ) 

```



## Plot Biggest decrease in Refugee Population
 
    
```{r function-plot_reg_decrease}
#' Plot Biggest decrease in Refugee Population
#' 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param lag Number of year to used as comparison base
#' @param topn how many top countries to show..
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom wbstats  wb 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_reg_decrease <- function(year = 2021,
                              lag = 5,
                              topn = 5,
                              region = "Americas",
                              pop_type =  c("REF", "ASY", "OIP") ){
  
  # library(tidyverse)
  
  thisyear <- year
  baseline <- thisyear -lag
  data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
    filter(Population.type  %in% pop_type)  %>%
    filter(Year == baseline | Year == thisyear) %>%
    mutate( Year = case_when(
      Year == thisyear ~ paste("thisyear"),
      Year == baseline ~ paste("baseline") )) %>%
    filter(UNHCRBureau == region) %>%
    group_by( CountryAsylumName, Year) %>%
    summarise(Value2 = sum(Value) )  %>%
    select(CountryAsylumName, Year, Value2) %>% 
  mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
        CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
        CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) %>% 
   # mutate(Year = paste0("year_",Year )) %>%
    spread(Year, Value2) %>%
    mutate(gap =  baseline - thisyear   ) %>%
    arrange(desc(gap)) %>%
    head(topn) %>%
    gather(key = Year, 
           value = Value2,
           -CountryAsylumName,
           -gap) %>%
    mutate( Year = case_when(
                    Year == "thisyear" ~ paste(thisyear),
                    Year == "baseline" ~ paste(baseline) )  )
  
 p <- ggplot(data, 
       aes(x = reorder(CountryAsylumName, gap),
           y = Value2, 
          fill = as.factor(Year))) +
  
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0, size = 1, colour = "#333333") +
  scale_fill_manual(values = c("#0072bc", "#FAAB18")) +
  labs(title = "Biggest Decrease of Population",
       subtitle = paste0( topn, " Biggest change in Refugee Population, ",region, " " ,  baseline," - ",thisyear), 
       x="", y ="",
       caption = "Source: UNHCR.org/refugee-statistics") +
  scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()))+ ## Format axis number
  theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
  
  return(p)
    
}
```
  
```{r example-plot_reg_decrease}
plot_reg_decrease(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Americas",
                  pop_type = c("REF", "ASY", "OIP"))
```
  
```{r tests-plot_reg_decrease}
#test_that("plot_reg_decrease works", {   expect_true(inherits(plot_reg_decrease, "function")) })
```
  
    
## Plot Biggest increase in Refugee Population 
    
```{r function-plot_reg_increase}
#' Plot Biggest Increase in Refugee Population
#' 
#' 

#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param topn how many top countries to show..
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom ggalt geom_dumbbell
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_reg_increase <- function(  year = 2021,
                              lag = 5,
                              topn = 5,
                              region = "Americas",
                              pop_type =  c("REF", "ASY", "OIP") ){
  
  # library(tidyverse)
  
  thisyear <- year
  baseline <- thisyear -lag
  data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
    filter(Population.type  %in% pop_type)  %>%
    filter(Year == baseline | Year == thisyear) %>%
    mutate( Year = case_when(
      Year == thisyear ~ paste("thisyear"),
      Year == baseline ~ paste("baseline") )) %>%
    filter(UNHCRBureau == region) %>%
    group_by( CountryAsylumName, Year) %>%
    summarise(Value2 = sum(Value) )  %>%
    select(CountryAsylumName, Year, Value2) %>% 
    mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
        CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
        CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) %>% 
   # mutate(Year = paste0("year_",Year )) %>%
    spread(Year, Value2) %>%
    mutate(gap =   thisyear -baseline  ) %>%
    arrange(desc(gap)) %>%
    head(topn) 
  
 p <- ggplot(data, aes(x = baseline , 
                       xend = thisyear,
                       y = reorder(CountryAsylumName, gap),
                       group = CountryAsylumName)) + 
  ggalt::geom_dumbbell(colour = "#dddddd",
                size = 3,
                colour_x = "#0072bc",
                colour_xend = "#FAAB18") + 
  labs(title = paste0("Where did Refugee Population increased in ", region , "?"),
       subtitle = paste0("Biggest increase in Refugee Population, ", baseline," - ",thisyear),
       x="", y ="",
       caption = "Source: UNHCR.org/refugee-statistics") +
  scale_x_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()))+ ## Format axis number
  theme_unhcr(font_size = 14)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
 
 return(p)
    
}
```
  
```{r example-plot_reg_increase}
plot_reg_increase(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Americas",
                  pop_type = c("REF", "ASY", "OIP"))

plot_reg_increase(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Asia",
                  pop_type = c("REF", "ASY", "OIP"))
```
  
```{r tests-plot_reg_increase}
#test_that("plot_reg_increase works", {   expect_true(inherits(plot_reg_increase, "function")) })
```
  

## Proportion of the population who are refugees, by country of origin  (SDG indicator 10.7.4 ) 

    
```{r function-plot_reg_prop_origin}
#' Proportion of the population who are refugees, by country of origin 
#' 
#' The proportion of a country???s population who become refugees is SDG indicator 10.7.4 
#' it consistutes is a useful way to identify the countries of origin producing the most refugees relative to their number of inhabitants.
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom stringr str_replace               
#' @importFrom wbstats wb           
#' @importFrom forcats fct_reorder    
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @return a ggplot2 object
#' 
#' @export
 
plot_reg_prop_origin <- function(year = 2022,  region = "Americas"){
  
  

  wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL", "NY.GDP.MKTP.CD", "NY.GDP.PCAP.CD", "NY.GNP.PCAP.CD"),     
               startdate = 1990, 
               enddate = 2022, 
               return_wide = TRUE)
      # Renaming variables for further matching
      names(wb_data)[1] <- "iso3c"
      names(wb_data)[2] <- "Year"
      wb_data$Year <- as.numeric(wb_data$Year)
  
  
  departed <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryOriginCode" = "iso_3")) %>% 
    dplyr::filter(Population.type  %in% c("REF","ASY","OIP") & 
           Year ==  year &
           UNHCRBureau  == region #&
           #!(is.na(UNHCRBureau))
           ) |>
    dplyr::group_by(CountryOriginName, CountryOriginCode) |>
    dplyr::summarise(Value2 = sum(Value) )  |>
    #mutate( value3 =  format_si(Value2))|>
    dplyr::mutate(CountryOriginName = stringr::str_replace(CountryOriginName, 
                                                           " \\(Bolivarian Republic of\\)", "")) |>
    
    ## Now merge with WB Data 
    dplyr::left_join(wb_data |> 
                       dplyr::select("SP.POP.TOTL","iso3c", "Year")|>
                       dplyr::filter(Year ==  year-1), 
                     by = c(  "CountryOriginCode" = "iso3c"    ))|>  
    dplyr::mutate(ref.part = round(Value2/(SP.POP.TOTL+Value2),4)  ) |>
    dplyr::arrange(desc(ref.part))|>
    head(10)  
  
p <- ggplot(departed,
                 aes( x= ref.part, forcats::fct_reorder(CountryOriginName, ref.part))) +
  
   geom_col(fill = "#0072BC") +
  
  # geom_col( fill = ifelse(departed$CountryOriginCode %in% c("VEN"), "#0072BC", "#CCCCCC")) +
  
  geom_label(aes(label = scales::label_percent( accuracy = .1)(ref.part) ),
             color = "black", hjust = "inward") +
  scale_x_continuous(labels = scales::label_percent(accuracy = .1)) +
  labs(x = NULL, 
       y = NULL,
       title = stringr::str_wrap(paste0("Number of refugees, asylum seekers & displaced across borders by country of origin in", region), 60),
       subtitle =    stringr::str_wrap( "Top 10 Countries, as a proportion of the national population of that country of origin (SDG indicator 10.7.4)", 80),
         caption = stringr::str_wrap("Source: UNHCR.org/refugee-statistics. \n Total count of population who have been recognized as refugees as a proportion of the total population of their country of origin, expressed per 100,000 population. Refugees refers to persons recognized by the Government and/or UNHCR, or those in a refugee-like situation.  Population refers to total resident population in a given country in a given year."), 100) +
  
     
  unhcrthemes::theme_unhcr(grid = "X", 
              axis = "y", 
              axis_title = "x",
              font_size = 14)  

return(p)
    
}
```
  
```{r example-plot_reg_prop_origin}
plot_reg_prop_origin(year = 2022,  region = "Americas")
```
  
```{r tests-plot_reg_prop_origin}
# test_that("plot_reg_prop_origin works", {   expect_true(inherits(plot_reg_prop_origin, "function")) })
```
  
 

## Decision on Refugee Status Determination

```{r function-plot_reg_rsd}
#' Plot Chart on Refugee Status Determination
#' 
#' Show the main host and origin countries based on number of decisions
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param measure this can be either:
#'            * Recognized  
#'            * ComplementaryProtection  
#'            * TotalDecided 
#'            * RefugeeRecognitionRate 
#'            * TotalRecognitionRate
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual
#'              scale_colour_manual 
#'             geom_text geom_line
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom stringr str_replace  
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty pretty_breaks
#' @importFrom patchwork plot_annotation
#' @importFrom unhcrthemes theme_unhcr unhcr_pal
#' 
#' 
#' @return a ggplot2 object
#' 
#' @export
plot_reg_rsd <- function(year = 2022,
                        region,
                        top_n_countries = 10, 
                        measure = "Recognized"){
  
  measurelabel <- dplyr::case_when( measure == "Recognized"  ~ "Recognized Refugee Status Decisions", 
                       measure == "ComplementaryProtection"  ~ "Complementary Protection Decisions",
                       measure == "TotalDecided"  ~ "Total Decision (independently of the outcome)", 
                       measure == "RefugeeRecognitionRate"  ~ "Refugee Recognition Rate", 
                       measure == "TotalRecognitionRate"  ~ "Total Recognition Rate")

topasyl <-  unhcrdatapackage::asylum_decisions %>%
  ## Add reference for the filters
  dplyr::left_join( unhcrdatapackage::reference %>% 
                      select(coa_region = `UNHCRBureau`, iso_3),
                    by = c("CountryAsylumCode" = "iso_3")) %>% 
  filter(coa_region == region & Year == year) %>% 
  
  ## the below is change - DecisionsAveragePersonsPerCase- is just indicative... so no need to use it to m
 # mutate(DecisionsAveragePersonsPerCase = map_dbl(DecisionsAveragePersonsPerCase, ~replace_na(max(as.numeric(.), 1), 1))) %>%
  mutate(DecisionsAveragePersonsPerCase = 1 ) %>%
  group_by(CountryAsylumName) %>% 
  summarize(Recognized = sum(Recognized * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            ComplementaryProtection = sum(ComplementaryProtection * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            TotalDecided = sum(TotalDecided * DecisionsAveragePersonsPerCase, na.rm = TRUE)) %>%
  mutate(RefugeeRecognitionRate = (Recognized ) / TotalDecided,
         TotalRecognitionRate = (Recognized + ComplementaryProtection) / TotalDecided ) %>%
  # filter(TotalDecided  != 0) %>%
  # filter(TotalDecided  > 1000)  %>%
  mutate(CountryAsylumName = str_replace(CountryAsylumName, "United States of America", "USA"))
  
topasyl1 <-  topasyl  %>%
  mutate( measured = .data[[measure]]) %>%
  arrange(desc(measured)) %>%
  head(top_n_countries)  
  
 
topOrigin <-  unhcrdatapackage::asylum_decisions %>%
  ## Add reference for the filters
  dplyr::left_join( unhcrdatapackage::reference %>% 
                      select(coa_region = `UNHCRBureau`, iso_3),  by = c("CountryOriginCode" = "iso_3")) %>% 
  filter(coa_region == region & Year == year) %>% 
  ## the below is change - DecisionsAveragePersonsPerCase- is just indicative... so no need to use it to m
 # mutate(DecisionsAveragePersonsPerCase = map_dbl(DecisionsAveragePersonsPerCase, ~replace_na(max(as.numeric(.), 1), 1))) %>%
  mutate(DecisionsAveragePersonsPerCase = 1 ) %>%
  group_by(CountryOriginName) %>% 
  summarize(Recognized = sum(Recognized * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            ComplementaryProtection = sum(ComplementaryProtection * DecisionsAveragePersonsPerCase, na.rm = TRUE),
            TotalDecided = sum(TotalDecided * DecisionsAveragePersonsPerCase, na.rm = TRUE)) %>%
  mutate(RefugeeRecognitionRate = (Recognized ) / TotalDecided,
         TotalRecognitionRate = (Recognized + ComplementaryProtection) / TotalDecided) %>%
  # filter(TotalDecided  != 0) %>%
  # filter(TotalDecided  > 1000)  %>%
  mutate(CountryOriginName = str_replace(CountryOriginName, " \\(Bolivarian Republic of\\)", ""))

topOrigin1 <-  topOrigin  %>%
  mutate( measured = .data[[measure]])  %>%
  arrange(desc(measured)) %>%
  head(top_n_countries)   
 

rsdasyl <-  ggplot(topasyl1, aes(y = measured, 
             x = reorder(CountryAsylumName, measured))) + 
  
  
  
  scale_y_continuous( label =  scales::label_percent( accuray = 0, suffix = "%") ) + 
  
  
  scale_y_continuous( label =   ifelse( measure %in% c("RefugeeRecognitionRate", "TotalRecognitionRate"), 
                        scales::label_percent( accuray = 0, suffix = "%"),
                        scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()) )
                      ) + ## Format axis number
  #facet_grid(.~ ctry_asy) +  
  geom_bar( stat ="identity", fill = "#0072bc") +
  coord_flip() +
 # geom_hline(yintercept = 0, linewidth = 1.1, colour = "#333333") +
  labs(#title = "Number of RSD application  in 2020",
       subtitle = paste0( "For top ", top_n_countries, " Countries of Asylum"),
       x = " ", 
       y = " "  ) +
  theme_unhcr( grid = "Y",
               axis = "x",  axis_title = "" ,
              font_size = 10) +
  theme(#axis.text.x = element_blank(),
    # legend.position = "none",
    
    panel.grid.major.x = element_line(color = "#cbcbcb"), 
    panel.grid.major.y = element_blank()) ### changing grid line that should appear) 
  
 
rsdorigin <- ggplot(topOrigin1, aes(y = measured, 
             x = reorder(CountryOriginName, measured))) +
  
  
  scale_y_continuous( label =   ifelse( measure %in% c("RefugeeRecognitionRate", "TotalRecognitionRate"), 
                        scales::label_percent( accuray = 0, suffix = "%"),
                        scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()) )
                      ) + ## Format axis number
  
 # scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale())) + ## Format axis number
  #facet_grid(.~ ctry_asy) +  
  geom_bar( stat ="identity", fill = "#0072bc") +
  coord_flip() +
#  geom_hline(yintercept = 0, size = 1.1, colour = "#333333")   +
  labs(#title = "Number of RSD application per country of Origin in 2020",
       subtitle = paste0( "For top ", top_n_countries, " Countries of Origin"),
       x = " ", 
       y = " " ) +
  theme_unhcr( grid = "Y",
               axis = "x",  axis_title = "" ,
              font_size = 10 ) + 
  theme(#axis.text.x = element_blank(),
    # legend.position = "none",
    
    panel.grid.major.x = element_line(color = "#cbcbcb"), 
    panel.grid.major.y = element_blank()) ### changing grid line that should appear) 

 
#joining charts 
requireNamespace("patchwork")
patchworkRSDa <- rsdasyl + rsdorigin
patchworkRSDa1 <- patchworkRSDa +
  #unhcRstyle::unhcr_theme(base_size = 8)  +  ## Insert UNHCR Style
  theme(legend.position = "none") +
  patchwork::plot_annotation(
    title = paste0(measurelabel, " | ", year, ", in ",region),
   # subtitle = ' ',
    caption = 'Source: UNHCR.org/refugee-statistics '
   ## \n Because of different types of procedure, data from the US may \n includes multiple applications per applicants compared to other countries
  )  

  return(patchworkRSDa1)
}
```
  
```{r example-plot_reg_rsd}
plot_reg_rsd(year = 2022,
             region = "Americas" ,
                        top_n_countries = 10, 
                        measure = "Recognized")


plot_reg_rsd(year = 2022,
             region = "Americas" ,
                        top_n_countries = 5, 
                        measure = "ComplementaryProtection")


plot_reg_rsd(year = 2022,
             region = "Americas" ,
                        top_n_countries = 10, 
                        measure = "TotalDecided")


plot_reg_rsd(year = 2022,
             region = "Americas" ,
                        top_n_countries = 10, 
                        measure = "RefugeeRecognitionRate")


plot_reg_rsd(year = 2022,
             region = "Americas" ,
                        top_n_countries = 10, 
                        measure = "TotalRecognitionRate")


# plot_reg_rsd(year = 2022,
#              region = "Europe", 
#                         top_n_countries = 10, 
#                         measure = "Recognized")
```
  
```{r tests-plot_reg_rsd}
# test_that("plot_reg_rsd works", {   expect_true(inherits(plot_reg_rsd, "function")) })
```
  


    
## Plot Evolution of Solutions in the Region

    
```{r function-plot_reg_solution}
#' Plot Solution over time in the region
#' 
#' Description
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param lag Number of year to used as comparison base
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text geom_smooth
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  if_else desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join 
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @importFrom ggrepel geom_label_repel
#' 
#' @return a ggplot2 object
#' 
#' @export
#'  

plot_reg_solution <- function( year = 2022, 
                            region = "Americas",
                            lag = 10){
  
    solution <-  dplyr::left_join( x= unhcrdatapackage::solutions_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryOriginCode" = "iso_3")) %>% 
                dplyr::filter(Solution.type %in% c("NAT","RST","RET" ) & 
                       UNHCRBureau  == region &
                       Year >= (year - lag) ) |>
                 dplyr::group_by(Year, Solution.type, Solution.type.label )|>
                 dplyr::summarise(Value = sum(Value) ) |>
                 dplyr::ungroup() |>
                 dplyr::group_by( Solution.type  )|>
                 dplyr::mutate(label = dplyr::if_else(Year == max(Year), 
                                               as.character(Solution.type.label),
                                               NA_character_))|>
                 dplyr::ungroup() 

#Make plot
p <- ggplot(solution, aes(x = Year, 
                          y = Value, 
                          colour = Solution.type)) + # Adding reference to color
    geom_smooth(se = FALSE, method = "loess", span = .2) +
    scale_x_continuous( breaks = seq(year - lag, year, by = 5) )+ 
    scale_y_continuous( label = scales::label_number(accuracy = 1,   scale_cut = cut_short_scale()))+
    #scale_colour_viridis_d() + ## Add color for each lines based on color-blind friendly palette
    scale_colour_manual( values = c( "NAT" = "#a6cee3",
                                     "RST"  = "#1f78b4",
                                     "RET" = "#b2df8a" )) +
    ## and the chart labels
    labs(title = paste0("Solution for Displacement in ", region) ,
         subtitle = paste0("Evolution in the past ", lag," years"),
         x = "",
         y = "",
         caption = "Source: UNHCR.org/refugee-statistics ") +   
    ggrepel::geom_label_repel(aes(label = label),
                              nudge_x = 1,
                              na.rm = TRUE) +
    unhcrthemes::theme_unhcr(grid = "Y", 
              axis = "x", 
              axis_title = "y",
              font_size = 14,
              legend = FALSE)  
  

 return(p)  

}

```
  
```{r example-plot_reg_solution}
plot_reg_solution(year = 2022, 
                            region = "Americas",
                            lag = 10)
```
  
```{r tests-plot_reg_solution}
# test_that("plot_reg_solution works", {   expect_true(inherits(plot_reg_solution, "function")) })
```
  

## Mapping Population  

    
```{r function-plot_reg_map}
#' Plot a regional map
#' 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param topn how many top countries to show..
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' @param useBertin -Tells if the map should use Bertin 1953 projection - https://visionscarto.net/bertin-projection-1953)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom sf st_transform st_as_sf st_drop_geometry
#' @importFrom rnaturalearth ne_countries
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale label_percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @importFrom wbstats  wb 
#' @importFrom Hmisc cut2
#' 
#' @return a base plot
#' 
#' @export
#' 
plot_reg_map <- function(    year = 2022, 
                            region = "Americas",
                            topn = 5,
                            pop_type =  c("REF", "ASY", "OIP"),
                            projection = "Mercator",
                            maxSymbolsize = .25   ){
 
      
      # Get World Bank data  #############
      wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL",  ## Population total https://data.worldbank.org/indicator/SP.POP.TOTL
                                            "NY.GDP.MKTP.CD", ## GDP current https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
                                            "NY.GDP.PCAP.CD", ## GDP per capita https://data.worldbank.org/indicator/NY.GDP.PCAP.CD 
                                            "NY.GNP.PCAP.CD" ## GNI per capita, Atlas method (current US$) https://data.worldbank.org/indicator/NY.GNP.PCAP.CD
      ),
      startdate = year-1, enddate = year, return_wide = TRUE) 
      # # Renaming variables for further matching
      names(wb_data)[1] <- "CountryAsylumCode"
      names(wb_data)[2] <- "Year"
      wb_data <- wb_data%>%
        filter(Year == year-1) 
      
      ## Get spatial data to add ##########
      mapproject <- ""
      
      listctr <-  unhcrdatapackage::reference |>
        filter(UNHCRBureau == region) |>
        select(iso_3) |>
        pull()
      
      
      
      ## Loading the stat tables ######
      data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                y= unhcrdatapackage::reference, 
                                by = c("CountryAsylumCode" = "iso_3")) %>%
        filter(Population.type  %in% pop_type &
                 Year == year & 
                 UNHCRBureau == region ) %>%
        group_by(Year, CountryAsylumName, CountryAsylumCode, UNHCRBureau,Latitude, Longitude  ) %>%
        summarise(Value = sum(Value) ) %>%
        ungroup()
      
      
      ## Join ########
      data2 <- data %>% 
        left_join(wb_data, 
                  by = c( "CountryAsylumCode")) %>%  
        mutate(ratio_disp_gdp = round( (Value / NY.GDP.MKTP.CD)*100, 4)  )  %>% 
        mutate(ratio_disp_gdpcap = round(  (Value/ NY.GDP.PCAP.CD)*100, 2)  )   %>% 
        mutate(ratio_disp_host = round( (Value/  SP.POP.TOTL)*100 , 2)  )  
      
      ## Get Break https://riatelab.github.io/mapsf/reference/mf_get_breaks.html
      # Discretize the variable
      data2$quintDisp <- Hmisc::cut2(data2$Value, g = 4)
      data2$quintDispGGP <- Hmisc::cut2(data2$ratio_disp_gdp, g = 4) 
      data2$quintDispHost <- Hmisc::cut2(data2$ratio_disp_host, g = 4)
        
      
      #names(data2)
      data2 <- data2 %>%
        sf::st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
      
      
      ## Getting world map for mapping
      world <- rnaturalearth::ne_countries(scale = "small", returnclass = "sf") %>% 
        filter(continent != "Antarctica")  %>%  
        filter(adm0_a3 %in%  listctr) 
      
      ### Need to fix specific case for Asisa... where the proj disperse the country...
      ##  filter(adm0_a3 != "VUT") 
      
      ## Manage Projection... 
      data2 <- data2 %>%  
        # this is the crs from d, which has no EPSG code:
        sf::st_transform(., '+init=epsg:4326')
      
      world <- world %>%  
        # this is the crs from d, which has no EPSG code:
        sf::st_transform(., '+init=epsg:4326')
      #   # this is the crs from d, which has no EPSG code:
      #   #sf::st_transform(., '+init=epsg:4326')
      #   #sf::st_transform(., '+proj=bertin1953 +R=1 0.72 0.73')
      #   #sf::st_transform(., '+proj=bertin1953 +x_0=1000')
      #   sf::st_transform(., '+proj=bertin1953')
      
      
      PopMap <- data2 |> 
                          sf::st_drop_geometry()|> 
                          ungroup() |>
                          arrange( desc (Value)) |> 
                          head(topn) |> 
                          select(Value) 
      
      minPopMap <- PopMap |>   min()
      maxPopMap <- PopMap |>  max()             
      
      
     regionname <- dplyr::case_when( region == "Americas"  ~  "Americas",
                                  region == "Asia"  ~  "Asia & the Pacific",
                                  region == "EastAfrica"  ~  "Eastern Africa",
                                  region =="Europe"  ~  "Europe",
                                  region == "MENA"  ~  "Middle East & North Africa",
                                  region == "SouthAfrica"  ~  "Southern Africa",
                                  region == "WestAfrica"  ~  "Western Africa")          
      
      ## Generate Map   ##################
      #Maps is created here with [MapSF package](https://riatelab.github.io/mapsf/index.html)
      # Select a font already installed on your system !!
      par(family="Lato")
      # set a theme
      mapsfunhcr <- mapsf::mf_theme(bg ="#d4dff2", #  "#E2E7EB",  ## background color --> Used country 
                      # bg = "#cdd2d4", "#faebd7ff",  "#cdd2d4",
                      mar = c(0, 0, 2, 0), ## margins
                      tab = FALSE,  # if TRUE the title is displayed as a 'tab'
                      fg = "#0072BC",  ## foreground color --> for the top title - use UNHCR Blue..
                      pos = "left", # position, one of 'left', 'center', 'right'
                      inner = FALSE, # if TRUE the title is displayed inside the plot area.
                      line = 2, #number of lines used for the title
                      cex = 2.5, #cex of the title
                      #font = "Lato",
                      font = 1 ) #font of the title
      
      
           # map_fun <- function(data, init, theme){
     #      # Initiate a base map
     #      mf_init(x = init, theme = theme)
     #      # always use add = TRUE after mf_init()
     #      mf_shadow(data, col = "grey50", cex = 0.2 , add = TRUE)
     #      mf_map(data, add = TRUE)
     #      mf_title(txt = "Martinique ", fg = "#FFFFFF")
     #      mf_credits(txt = "Credit", bg = "#ffffff80") 
     #      return(invisible(NULL)) 
     #      }
      
      
      ##Initialise the map with a background
      mapsf::mf_init( x = world, theme = mapsfunhcr) 
      # always use add = TRUE after mf_init()
      
      # Plot a shadow
      mapsf::mf_shadow(world, col = "grey50", cex = 0.2 , 
                       add = TRUE)
      
      mapsf::mf_map(world, 
                    lwd = 0.5, 
                    border = "#93A3AB", 
                    col = "#FFFFFF", 
                    add = TRUE)
      
      # Set a layout
      mapsf::mf_title(txt = paste0("Forced Displacement in ",
                                   regionname, " | ", year), fg = "#FFFFFF")
      mapsf::mf_credits(txt = "Source: UNHCR.org/refugee-statistics - A Country is name if it features among the five largest population.\n The boundaries and names shown and the designations used on this map do not imply official endorsment or acceptance by the inited nations", bg = "#ffffff80" ) 
      
      
      ## Proportional Symbol with color based on other
      mapsf::mf_prop_typo( 
        x = data2, # frame to use.. 
        var = c("Value", "quintDispHost"),  ## First value for size, second for color
        inches = maxSymbolsize, # size of the biggest symbol (radius for circles, half width for squares) in inches
        val_max = maxPopMap,  # maximum value used for proportional symbols
        symbol = "circle", ## type of symbol- 'circle' or 'square'
        border = "grey25", ## border color of symbol
        lwd = 1.5, #  border width of symbol
        pal = "Inferno",  ## Color palette  - https://developer.r-project.org/Blog/public/2019/04/01/hcl-based-color-palettes-in-grdevices/
        alpha = .8,  ## if pal is a hcl.colors palette name, the alpha-transparency level
        leg_no_data = "No data", ## When no data
        col_na = "grey",  ## When no data
        leg_pos = c("topright", "bottomright"),  # position of the legend
        leg_title = c("Number of Individuals", "Ratio with Host Community"), # title of the legend
        leg_title_cex = c(.7, .7),  # title font size of the legend
        leg_val_cex = c(.5, .5), # content font size of the legend
        leg_val_rnd = .2, # number of decimal places of the values in the legend
        leg_frame = c(FALSE, FALSE), # add frame around the legend
        add = TRUE
      )
    # labels for a few  countries - https://riatelab.github.io/mapsf/reference/mf_label.html
     mapsf::mf_label(x = data2[data2$Value >= minPopMap,], 
                      var = "CountryAsylumName",  # name(s) of the variable(s) to plot
                      cex = 0.9, #  labels cex
                      col = "black", 
                      font = 3.5,
                      halo = TRUE, # add halo
                      bg = "white",  # halo color
                      r = 0.2,  # width of the halo
                      overlap = FALSE,  # if FALSE, labels are moved so they do not overlap.
                      lines = TRUE) 
     
     return(invisible(NULL))
}
```
  
```{r example-plot_reg_map}
plot_reg_map(  year = 2022,
                            region = "Asia",
                            topn = 5,
                            pop_type =  c("REF", "ASY", "OIP"),
                            projection = "Mercator",
                            maxSymbolsize = .25)


# plot_reg_map(  year = 2022,
#                             region = "WestAfrica",
#                             topn = 5,
#                             pop_type =  c("REF", "ASY", "OIP"),
#                             projection = "Mercator",
#                             maxSymbolsize = .25)

```
  
```{r tests-plot_reg_map}
# test_that("plot_reg_map works", {   expect_true(inherits(plot_reg_map, "function")) })
```
  
 
    
     


--- 

# Report Templates

Templates are re-built notebook that includes all the plotting functions above and are integrated with report parameters. Templates are available both as html report (that can be converted to PDF) and as PowerPoint presentations, all defined from UNHCR standard brand (cf [unhcrdown](https://github.com/vidonne/unhcrdown). The templates are available either for countries or regions.

## Country Factsheet

```{r function-template_CtryFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "Country_Factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2022)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param folder folder within your project where to put the generated report. 
#' Folder will be created if it does not exist
#' 
#' @importFrom unhcrdown paged_simple
#' @importFrom dplyr filter select pull
#' @importFrom rmarkdown render
#' @importFrom here here
#' 
#' @return nothing the file for the report is generated
#' 
#' @export 
#'

template_CtryFactsheet <- function(year = 2022,
                                   country_asylum_iso3c,
                                   folder = "Report") {
  
  ## Create the outfolder if it does not exist
  output_dir <- paste0(getwd(),"/",folder)
  if (!dir.exists(output_dir)) {dir.create(output_dir)}
  
  ctrname <- unhcrdatapackage::reference |>
             dplyr::filter( iso_3 == country_asylum_iso3c) |>
             dplyr::select(ctryname) |>
             dplyr::pull()
  
  rmarkdown::render(
    system.file("rmarkdown/templates/country_factsheet/skeleton/skeleton.Rmd", package = "unhcrdatapackage"),
    output_file = here::here(folder, paste0('StatFactsheetCtr-', country_asylum_iso3c, '-', year, '.html') ),
    params = list(countryname= ctrname,
                  country = country_asylum_iso3c, 
                  year = year)  )
}
  

```

```{r example-template_CtryFactsheet}
## generate for one country
# template_CtryFactsheet(year = 2022, country_asylum_iso3c = "USA",   folder = "Report")

## Generate for a specific region
# region <- "Americas"
# year <- 2022
# library(tidyverse)
# ## get all countries with more than 1000 Reported individuals
# ctr <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long,
#                                 y= unhcrdatapackage::reference,
#                                 by = c("CountryAsylumCode" = "iso_3")) %>%
#         filter(Year == year &
#                 UNHCRBureau == region ) %>%
#         group_by( CountryAsylumName, CountryAsylumCode   ) %>%
#         summarise(Value = sum(Value) ) %>%
#         ungroup() %>%
#         filter( Value  > 1000 )
# 
#   for ( i in (1:nrow(ctr))) {
#     # i <- 1
#     country_asylum_iso3c = as.character(ctr[i ,2 ])
#     cat(paste0(country_asylum_iso3c, "\n"))
#     unhcrdatapackage::template_CtryFactsheet(year = 2022, country_asylum_iso3c = country_asylum_iso3c,   folder = "Report")
#   }
```


## Country Presentation

```{r function-template_CtryPrez}
# usethis::use_rmarkdown_template(
#   template_name = "country_prez",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2022)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country 
#' @param folder folder within your project where to put the generated report. 
#' Folder will be created if it does not exist
#' 
#' @importFrom unhcrdown pptx_slides
#' @importFrom dplyr filter select pull
#' @importFrom rmarkdown render
#' @importFrom here here
#' 
#' @return nothing the file for the report is generated
#' 
#' @export 
#'

template_CtryPrez <- function(year = 2022,
                                   country_asylum_iso3c,   
                              folder = "Report") {
  
  ## Create the outfolder if it does not exist
  output_dir <- paste0(getwd(),"/",folder)
  if (!dir.exists(output_dir)) {dir.create(output_dir)}
  
  ctrname <- unhcrdatapackage::reference |>
             dplyr::filter( iso_3 == country_asylum_iso3c) |>
             dplyr::select(ctryname) |>
             dplyr::pull()
  
  rmarkdown::render(
    system.file("rmarkdown/templates/country_prez/skeleton/skeleton.Rmd", package = "unhcrdatapackage"),
    output_file = here::here(folder, paste0('StatFactsheet-', country_asylum_iso3c, '-', year, '.pptx') ),
    params = list(countryname= ctrname,
                  country = country_asylum_iso3c, 
                  year = year)  )
}

```

```{r example-template_CtryPrez} 
## generate for one country
# unhcrdatapackage::template_CtryPrez(year = 2022, country_asylum_iso3c = "CHL",   folder = "Report")

## Generate for a specific region
# region <- "Americas"
# 
# ## get all countries with more than 1000 Reported individuals
# ctr <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
#                                 y= unhcrdatapackage::reference, 
#                                 by = c("CountryAsylumCode" = "iso_3")) %>%
#         filter(Year == year & 
#                 UNHCRBureau == region ) %>%
#         group_by( CountryAsylumName, CountryAsylumCode   ) %>%
#         summarise(Value = sum(Value) ) %>%
#         ungroup() %>%
#         filter( Value  > 1000 )
#   
#   for ( i in (1:nrow(ctr))) {
#     country_asylum_iso3c = ctr[i ,2 ]
#     template_CtryPrez(year = 2022, country_asylum_iso3c = country_asylum_iso3c,   folder = "Report") 
#   }
```

## Regional Factsheet

```{r function-template_RegFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "regional_factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Bureau that covers all the countrie factsheet to generate
#' @param lag Number of year to used as comparison base#' @param folder folder within your project where to put the generated report. 
#' Folder will be created if it does not exist
#' @importFrom unhcrdown paged_simple
#' @importFrom dplyr filter select pull
#' @importFrom rmarkdown render
#' @importFrom here here
#' 
#' @return nothing the file for the report is generated
#' 
#' @export 
#'

template_RegFactsheet <- function(year = 2022,
                                 region = "Americas",
                                 lag = 10,   
                                 folder = "Report") {
  
  ## Create the outfolder if it does not exist
  output_dir <- paste0(getwd(),"/",folder)
  if (!dir.exists(output_dir)) {dir.create(output_dir)}
  
  regionname <- dplyr::case_when( region == "Americas"  ~  "Americas",
                                  region == "Asia"  ~  "Asia & the Pacific",
                                  region == "EastAfrica"  ~  "Eastern Africa",
                                  region =="Europe"  ~  "Europe",
                                  region == "MENA"  ~  "Middle East & North Africa",
                                  region == "SouthAfrica"  ~  "Southern Africa",
                                  region == "WestAfrica"  ~  "Western Africa")
  
  rmarkdown::render(
    system.file("rmarkdown/templates/regional_factsheet/skeleton/skeleton.Rmd", package = "unhcrdatapackage"),
    output_file = here::here(folder, paste0('StatFactsheet-',  region, '-', year, '.html') ),
    params = list(region=region,
                  regionname = regionname,
                  year = year,
                  lag = lag)  )
}

```

```{r example-template_RegFactsheet}

# template_RegFactsheet(year = 2022, region = "Europe", lag = 10,   folder = "Report")

## We can also generate all factsheets in a loop for 2022

# region <-  unhcrdatapackage::reference |>
#   dplyr::distinct(UNHCRBureau) |>
#   dplyr::filter(!(is.na(UNHCRBureau))) |>
#   dplyr::pull()
# 
# for( reg in region) {
#   unhcrdatapackage::template_RegFactsheet(year = 2022, 
#                         region = reg, lag = 10,   folder = "Report")
# }



```

## Regional Presentation

```{r function-template_RegPrez}
# usethis::use_rmarkdown_template(
#   template_name = "regional_prez",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Region",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param region Bureau that covers all the countrie factsheet to generate
#' @param lag Number of year to used as comparison base
#' 
#' @param folder folder within your project where to put the generated report. 
#' Folder will be created if it does not exist
#' 
#' @importFrom unhcrdown pptx_slides
#' @importFrom dplyr filter select pull
#' @importFrom rmarkdown render
#' @importFrom here here
#' 
#' 
#' @return nothing the file for the report is generated
#' 
#' @export 
#'

template_RegPrez <- function(year = 2022,
                             region = "Americas",
                             lag = 10,
                             folder = "Report") {
  
  ## Create the outfolder if it does not exist
  output_dir <- paste0(getwd(),"/",folder)
  if (!dir.exists(output_dir)) {dir.create(output_dir)}
  
  regionname <- dplyr::case_when( region == "Americas"  ~  "Americas",
                                  region == "Asia"  ~  "Asia & the Pacific",
                                  region == "EastAfrica"  ~  "Eastern Africa",
                                  region =="Europe"  ~  "Europe",
                                  region == "MENA"  ~  "Middle East & North Africa",
                                  region == "SouthAfrica"  ~  "Southern Africa",
                                  region == "WestAfrica"  ~  "Western Africa")
  rmarkdown::render(
    system.file("rmarkdown/templates/regional_prez/skeleton/skeleton.Rmd", package = "unhcrdatapackage"),
    output_file = here::here(folder, paste0('StatFactsheet-', region, '-', year, '.pptx') ),
    params = list(region=region, 
                  regionname = regionname,
                  year = year,
                  lag = lag)  )
 
}

```

```{r example-template_RegPrez}
# template_RegPrez(year = 2022, region = "Americas", lag = 10,   folder = "Report")

# # Generate for a specific region
# region <- "Americas"
# year <- 2022
# library(tidyverse)
# ## get all countries with more than 1000 Reported individuals
# ctr <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long,
#                                 y= unhcrdatapackage::reference,
#                                 by = c("CountryAsylumCode" = "iso_3")) %>%
#         filter(Year == year &
#                 UNHCRBureau == region ) %>%
#         group_by( CountryAsylumName, CountryAsylumCode   ) %>%
#         summarise(Value = sum(Value) ) %>%
#         ungroup() %>%
#         filter( Value  > 1000 )
# 
#   for ( i in (1:nrow(ctr))) {
#     # i <- 1
#     country_asylum_iso3c = as.character(ctr[i ,2 ])
#     cat(paste0(country_asylum_iso3c, "\n"))
#     unhcrdatapackage::template_CtryPrez(year = 2022, country_asylum_iso3c = country_asylum_iso3c,   folder = "Report")
#   }
```

# Update Dataset
    
```{r function-update_dataset}
#' Update the data on the package
#' 
#' The function pull the data from https://data.humdata.org/dataset/unhcr-population-data-for-world and do a few adjustement before inserting them in the package
#' 
#' @importFrom ckanr   ckanr_setup  package_search
#' @importFrom purrr  pluck  walk
#' @importFrom readr read_csv
#' @importFrom fs path path_file
#' @importFrom here here
#' @importFrom plyr rename
#' @importFrom reshape2 melt
#' @importFrom sinew makeOxygen
#' @importFrom tools resaveRdaFiles
#' 
#' @return nothing just refresh the data .rda
#' 
#' @export
update_dataset <- function(){
  


    ckanr::ckanr_setup("https://data.humdata.org")
    
    ckanr::package_search("name:unhcr-population-data-for-world", as = "table") %>% 
      purrr::pluck("results", "resources", 1, "url") %>% 
      purrr::walk(~ckanr::ckan_fetch(., store = "disk", path = fs::path("data-raw", fs::path_file(.))))
    
    read_sans_hxl <- function(file, ...) {
      hdrs <- readr::read_csv(file, n_max = 0) %>% names()
      
      readr::read_csv(file, col_names = hdrs, skip = 2, ...)
    }



    ## Displaced ##########
    cat(paste0("Reading end_year_population_totals_residing_world \n"))
    end_year_population_totals <- read_sans_hxl(file =  here::here("data-raw","end_year_population_totals_residing_world.csv"))
    
    
    # Rename column to have proper Variable names
    end_year_population_totals <- plyr::rename(end_year_population_totals, c("Country of Origin Code"="CountryOriginCode",
                                           "Country of Asylum Code"="CountryAsylumCode", 
                                           "Country of Origin Name"="CountryOriginName",
                                           "Country of Asylum Name"="CountryAsylumName", 
                                           "Refugees"="REF", 
                                           "Internally displaced persons"="IDP", 
                                           "Asylum seekers"="ASY",
                                           "Others of concern to UNHCR"="OOC",
                                           "Stateless Persons"="STA",    
                                          #  "Venezuelans Displaced Abroad"="VDA"
                                           "Host community" = "HCO",
                                           "Other people in need of international protection"="OIP"))
    cat(names(end_year_population_totals))
    
    sinew::makeOxygen(end_year_population_totals, add_fields = "source")
    
    save(end_year_population_totals, file =  here::here("data","end_year_population_totals.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","end_year_population_totals.RData"),compress="bzip2")
    
    cat(paste0("Saving end_year_population_totals_residing_world \n"))
     
    
    
    
    ## Create a long format for the dataset
    
    end_year_population_totals_long <- reshape2::melt(end_year_population_totals,
                                               # ID variables - all the variables to keep but not split apart on
                                               id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                               # The source columns
                                               measure.vars=c("REF","IDP", "ASY","OOC","STA","OIP","HCO"),
                                               # Name of the destination column that will identify the original
                                               # column that the measurement came from
                                               variable.name="Population.type",
                                               value.name="Value")
    
    end_year_population_totals_long <- end_year_population_totals_long[end_year_population_totals_long$Value > 0, ]
    
    end_year_population_totals_long$Population.type.label <- ""
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="IDP"] <- "Internally displaced persons"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern to UNHCR"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OIP"] <- "Other people in need of international protection"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
    end_year_population_totals_long$Population.type.label.short <- ""
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="IDP"] <- "IDPs"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OIP"] <- "In need of int. protect."
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
      
    save(end_year_population_totals_long, file =  here::here("data","end_year_population_totals_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","end_year_population_totals_long.RData"),compress="xz") 
    
    cat(paste0("Saving long format for  end_year_population_totals_residing_world \n"))
    
    
    ## Solutions ##########
    
    solutions_residing <- read_sans_hxl(file =  here::here("data-raw","solutions_residing_world.csv"))
    
    cat(paste0("Reading solutions_residing_world \n"))
    
    sinew::makeOxygen(solutions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    solutions <- plyr::rename(solutions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                                             "Country of Origin Name"="CountryOriginName",
                                                                             "Country of Asylum Name"="CountryAsylumName", 
                                                                             "Resettlement arrivals"="RST",
                                                                             "Refugee returns"="RET",
                                                                             "Naturalisation"="NAT",
                                                                             "IDP returns"="RDP" ))
    
    save(solutions, file =  here::here("data","solutions.RData"))
    sinew::makeOxygen(solutions, add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions.RData"),compress="bzip2")
    
    cat(paste0("Saving solutions_residing_world \n"))
    
    solutions_long <- reshape2::melt(solutions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                                      # The source columns
                                                      measure.vars=c("NAT","RST", "RET","RDP"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Solution.type",
                                                      value.name="Value")
    
    solutions_long <- solutions_long[solutions_long$Value > 0, ]
    
    
    solutions_long$Solution.type.label <- ""
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RST"] <- "Resettlement arrivals"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="NAT"] <- "Naturalisation"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RET"] <- "Refugee returns"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RDP"] <- "IDP returns"
    
    save(solutions_long , file =  here::here("data","solutions_long.RData"))
    sinew::makeOxygen(solutions_long , add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions_long.RData"),compress="xz")
    
    cat(paste0("Saving long format for solutions_residing_world \n"))
    
    ## Demographics ##########
    
    demographics_residing <- read_sans_hxl(file =  here::here("data-raw","demographics_residing_world.csv"))
    
    cat(paste0("Reading demographics_residing_world \n"))
    #names(demographics_residing)
    
    sinew::makeOxygen(demographics_residing, add_fields = "source")
    # Rename column to have proper Variable names
    demographics <- plyr::rename(demographics_residing, c("Country of Origin Code"="CountryOriginCode",
                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                             "Country of Origin Name"="CountryOriginName",
                                                             "Country of Asylum Name"="CountryAsylumName",  
                                                             "Population Type"= "Population.type",
                                                             "Female 0-4"="Female04", 
                                                             "Female 5-11"="Female511", 
                                                             "Female 12-17"="Female1217", 
                                                             "Female 18-59"="Female1859",
                                                             "Female 60 or more"="Female60ormore",
                                                             "Female Unknown"="FemaleUnknown",
                                                             "Female Total"="FemaleTotal", 
                                                             "Male 0-4"="Male04", 
                                                             "Male 5-11"="Male511", 
                                                             "Male 12-17"="Male1217", 
                                                             "Male 18-59"="Male1859",
                                                             "Male 60 or more"="Male60ormore",
                                                             "Male Unknown"="MaleUnknown",
                                                             "Male Total"="MaleTotal")
                                                             )
    
    
    #names(demographics)
    
    demographics$Population.type.label <- ""
    demographics$Population.type.label[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label[demographics$Population.type=="IDP"] <- "Internally displaced persons"
    demographics$Population.type.label[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label[demographics$Population.type=="OOC"] <- "Others of concern to UNHCR"
    demographics$Population.type.label[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label[demographics$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    demographics$Population.type.label[demographics$Population.type=="OIP"] <- "Other people in need of international protection"
    demographics$Population.type.label[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label[demographics$Population.type=="RDP"] <- "IDP returns"
    
    demographics$Population.type.label.short <- ""
    demographics$Population.type.label.short[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label.short[demographics$Population.type=="IDP"] <- "IDPs"
    demographics$Population.type.label.short[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label.short[demographics$Population.type=="OOC"] <- "Others of Concern"
    demographics$Population.type.label.short[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label.short[demographics$Population.type=="VDA"] <- "Venezuelans Abroad"
    demographics$Population.type.label.short[demographics$Population.type=="OIP"] <- "In need of int. protect."
    demographics$Population.type.label.short[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label.short[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label.short[demographics$Population.type=="RDP"] <- "IDP returns"
    
    # names(demographics)
    # table(demographics$location, useNA = "ifany")
    # table(demographics$urbanRural, useNA = "ifany")
    # table(demographics$accommodationType, useNA = "ifany")
    # table(demographics$Population.type.label.short, useNA = "ifany")
    
    save(demographics, file =  here::here("data","demographics.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","demographics.RData"),compress="bzip2")
    
    cat(paste0("Saving demographics_residing_world \n"))
    
    ## RSD Application ########## 
    asylum_applications_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_applications_residing_world.csv"))
    
    cat(paste0("Reading asylum_applications_residing_world \n"))
    sinew::makeOxygen(asylum_applications_residing, add_fields = "source")
    
    # Rename column to have proper Variable names
    asylum_applications <- plyr::rename(asylum_applications_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                        "Country of Asylum Code"="CountryAsylumCode", 
                                                                        "Country of Origin Name"="CountryOriginName",
                                                                        "Country of Asylum Name"="CountryAsylumName", 
                                                                        "Procedure Type"="ProcedureType",                      
                                                                        "Procedure Name"="ProcedureName",                      
                                                                        "Application Type Code"="ApplicationTypeCode",               
                                                                        "Application Type"="ApplicationType",                    
                                                                        "Application Data Type"="ApplicationDataType",               
                                                                        "Application Data"="ApplicationData",                    
                                                                        "Application Average Persons Per Case"="ApplicationAveragePersonsPerCase",
                                                                        "Number of Applications"="NumberApplications" 
    )
    )
    
    asylum_applications$ApplicationType[asylum_applications$ApplicationTypeCode == "V"] <- "Various"
    asylum_applications$ApplicationTypeCode[asylum_applications$ApplicationType == "New and appeal"] <- "NA"
    
    #View(unique(asylum_applications[ ,c("ApplicationTypeCode","ApplicationType")]))
    
    # View(unique(asylum_applications[ ,c("ProcedureType",  "ProcedureName")]))
    # 
    # View(unique(asylum_applications[ ,c("ApplicationDataType","ApplicationData")]))
    
    save(asylum_applications, file =  here::here("data","asylum_applications.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_applications.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_applications_residing_world \n"))
    
    ## RSD Decision ##########
    asylum_decisions_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_decisions_residing_world.csv"))
    
    cat(paste0("Reading asylum_decisions_residing_world \n"))
    
    sinew::makeOxygen(asylum_decisions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    asylum_decisions <- plyr::rename(asylum_decisions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                   "Country of Asylum Code"="CountryAsylumCode", 
                                                                   "Country of Origin Name"="CountryOriginName",
                                                                   "Country of Asylum Name"="CountryAsylumName", 
                                                                   "Procedure Type"="ProcedureType",                    
                                                                   "Procedure Name"="ProcedureName",                    
                                                                   "Decision Type Code"="DecisionTypeCode",                
                                                                   "Decision Data Type"="DecisionDataType",                
                                                                   "Decision Data"="DecisionData",                     
                                                                   "Decisions Average Persons Per Case"= "DecisionsAveragePersonsPerCase",
                                                                   "Complementary Protection"="ComplementaryProtection",          
                                                                   "Otherwise Closed" ="OtherwiseClosed",                
                                                                   "Total Decided" = "TotalDecided"
                                                                   )
    )
    
    
    # View(unique(asylum_decisions[ ,c("ProcedureType",  "ProcedureName")]))
    # View(unique(asylum_decisions[ ,c("DecisionTypeCode")]))
    
    asylum_decisions$DecisionTypeName <- ""
    asylum_decisions$DecisionTypeCode[is.na(asylum_decisions$DecisionTypeCode) ] <- "NA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FI"] <- "First instance"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "AR"] <- "Re-opened/repeat"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FA"] <- "First instance and appeal"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "BL"] <- "BL"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "NA"] <- "New applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "RA"] <- "Repeat/reopened applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "CA"] <- "CA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "EO"] <- "US Executive Office of Immigration Review"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "IN"] <- "US Citizenship and Immigration Services"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TR"] <- "TR"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "JR"] <- "Judicial Review "
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "SP"] <- "Subsidiary protection"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TA"] <- "Temporary asylum"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TP"] <- "Temporary Protection" 
    
    #View(unique(asylum_decisions[ ,c("DecisionTypeCode","DecisionTypeName")])) 
    sinew::makeOxygen(asylum_decisions, add_fields = "source")
    save(asylum_decisions, file =  here::here("data","asylum_decisions.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_decisions_residing_world \n"))
    
    ## RDS Decision Long format ########
    
    #names(asylum_decisions)
    
    asylum_decisions_long <- reshape2::melt(asylum_decisions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode",
                                                                "CountryOriginName","CountryAsylumName",
                                                                "ProcedureType",  "ProcedureName",
                                                                "DecisionTypeCode","DecisionTypeName",
                                                                "DecisionData","DecisionsAveragePersonsPerCase"),
                                                      # The source columns
                                                      measure.vars=c("Recognized","ComplementaryProtection","OtherwiseClosed","Rejected"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Decision.output",
                                                      value.name="Value")
    
    asylum_decisions_long <- asylum_decisions_long[asylum_decisions_long$Value > 0, ]
    
    sinew::makeOxygen(asylum_decisions_long, add_fields = "source")
    save(asylum_decisions_long, file =  here::here("data","asylum_decisions_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions_long.RData"),compress="xz")  
    
    cat(paste0("Saving long format for asylum_decisions_residing_world \n"))
}
```
  
```{r example-update_dataset}
#update_dataset()
```
  
```{r tests-update_dataset}
#test_that("update_dataset works", {  expect_true(inherits(update_dataset, "function")) })
```
  

# Refresh package

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library", overwrite = 'yes')
pkgdown::build_site()
```

