---
title: "All Plotting functions"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
knitr::opts_chunk$set(
                      comment = "#>",
                      message=FALSE, 
                      warning=FALSE,
                      #fig.retina = 2, 
                      fig.width = 8,
                      fig.asp = 0.618,
                     # fig.align = "center",
                     # dev = "ragg_png",
                      out.width = "90%"
)
unlink(".RData")
library(testthat)
library(ggplot2)
library(unhcrthemes)
# library(extrafont) 
# font_import()
# loadfonts()
# font_install('fontcm')
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```




# Country Questions

## Plot Population type per year

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-plot_ctr_population_type_per_year}
#' Graph of population type per year
#'
#' @param start_year Numeric value of first year  
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#'
#' @export
#'
#'

plot_ctr_population_type_per_year <- function(start_year = 2015,
                                     country_asylum_iso3c = country_asylum_iso3c,
                                     pop_type = Population.type
                                     ) {
  



  cols_poptype <- c("Asylum seekers" = "#18375F",
                    "Refugees" = "#0072BC",
                    #"Venezuelans Displaced Abroad" = "#EF4A60", 
                    "Other people in need of international protection" = "#EF4A60", 
                    "Others of Concern to UNHCR" = "#999999",
                    "Internally displaced persons" = "#00B398",
                    "Stateless Persons" = "#E1CC0D")
  
  
  df <- unhcrdatapackage::end_year_population_totals_long  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year >= start_year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
                  Population.type %in% pop_type #### Parameter
    )  |>  
    group_by(Year, CountryAsylumName, Population.type.label)  |> 
    summarise(Value = sum(Value, na.rm = TRUE)) |> 
    ungroup()
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()
  
  year_breaks <- diff(range(df$Year)) + 1 
  
  p <- ggplot(df) +
    geom_col(aes(x = Year, y = Value, fill = Population.type.label),
             width = 0.7) +
    geom_text(aes(x = Year, 
                  y = Value, 
                  color = Population.type.label, 
                  label = label_number( accuracy = 1,
                                   scale_cut = cut_short_scale())(Value)),
              position = position_stack(vjust = 0.5),
              show.legend = FALSE,
              size = 5) +
    scale_color_manual(values = c("#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF")) +
    scale_fill_manual(values = cols_poptype,
                      drop = TRUE,
                      limits = force) +
    scale_x_continuous(breaks = scales::breaks_pretty(n = year_breaks)) +
    scale_y_continuous(expand = expansion(c(0, 0.1))) +
    labs(title = paste0(CountryAsylum_name_text, ": Population type per year"), 
         subtitle = "Number of people (thousand)",
         caption = "Source: UNHCR Refugee Data Finder") +
    theme_unhcr(grid = FALSE, axis = "x", axis_title = FALSE, axis_text = "x") +
    stat_summary(fun = sum, aes(x = Year,
                                y = Value, 
                                label = scales::label_number( accuracy = 1,
                                                       scale_cut = cut_short_scale())(..y..), 
                                group = Year), 
                 geom = "text", size = 5,
                 vjust = -0.5) +
    theme(legend.direction = "vertical",
          legend.key.size = unit(0.8, 'cm'),
          text = element_text(size = 20),
          plot.subtitle=element_text(size=19),
          plot.title = element_text(size=23),
          plot.caption = element_text(size=13))
  
  return(p) # print(p)
  }
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples-plot_ctr_population_type_per_year, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_per_year(start_year = 2016,
                         country_asylum_iso3c = "PAN",
                          pop_type = c("REF", 
                                       "ASY", 
                                       "OIP", 
                                       "OOC",
                                       "STA",
                                       "IDP" )
                  )
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-plot_ctr_population_type_per_year}


```



## Plot Main country of origin  in one specific country - Absolute value


```{r function-plot_ctr_population_type_abs}
#' Main country of origin - Absolute value
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY,   OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_population_type_abs <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                       #VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <- 
  unhcrdatapackage::end_year_population_totals  |> 
  filter(CountryAsylumCode != "UKN",
                !is.na(CountryAsylumCode),
                (Year == year | Year == year -1),  #### Parameter
                CountryAsylumCode == country_asylum_iso3c, #### Parameter
  )  |>  
  select(Year, CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
  group_by(Year, CountryAsylumName, CountryOriginName) |>
  filter(!!sym(pop_type) != 0) |>
  mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
  ungroup() |>
  group_by(CountryAsylumName, CountryOriginName) |> 
  arrange(Year) |>
  mutate(diff_pop_type_value = percent(((pop_type_value-lag(pop_type_value))/lag(pop_type_value)),
                                                      accuracy = 1.1,
                                                      trim = FALSE
  )) |> 
  ungroup() |>
  filter(Year == year) |> 
  mutate(
    origin_data_prot = forcats::fct_lump_n(
      f = CountryOriginName,
      n = top_n_countries,  #### Parameter
      w = pop_type_value,
      other_level = 'Other nationalities',
      ties.method = "last"
    )
  ) |>
  mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                            'Other nationalities'),
                diff_pop_type_value = case_when(origin_data_prot == 'Other nationalities' ~ "",
                                                TRUE ~ diff_pop_type_value)) |>
  group_by(CountryAsylumName, diff_pop_type_value, origin_data_prot) |>
  summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
  ungroup() |> 
  arrange(desc(pop_type_value)) |>
  filter(pop_type_value != 0L) |>
  mutate(
    origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
    origin_data_prot =  suppressWarnings(
      case_when(
        origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                         "Other nationalities",
                                                                         after = 0),
        TRUE ~ origin_data_prot
      )
    ),
    perc = percent(
      pop_type_value / sum(pop_type_value),
      accuracy = 1,
      trim = TRUE
    )
  )

CountryAsylum_name_text <- df |> 
  distinct(CountryAsylumName) |> 
  pull()


p <-  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                           scale_cut = cut_short_scale())(pop_type_value)
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(pop_type_value)),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  geom_text( # positive diff percentage label
    data = subset(df, with(df, !grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.8,
    vjust = 0.5,
    colour = "grey",
    size = 4
  ) +
  geom_text( # negative diff percentage label
    data = subset(df, with(df, grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.5,
    vjust = 0.5,
    colour = "#0472bc",
    size = 4
  ) +
  geom_text( #increase triangle
    data = subset(df, with(df, !grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9650),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0bb498",
    size = 7
  ) +
  geom_text( #decrease triangle
    data = subset(df, with(df, grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9660),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0472bc",
    size = 7
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": Main Countries of origin (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = "Number of people",
       caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
  theme_unhcr(grid = FALSE, axis = "y", axis_title = FALSE, axis_text = "y") +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_abs, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 4,
                    pop_type = "REF"
                    ) 

## Same with 9 top countries and asylum seekers included
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 9,
                    pop_type = "REF"
                    ) 

```

```{r tests-plot_ctr_population_type_abs}

```



## Plot Main country of origin in one specific country - Percentage


```{r function-plot_ctr_population_type_perc}
#' Main country of origin - Percentage
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_population_type_perc <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                      # VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <-  
    unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
    )  |>  
    select(CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
    group_by(CountryAsylumName, CountryOriginName) |>
    filter(!!sym(pop_type) != 0) |>
    mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
    ungroup() |>
    mutate(
      origin_data_prot = forcats::fct_lump_n(
        f = CountryOriginName,
        n = top_n_countries,  #### Parameter
        w = pop_type_value,
        other_level = 'Other nationalities',
        ties.method = "last"
      )
    ) |>
    mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                              'Other nationalities')) |>
    group_by(CountryAsylumName,origin_data_prot) |>
    summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
    ungroup() |> 
    arrange(desc(pop_type_value)) |>
    filter(pop_type_value != 0L) |>
    mutate(
      origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
      origin_data_prot =  suppressWarnings(
        case_when(
          origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                           "Other nationalities",
                                                                           after = 0),
          TRUE ~ origin_data_prot
        )
      ),
      perc = percent(
        pop_type_value / sum(pop_type_value),
        accuracy = 1,
        trim = FALSE
      )
    )
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()



p <- 
  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": Main Countries of origin (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = "Percentage",
       caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
 theme_unhcr(grid = FALSE, axis = "y", axis_title = FALSE, axis_text = "y") +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_perc, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_perc(year = 2021,
                    country_asylum_iso3c = "BRA",
                    top_n_countries = 9,
                    pop_type = "REF"  ) 

plot_ctr_population_type_perc(year = 2021,
                    country_asylum_iso3c = "BRA",
                    top_n_countries = 9,
                    pop_type = "ASY"  ) 
```

```{r tests-plot_ctr_population_type_perc}

```


## Plot Increases and Decreases in Population Groups


```{r function-plot_ctr_diff_in_pop_groups}
#' Increases and Decreases in Population Groups
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer  gather separate spread
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_diff_in_pop_groups <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type
) {



  diff_perc <- function(x){
    x = as.numeric((x - lag(x))/lag(x)) + 0
    
  }
  
  
  df <- unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  (Year == year-1 | Year == year),  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    group_by(Year, CountryAsylumName) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() |> 
    arrange(Year) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName) |> 
    summarise(across(where(is.numeric), 
                                   list(diffabs = diff,
                                        diffperc = diff_perc),
                                   .names = "{.col}_{.fn}")) |> 
    ungroup() |> 
    slice(2) 
  
  df <- replace(df, is.na(df), 0)
  
  df <- df |> 
    tidyr::gather(v, value, REF_diffabs:OIP_diffperc) |> 
    tidyr::separate(v, c("pop_type", "value_type"), sep = "\\_") |> 
    tidyr::spread(key = value_type, value = value) |> 
    mutate(diffper =percent(
      diffperc,
      accuracy = 1,
      trim = FALSE
    ))
  
  
  p <- df |> 
    filter(pop_type %in% pop_type) |>
    ggplot() +
    geom_col(aes(x = pop_type, 
                 y = diffabs,
                 fill = pop_type),
             width = 0.8) +
    scale_fill_manual(
      values = c("ASY" = "#18375F",
                 "REF" = "#0072BC",
                 "OIP" = "#EF4A60", 
                 #"VDA" = "#EF4A60", 
                 "OOC" = "#999999",
                 "IDP" = "#00B398",
                 "STA" = "#E1CC0D"),
      drop= TRUE,
      limits = force,
      guide="none"
    ) +
    scale_x_discrete(labels= c("ASY" = "Asylum seekers",
                               "REF" = "Refugees",
                               #"VDA" = "Venezuelans Displaced\nAbroad", ,
                               "OIP" = "Other people in need\n of international protection", 
                               "OOC" = "Others of Concern\nto UNHCR",
                               "IDP" = "Internally Displaced\nPersons",
                               "STA" = "Stateless Persons"),
                     drop = TRUE,
                     limits = force) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = label_number(accuracy = 1,
                              scale_cut = cut_short_scale())(diffabs) ),
      vjust = -0.5 ,
      colour = "black",
      size = 5
    ) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = -2.0 ,
      colour = "black",
      size = 5
    ) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = label_number(accuracy = 1,
                             scale_cut = cut_short_scale())(diffabs)
      ),
      vjust = 2.7 ,
      colour = "white",
      size = 5
    ) + 
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = 1.2 ,
      colour = "white",
      size = 5
    ) + #################################
  # geom_text(
  #   data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #   aes(
  #     x = pop_type,
  #     y = diffabs,
  #     label = label_number(accuracy = 1,
  #                                  scale_cut = cut_short_scale())(diffabs)
  #   ),
  #   vjust = -2.0 ,
  #   colour = "white",
  #   size = 5
  # )  +
  #   geom_text(
  #     data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #     aes(
  #       x = pop_type,
  #       y = diffabs,
  #       label = diffper
  #     ),
  #     vjust = -0.5 ,
  #     colour = "white",
  #     size = 5
  #   ) +
  geom_text(
    data = subset(df, diffabs < 0/ 1.5),
    aes(
      x = pop_type,
      y = diffabs,
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(diffabs)
    ),
    vjust =  1.2,
    colour = "black",
    size = 5
  ) + 
    geom_text(
      data = subset(df, diffabs < 0  / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = 2.7,
      colour = "black",
      size = 5
    ) +
    geom_hline(yintercept = 0, color = "black") +
    labs(title = paste0(df |> 
                          distinct(CountryAsylumName) |> 
                          pull(), 
                        ": Increases and Decreases in Population Groups | ",
                        year-1,
                        "-",
                        year),
         subtitle = "Number of people and percentage",
         caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency")  + 
    theme_unhcr(grid = FALSE, axis = "x", axis_title = FALSE, axis_text = "x") +
    theme(axis.line.x = element_line(color="white"),
          axis.text.x = element_text(size=10))
  
  return(p) # print(p)
}
```

```{r examples-plot_ctr_diff_in_pop_groups, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_diff_in_pop_groups(year = 2021,
                            country_asylum_iso3c = "USA",
                            pop_type = c("REF", "ASY")
         )

```

```{r tests-plot_ctr_diff_in_pop_groups}

```




## Plot Main Destination from  one specific country 


```{r function-plot_ctr_destination}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_origin_iso3c Character value with the ISO-3 character code of the Country of Origin
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_destination <- function(year = 2021,
                                 country_origin_iso3c = country_origin_iso3c,
                                 pop_type = pop_type) {



  
  
Destination <- left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))  |>
  filter(CountryOriginCode  == country_origin_iso3c  & 
                 Year == year &
                Population.type  %in% as.vector(pop_type)  )  |>  
   mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
         CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
         CountryAsylumName = str_replace(CountryAsylumName, "United States of America", "USA"),
         CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) |> 
   
   group_by( CountryAsylumName) |>
   summarise(DisplacedAcrossBorders = sum(Value) )  |>
   mutate( DisplacedAcrossBordersRound =  ifelse(DisplacedAcrossBorders > 1000, 
                            paste(label_number( accuracy = .1,
                                   scale_cut = cut_short_scale())(DisplacedAcrossBorders)),
                            as.character(DisplacedAcrossBorders) ) ) |>
   arrange(desc(DisplacedAcrossBorders)) |>
   head(10) |>
   filter(DisplacedAcrossBorders >0)

if( nrow(Destination) ==  0 ){
  p <- paste0("There's no recorded countries of destination for ",country_origin_iso3c )
  
} else {


#Make plot
p <- ggplot(Destination, aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), ## Reordering country by Value
                           y = DisplacedAcrossBorders)) +
  geom_bar(stat = "identity", 
           position = "identity", 
           fill = "#0072bc") + # here we configure that it will be bar chart+
## Format axis number
  scale_y_continuous( labels = label_number(scale_cut = cut_short_scale())) + 
  
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data = subset(Destination, DisplacedAcrossBorders < max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              #family = "Lato", 
              size = 4   ) +  

  geom_label( data = subset(Destination, DisplacedAcrossBorders >= max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              # family = "Lato", 
              size = 4   ) +   
  # Add `coord_flip()` to make your vertical bars horizontal:
  coord_flip() + 
  
  ## and the chart labels
  labs(title = paste0("What are the main destinations for Forcibly Displaced People?" ),
       
       subtitle = paste0("Top Destination Countries - Data as of ",year, " for population from ",country_origin_iso3c ), 
       x = "",
       y = "",
       caption = "Data: UNHCR Refugee Population Statistics Database; Visualisation: UnhcrDataPackage.\n Forced Displacement includes Refugees, Asylym Seekers and Other in Need of International Protection.") +
    
  # Style  
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
  
  
  }
  return(p) # print(p)
}

```

```{r examples-plot_ctr_destination, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_destination(year = 2021,
                     country_origin_iso3c = "COL",
                     pop_type = c("REF", "ASY")
         )

```
    
## Plot Tree Map of Categories

```{r function-plot_ctr_treemap}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line 
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_treemap <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {




  datatree <-  unhcrdatapackage::end_year_population_totals_long  |> 
    filter(Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName,  Population.type, 
                    Population.type.label, Population.type.label.short) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() 
  
  p <- ggplot(datatree, 
       aes(area = Value, 
           fill = Population.type,
           label = paste0(round(100*Value/sum(Value),1), 
                          "%\n", 
                          Population.type.label))) +
         treemapify::geom_treemap() +
         treemapify::geom_treemap_text(colour = "white",
                           place = "centre", size = 25) +
         scale_fill_manual( values = c(   "IDP" = "#00B398",
                                         # "VDA"="#EF4A60",
                                          "OIP"="#EF4A60",
                                          "ASY" = "#18375F",
                                          "REF" = "#0072BC",
                                          "OOC" ="#8395b9",
                                          "STA"="#E1CC0D")) +
         
      theme_unhcr(font_size = 12, grid = "Y", axis = "x", axis_title = "y", legend = FALSE) +
         theme(legend.position = "none") +
         ## and the chart labels
         labs(title = paste0("Population of Concern in ", country_asylum_iso3c),
              subtitle = paste0("As of ", year, ", a total of ", format(round(sum(datatree$Value), -3),  big.mark=","), " Individuals"),
              x = "",
              y = "",
              caption = "Source: UNHCR.org/refugee-statistics  ")  

   return(p)
}

```
    
```{r examples-plot_ctr_treemap, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_treemap(year = 2021,
                            country_asylum_iso3c = "USA",
                            pop_type = c("REF", "ASY")
         )

```    
    


## Plot Refugees Age Pyramid

```{r function-plot_ctr_pyramid}
#' Population Pyramid
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace str_detect
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_pyramid <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {



  
  demographics1 <- unhcrdatapackage::demographics |>
                   left_join( unhcrdatapackage::reference |> 
                                       select(UNHCRBureau, iso_3),  
                                     by = c("CountryAsylumCode" = "iso_3")) |> 
                   filter(CountryAsylumCode  == country_asylum_iso3c &
                               Year == year-1 &
                               Population.type  %in% as.vector(pop_type) ) |>
    
                    mutate ( totGen = FemaleTotal +MaleTotal,
                               totbreak = Female04 + Female511 + Female1217 + 
                                          Female1859 + Female60ormore + FemaleUnknown +
                                          Male04 + Male511 + Male1217 + Male1859 +
                                          Male60ormore + MaleUnknown,
                               
                               hasbreak = ifelse(Total - totGen == 0, "yes", "no" ))



if( nrow(demographics1) ==  0 ){
  p <-  paste0("There's no recorded Gender disaggregation for Forcibly Displaced People across Borders in ",country_asylum_iso3c  )
  
} else {

  tot <- format( sum(demographics1$Total) ,  big.mark=",")
  totprop <-   format( round( sum(demographics1$totGen) / 
      sum(demographics1$Total )  *100,1),  big.mark=",")  
  
  if (totprop == 0 ) {
    p <- paste0("There's no recorded Gender disaggregation for all of the ",tot, " persons in", country_asylum_iso3c  )
    
  } else {
    #names(demographics)
    pyramid <-  demographics1[ demographics1$Year == max(demographics1$Year),
                              c(
                                  "Female04",
                                  "Female511",
                                  "Female1217",
                                  "Female1859",
                                  "Female60ormore",
                                  "FemaleUnknown",
                                 # "FemaleTotal",
                                  "Male04",
                                  "Male511",
                                  "Male1217",
                                  "Male1859",
                                  "Male60ormore",
                                  "MaleUnknown"#,
                                 # "MaleTotal"       
                                 )]  
    
    pyramid2 <- data.frame(lapply(pyramid, function(x) { as.numeric( gsub("NA", "0", x)) })) |>
      pivot_longer(
        cols = Female04:MaleUnknown,
        names_to = "Class",
        values_to = "Sum",
        values_drop_na = TRUE
      ) 
    
    pyramid3 <- as.data.frame(aggregate(pyramid2$Sum,
                                              by = list(pyramid2$Class#, pyramid2$REGION_UN
                                                        ),
                                              sum))
    names(pyramid3)[1] <- "Class"
    names(pyramid3)[2] <- "Count"
    
    pyramid3 <- pyramid3 |> 
      mutate(gender = case_when(str_detect(Class, "Male") ~ "Male",
                                str_detect(Class, "Female") ~ "Female")) |> 
      mutate(age = case_when(str_detect(Class, "04") ~ "0-4",
                             str_detect(Class, "511") ~ "5-11",
                             str_detect(Class, "1217") ~ "12-17",
                             str_detect(Class, "1859") ~ "18-59",
                             str_detect(Class, "60") ~ "60+",
                             str_detect(Class, "Unknown") ~ "Unknown")) 
    
    pyramid3$pc <- pyramid3$Count / sum(pyramid3$Count) * 100
    pyramid3$age <- factor(pyramid3$age, levels = c("0-4", "5-11",  "12-17",  "18-59", "60+", "Unknown"))
    
    p <- ggplot(pyramid3, aes(x = age, 
                         fill = gender,
                          y = ifelse(test = gender == "Female",
                                yes = -pc, no = pc)) ) + 
      geom_bar(stat = "identity") +
      geom_label(aes(x = age,
                     y = ifelse(test = gender == "Female",
                                yes = -pc -5 , no = pc),
                    label =  paste0(format(round(pc, 1),  big.mark=","),"%") 
                    ),
                 hjust = 0,
                 vjust = 0.5,
                 colour = "black",
                 fill = NA,
                 label.size = NA,
                # family = "Lato",
                 size = 4) +
      scale_y_continuous(labels = abs, limits = max(pyramid3$pc) * c(-1,1)) +
      labs(title = paste0("Population Pyramid for Forcibly Displaced People" ),
           
           subtitle = paste0("As of ", year, 
                             ", gender disaggregation is available for ", totprop, " % of the ",tot,
                             " individuals in", country_asylum_iso3c),
           x = "", 
           y = "Percent of population",
           caption =  "Data: UNHCR Refugee Population Statistics Database; Visualisation: UnhcrDataPackage.\n Forced Displacement includes Refugees, Asylym Seekers and Other in Need of International Protection.") +
      scale_colour_manual(values = c("#126db4","#01ab91"), # based on Asia Report
                          aesthetics = c("colour", "fill")) +
      coord_flip()+
      theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
      theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
                panel.grid.major.y = element_blank())
    
   
 }
}
  
   return(p)
}
```

    
```{r examples-plot_ctr_pyramid, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_pyramid(year = 2021,
                            country_asylum_iso3c = "VEN",
                            pop_type = c("REF", "ASY")
         )

``` 



## Asylum Processing


    
## Refugee Recognition rate

    
## Refugee Status Determination Application

    
## Refugees accessing durable solutions


## Solution 
    
```{r function-plot_ctr_solution}
#' Plotting solutions within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text guide_axis facet_wrap vars
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'
 
plot_ctr_solution <- function(year = 2021,
                              lag = 10,
                              country_asylum_iso3c = country_asylum_iso3c,
                              pop_type = pop_type){
  
    Solution <- unhcrdatapackage::solutions_long  %>%
                dplyr::left_join(y= unhcrdatapackage::reference, 
                               by = c("CountryAsylumCode" = "iso_3")) %>%
      
              filter(CountryAsylumCode  == country_asylum_iso3c & 
                      Year > (year - lag) &
                      Solution.type.label != "IDP returns" ) %>%
              mutate(Year = as.factor(Year) ) %>%
              group_by(Year, Solution.type.label ) %>%
              summarise(Value2 = sum(Value) )  %>%
              mutate( valabel =  ifelse(Value2 > 1000, 
                                       paste(scales::label_number_si(accuracy = 0.1)(Value2)),
                                       as.character(Value2)) )   

    
    ncat <- ifelse( nlevels(as.factor(Solution$Solution.type.label)) %in% c(2,4), 2,3)
    #levels(as.factor(solutions_long.asy$Solution.type.label))
    Solution$Solution.type.label <- factor(Solution$Solution.type.label,
                                                     levels = c("Naturalisation", 
                                                                "Resettlement arrivals",
                                                                "Refugee returns",
                                                                "IDP returns" )) 



if( nrow(Solution) ==  0 ){
   p <- paste0("There's no recorded solutions in ", country_asylum_iso3c )
  
} else {
  

#Make plot
p <- ggplot(Solution, aes(x = Year, y = Value2  )) + 
  geom_bar(stat = "identity", 
           position = "identity", 
           fill = "#0072bc" ) + # here we configure that it will be bar chart
  scale_y_continuous( label = scales::label_number_si()) + ## Format axis number
  scale_x_discrete(guide = guide_axis(check.overlap = TRUE))+
  #xlim(c(year-lag, year +1)) +
  facet_wrap( vars(Solution.type.label ), ncol = ncat) +
  #geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(panel.grid.major.y  = element_line(color = "#cbcbcb"), 
        panel.grid.major.x  = element_blank(), 
        panel.grid.minor = element_blank()) + ### changing grid line that should appear
  ## and the chart labels
  labs(title = "What are the trends in terms of Solutions?",
       subtitle = paste0("Data for Forcibly Displaced People across Borders as of ", year, " filtered for ", country_asylum_iso3c), 
       x = "",
       y = "",
       caption = "Data: UNHCR Refugee Population Statistics Database; Visualisation: UnhcrDataPackage.\n Forced Displacement includes Refugees, Asylym Seekers and Other in Need of International Protection.")

}
    
return(p)
}
```
  
```{r example-plot_ctr_solution}
plot_ctr_solution(year = 2021,
                  country_asylum_iso3c= "UGA",
                  pop_type = c("REF", "ASY"))
```
  
```{r tests-plot_ctr_solution}
test_that("plot_ctr_solution works", {
  expect_true(inherits(plot_ctr_solution, "function")) 
})
```
  



## Resettlement Trend


## Population origin-destination

    
## Proportion of the population who are refugees, by country of origin

    
## Ratio Refugee Vs Host population

    
## Plot Ratio Refugee Migrant
    
```{r function-plot_ctr_disp_migrant}
#' Plotting ration Refugee/Asylum seekers vs Migrant within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text geom_point scale_size coord_cartesian
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom wbstats  wb 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @importFrom viridis scale_fill_viridis
#' 
#' @export
#'
plot_ctr_disp_migrant <- function(year = 2021,
                              country_asylum_iso3c = country_asylum_iso3c,
                              pop_type = pop_type){
  
  wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL", "NY.GDP.MKTP.CD", "NY.GDP.PCAP.CD", "NY.GNP.PCAP.CD"),
             
               country = c( country_asylum_iso3c )  ,         
               startdate = 1990, 
               enddate = 2020, 
               return_wide = TRUE)
      # Renaming variables for further matching
      names(wb_data)[1] <- "iso_3"
      names(wb_data)[2] <- "Year"
      wb_data$Year <- as.numeric(wb_data$Year)

  
  displaced <- left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                               y= unhcrdatapackage::reference, 
                               by = c("CountryAsylumCode" = "iso_3")) %>%
              filter(Population.type  %in% pop_type) %>%
              filter(CountryAsylumCode == country_asylum_iso3c) %>%
              filter( Year == year ) %>%
              mutate( iso_3 = CountryOriginCode) %>% 
              group_by(Year, iso_3,CountryOriginName, UNHCRBureau, hcr_subregion, INCOME_GRP) %>%
              summarise(Asylum_Refugee_in = sum(Value) )  %>%
              filter( iso_3 != "UKN") %>%
              arrange( desc(Asylum_Refugee_in)) %>%
              head(10)%>%
              as.data.frame()
  
  thiscode <- unhcrdatapackage::reference |>
                filter(iso_3 == country_asylum_iso3c) |>
                 select(M49_code) |>
                 pull()

  migrant <-  left_join( x= unhcrdatapackage::migrants, 
                               y= unhcrdatapackage::reference, 
                               by = c("CountryOriginM49" = "M49_code")) %>%
              filter(CountryDestinationM49 == thiscode) %>%
              group_by(Year, iso_3,CountryOriginName, UNHCRBureau, hcr_subregion, INCOME_GRP) %>%
              summarise(Immigrant = sum(Value) ) %>%
              mutate( shareOrgin = (Immigrant / sum(Immigrant))*100 ) %>%
              filter( Year == 2020 ) %>%
              as.data.frame() %>%
              mutate( Year = as.numeric(Year) ) %>%
              mutate( shareOrgin =  round(Immigrant / sum(Immigrant),3)*100 )

#str(migrant)
#str(displaced)

thismigProfile <-  migrant  %>%
  dplyr::full_join( displaced[ ,c("Asylum_Refugee_in","iso_3" )], by = c("iso_3")) %>%
  dplyr::left_join(  wb_data, by = c("Year","iso_3")) %>%
  ## Calculate a few ration
  mutate( ratioAsylum_Refugee_in = (Asylum_Refugee_in / SP.POP.TOTL)*100,
          ratioImmigrant = (Immigrant / SP.POP.TOTL)*100,
          ratioAsylum_Immigrant = (Asylum_Refugee_in / Immigrant)*100)  %>%
  arrange( desc(Asylum_Refugee_in)) %>%
  head(10)


if( nrow(displaced) ==  0 ){
  p <- paste0("There's no recorded Forcibly Displaced Poeple across Borders in ",thiscountry )
  
} else {

p <- ggplot(thismigProfile,
       aes(x= ratioAsylum_Immigrant, 
           y= shareOrgin, 
           size= Asylum_Refugee_in, 
           fill= INCOME_GRP,
           label = iso_3)) +
  geom_point(alpha=0.5, 
             shape=21, 
             color="black") +
  scale_size(range = c(.1, 24), guide= "none", ## Do not show Legend
             name="# of Forcibly Displaced People") +
  viridis::scale_fill_viridis(discrete=TRUE,
                              name="Country Income Classification") +
  # facet_wrap( vars(Year ), ncol = 2) +
  coord_cartesian(clip = "off") +
  ggrepel::geom_label_repel(box.padding = 0.5,
                            size =4,
                            # max.overlaps = 2 
                            fill = "white", 
                            xlim = c(-Inf, Inf), 
                            ylim = c(-Inf, Inf)) + 
  labs(title = "Share of Forcibly Displaced People within Migrants",
       subtitle = "Per Country of Origin as of 2020. \n The size of the circle represents the number of Refugees & Asylum Seekers ", 
       x = "Ratio Asylum / Immigrant",
       y ="Ratio Country / Total Immigrant",
       caption = "UNDESA Migrant Stock & UNHCR (includes REF +ASY+OIP in calculation) as of 2020.\n Only countries with more than 50K Forcibly Displaced Accorss borders are presented.") +
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(legend.position="bottom", 
        panel.grid.major.y  = element_line(color = "#cbcbcb"), 
        panel.grid.major.x  = element_line(color = "#cbcbcb"), 
        panel.grid.minor = element_blank())   ### changing grid line that should appear
  
}

return(p)
    
}
```
  
```{r example-plot_ctr_disp_migrant}
plot_ctr_disp_migrant(year = 2021,
                    country_asylum_iso3c = "BRA",
                  pop_type = c("REF", "ASY", "OIP") )
```
  
```{r tests-plot_ctr_disp_migrant}
test_that("plot_ctr_disp_migrant works", {
  expect_true(inherits(plot_ctr_disp_migrant, "function")) 
})
```
  
    
    
--- 

# Regional Questions


## Plot Biggest decrease in Refugee Population
 
    
```{r function-plot_reg_decrease}
#' Plot Biggest decrease in Refugee Population
#' 
#' 

#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param topn how many top countries to show..
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom wbstats  wb 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @return plot a ggplot2 object 
#' 
#' @export
plot_reg_decrease <- function(year = 2021,
                              lag = 5,
                              topn = 5,
                              region = "Americas",
                              pop_type =  c("REF", "ASY", "OIP") ){
  
  # library(tidyverse)
  
  thisyear <- year
  baseline <- thisyear -lag
  data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
    filter(Population.type  %in% pop_type)  %>%
    filter(Year == baseline | Year == thisyear) %>%
    mutate( Year = case_when(
      Year == thisyear ~ paste("thisyear"),
      Year == baseline ~ paste("baseline") )) %>%
    filter(UNHCRBureau == region) %>%
    group_by( CountryAsylumName, Year) %>%
    summarise(Value2 = sum(Value) )  %>%
    select(CountryAsylumName, Year, Value2) %>% 
  mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
        CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
        CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) %>% 
   # mutate(Year = paste0("year_",Year )) %>%
    spread(Year, Value2) %>%
    mutate(gap =  baseline - thisyear   ) %>%
    arrange(desc(gap)) %>%
    head(topn) %>%
    gather(key = Year, 
           value = Value2,
           -CountryAsylumName,
           -gap) %>%
    mutate( Year = case_when(
                    Year == "thisyear" ~ paste(thisyear),
                    Year == "baseline" ~ paste(baseline) )  )
  
 p <- ggplot(data, 
       aes(x = reorder(CountryAsylumName, gap),
           y = Value2, 
          fill = as.factor(Year))) +
  
  coord_flip() +
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 0, size = 1, colour = "#333333") +
  scale_fill_manual(values = c("#0072bc", "#FAAB18")) +
  labs(title = "Biggest Decrease of Population",
       subtitle = paste0( topn, " Biggest change in Refugee Population, ",region, " " ,  baseline," - ",thisyear), 
       x="", y ="",
       caption = "UNHCR https://www.unhcr.org/refugee-statistics/") +
  scale_y_continuous( label = scales::label_number_si()) + ## Format axis number
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
  
  return(p)
    
}
```
  
```{r example-plot_reg_decrease}
plot_reg_decrease(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Americas",
                  pop_type = c("REF", "ASY", "OIP"))
```
  
```{r tests-plot_reg_decrease}
test_that("plot_reg_decrease works", {
  expect_true(inherits(plot_reg_decrease, "function")) 
})
```
  
    
## Plot Biggest increase in Refugee Population 
    
```{r function-plot_reg_increase}
#' Plot Biggest Increase in Refugee Population
#' 
#' 

#' @param year Numeric value of the year (for instance 2020)
#' @param lag Number of year to used as comparison base
#' @param topn how many top countries to show..
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom ggalt geom_dumbbell
#' @importFrom unhcrthemes theme_unhcr
#' @return plot a ggplot2 object 
#' 
#' @export
plot_reg_increase <- function(  year = 2021,
                              lag = 5,
                              topn = 5,
                              region = "Americas",
                              pop_type =  c("REF", "ASY", "OIP") ){
  
  # library(tidyverse)
  
  thisyear <- year
  baseline <- thisyear -lag
  data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3")) %>%
    filter(Population.type  %in% pop_type)  %>%
    filter(Year == baseline | Year == thisyear) %>%
    mutate( Year = case_when(
      Year == thisyear ~ paste("thisyear"),
      Year == baseline ~ paste("baseline") )) %>%
    filter(UNHCRBureau == region) %>%
    group_by( CountryAsylumName, Year) %>%
    summarise(Value2 = sum(Value) )  %>%
    select(CountryAsylumName, Year, Value2) %>% 
    mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
        CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
        CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) %>% 
   # mutate(Year = paste0("year_",Year )) %>%
    spread(Year, Value2) %>%
    mutate(gap =   thisyear -baseline  ) %>%
    arrange(desc(gap)) %>%
    head(topn) 
  
 p <- ggplot(data, aes(x = baseline , 
                       xend = thisyear,
                       y = reorder(CountryAsylumName, gap),
                       group = CountryAsylumName)) + 
  ggalt::geom_dumbbell(colour = "#dddddd",
                size = 3,
                colour_x = "#0072bc",
                colour_xend = "#FAAB18") + 
  labs(title = paste0("Where did Refugee Population increased in ", region , "?"),
       subtitle = paste0("Biggest increase in Refugee Population, ", baseline," - ",thisyear),
       x="", y ="",
       caption = "UNHCR https://www.unhcr.org/refugee-statistics/") +
  scale_x_continuous( label = scales::label_number_si()) + ## Format axis number
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
 
 return(p)
    
}
```
  
```{r example-plot_reg_increase}
plot_reg_increase(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Americas",
                  pop_type = c("REF", "ASY", "OIP"))

plot_reg_increase(year = 2021,
                  lag = 5,
                  topn = 5,
                  region = "Asia",
                  pop_type = c("REF", "ASY", "OIP"))
```
  
```{r tests-plot_reg_increase}
test_that("plot_reg_increase works", {
  expect_true(inherits(plot_reg_increase, "function")) 
})
```
  
    
## Comparison over time by Region

    
## Evolution over time of the different Population of Concern

    
## Evolution by Country of Origin

    
## Refugee Over time

    
## Smootheed Evolution over time

## Mapping Population  

    
```{r function-plot_reg_map}
#' Plot a regional map
#' 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param topn how many top countries to show..
#' @param region Character value with the related UNHCR bureau - when left null, it will display the whole world
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' @param useBertin -Tells if the map should use Bertin 1953 projection - https://visionscarto.net/bertin-projection-1953)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom sf st_transform st_as_sf st_drop_geometry
#' @importFrom rnaturalearth ne_countries
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' @importFrom wbstats  wb 
#' @importFrom Hmisc cut2
#' @return plot a ggplot2 object 
#' 
#' @export
#' 
plot_reg_map <- function(    year = 2022, 
                            region = "Americas",
                            topn = 5,
                            pop_type =  c("REF", "ASY", "OIP"),
                            projection = "Mercator",
                            maxSymbolsize = .25   ){
 
      
      # Get World Bank data  #############
      wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL",  ## Population total https://data.worldbank.org/indicator/SP.POP.TOTL
                                            "NY.GDP.MKTP.CD", ## GDP current https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
                                            "NY.GDP.PCAP.CD", ## GDP per capita https://data.worldbank.org/indicator/NY.GDP.PCAP.CD 
                                            "NY.GNP.PCAP.CD" ## GNI per capita, Atlas method (current US$) https://data.worldbank.org/indicator/NY.GNP.PCAP.CD
      ),
      startdate = year-1, enddate = year, return_wide = TRUE) 
      # # Renaming variables for further matching
      names(wb_data)[1] <- "CountryAsylumCode"
      names(wb_data)[2] <- "Year"
      wb_data <- wb_data%>%
        filter(Year == year-1) 
      
      ## Get spatial data to add ##########
      mapproject <- ""
      
      listctr <-  unhcrdatapackage::reference |>
        filter(UNHCRBureau == region) |>
        select(iso_3) |>
        pull()
      
      
      
      ## Loading the stat tables ######
      data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                y= unhcrdatapackage::reference, 
                                by = c("CountryAsylumCode" = "iso_3")) %>%
        filter(Population.type  %in% pop_type &
                 Year == year & 
                 UNHCRBureau == region ) %>%
        group_by(Year, CountryAsylumName, CountryAsylumCode, UNHCRBureau,Latitude, Longitude  ) %>%
        summarise(Value = sum(Value) ) %>%
        ungroup()
      
      
      ## Join ########
      data2 <- data %>% 
        left_join(wb_data, 
                  by = c( "CountryAsylumCode")) %>%  
        mutate(ratio_disp_gdp = round( (Value / NY.GDP.MKTP.CD)*100, 4)  )  %>% 
        mutate(ratio_disp_gdpcap = round(  (Value/ NY.GDP.PCAP.CD)*100, 2)  )   %>% 
        mutate(ratio_disp_host = round( (Value/  SP.POP.TOTL)*100 , 2)  )  
      
      ## Get Break https://riatelab.github.io/mapsf/reference/mf_get_breaks.html
      # Discretize the variable
      data2$quintDisp <- Hmisc::cut2(data2$Value, g = 4)
      data2$quintDispGGP <- Hmisc::cut2(data2$ratio_disp_gdp, g = 4) 
      data2$quintDispHost <- Hmisc::cut2(data2$ratio_disp_host, g = 4)
        
      
      #names(data2)
      data2 <- data2 %>%
        sf::st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
      
      
      ## Getting world map for mapping
      world <- rnaturalearth::ne_countries(scale = "small", returnclass = "sf") %>% 
        filter(continent != "Antarctica")  %>%  
        filter(adm0_a3 %in%  listctr) 
      
      ## Manage Projection... 
      data2 <- data2 %>%  
        # this is the crs from d, which has no EPSG code:
        sf::st_transform(., '+init=epsg:4326')
      
      world <- world %>%  
        # this is the crs from d, which has no EPSG code:
        sf::st_transform(., '+init=epsg:4326')
      #   # this is the crs from d, which has no EPSG code:
      #   #sf::st_transform(., '+init=epsg:4326')
      #   #sf::st_transform(., '+proj=bertin1953 +R=1 0.72 0.73')
      #   #sf::st_transform(., '+proj=bertin1953 +x_0=1000')
      #   sf::st_transform(., '+proj=bertin1953')
      
      
      PopMap <- data2 |> 
                          sf::st_drop_geometry()|> 
                          ungroup() |>
                          arrange( desc (Value)) |> 
                          head(topn) |> 
                          select(Value) 
      
      minPopMap <- PopMap |>   min()
      maxPopMap <- PopMap |>  max()             
      
                
      
      ## Generate Map   ##################
      #Maps is created here with [MapSF package](https://riatelab.github.io/mapsf/index.html)
      # Select a font already installed on your system !!
      par(family="Lato")
      # set a theme
      mapsf::mf_theme(bg ="#d4dff2", #  "#E2E7EB",  ## background color --> Used country 
                      # bg = "#cdd2d4", "#faebd7ff",  "#cdd2d4",
                      mar = c(0, 0, 2, 0), ## margins
                      tab = FALSE,  # if TRUE the title is displayed as a 'tab'
                      fg = "#0072BC",  ## foreground color --> for the top title - use UNHCR Blue..
                      pos = "left", # position, one of 'left', 'center', 'right'
                      inner = FALSE, # if TRUE the title is displayed inside the plot area.
                      line = 2, #number of lines used for the title
                      cex = 2.5, #cex of the title
                      #font = "Lato",
                      font = 1 ) #font of the title
      
      
      
      mapsf::mf_init(world) 
      # Plot a shadow
      mapsf::mf_shadow(world,col = "grey50", cex = 0.2 , add = TRUE)
      mapsf::mf_map(world, 
                    add = TRUE, 
                    lwd = 0.5, 
                    border = "#93A3AB", 
                    col = "#FFFFFF")
      
      
      # Set a layout
      mapsf::mf_title(txt = paste0("Forcible Displacement in ", year), fg = "#FFFFFF")
      mapsf::mf_credits(txt = "Source: UNHCR.org/refugee-statistics - A Country is name if it features among the five largest population.\n The boundaries and names shown and the designations used on this map do not imply official endorsment or acceptance by the inited nations", bg = "#ffffff80") 
      
      ## Proportional Symbol with color based on other
      mapsf::mf_prop_typo( 
        x = data2, # frame to use.. 
        var = c("Value", "quintDispHost"),  ## First value for size, second for color
        inches = maxSymbolsize, # size of the biggest symbol (radius for circles, half width for squares) in inches
        val_max = maxPopMap,  # maximum value used for proportional symbols
        symbol = "circle", ## type of symbol- 'circle' or 'square'
        border = "grey25", ## border color of symbol
        lwd = 1.5, #  border width of symbol
        pal = "Inferno",  ## Color palette  - https://developer.r-project.org/Blog/public/2019/04/01/hcl-based-color-palettes-in-grdevices/
        alpha = .8,  ## if pal is a hcl.colors palette name, the alpha-transparency level
        leg_no_data = "No data", ## When no data
        col_na = "grey",  ## When no data
        leg_pos = c("topright", "bottomright"),  # position of the legend
        leg_title = c("Number of Individuals", "Ratio with Host Community"), # title of the legend
        leg_title_cex = c(.7, .7),  # title font size of the legend
        leg_val_cex = c(.5, .5), # content font size of the legend
        leg_val_rnd = .2, # number of decimal places of the values in the legend
        leg_frame = c(FALSE, FALSE), # add frame around the legend
        add = TRUE
      )
      # labels for a few  countries - https://riatelab.github.io/mapsf/reference/mf_label.html
     return(  mapsf::mf_label(x = data2[data2$Value >= minPopMap,], 
                      var = "CountryAsylumName",  # name(s) of the variable(s) to plot
                      cex = 0.9, #  labels cex
                      col = "black", 
                      font = 3.5,
                      halo = TRUE, # add halo
                      bg = "white",  # halo color
                      r = 0.05,  # width of the halo
                      overlap = FALSE,  # if FALSE, labels are moved so they do not overlap.
                      lines = TRUE) )



}
```
  
```{r example-plot_reg_map}
plot_reg_map(  year = 2022, 
                            region = "Americas",
                            topn = 5,
                            pop_type =  c("REF", "ASY", "OIP"),
                            projection = "Mercator",
                            maxSymbolsize = .25)

plot_reg_map(  year = 2022, 
                            region = "WestAfrica",
                            topn = 5,
                            pop_type =  c("REF", "ASY", "OIP"),
                            projection = "Mercator",
                            maxSymbolsize = .25)

```
  
```{r tests-plot_reg_map}
test_that("plot_reg_map works", {
  expect_true(inherits(plot_reg_map, "function")) 
})
```
  
 
    
## Refugee Chart Race
     


--- 

# Template

```{r function-template_CtryFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "Country_Factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param UNHCRBureau Bureau that covers all the countrie factsheet to generate
#' 
#' @export
#'

template_CtryFactsheet <- function(year = 2021,
                      UNHCRBureau) {
 
}

```


```{r function-template_RegFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "Regional_Factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param UNHCRBureau Bureau that covers all the countrie factsheet to generate
#' 
#' @export
#'

template_RegFactsheet <- function(year = 2021,
                      UNHCRBureau) {
 
}

```



# Update Dataset
    
```{r function-update_dataset}
#' Update the data on the package
#' 
#' The function pull the data from https://data.humdata.org/dataset/unhcr-population-data-for-world and do a few adjustement before inserting them in the package
#' 
#' @importFrom ckanr   ckanr_setup  package_search
#' @importFrom purrr  pluck  walk
#' @importFrom readr read_csv
#' @importFrom fs path path_file
#' @importFrom here here
#' @importFrom plyr rename
#' @importFrom reshape2 melt
#' @importFrom sinew makeOxygen
#' @importFrom tools resaveRdaFiles
#' 
#' @return nothing just refresh the data .rda
#' 
#' @export
update_dataset <- function(){
  


    ckanr::ckanr_setup("https://data.humdata.org")
    
    ckanr::package_search("name:unhcr-population-data-for-world", as = "table") %>% 
      purrr::pluck("results", "resources", 1, "url") %>% 
      purrr::walk(~ckanr::ckan_fetch(., store = "disk", path = fs::path("data-raw", fs::path_file(.))))
    
    read_sans_hxl <- function(file, ...) {
      hdrs <- readr::read_csv(file, n_max = 0) %>% names()
      
      readr::read_csv(file, col_names = hdrs, skip = 2, ...)
    }



    ## Displaced ##########
    cat(paste0("Reading end_year_population_totals_residing_world \n"))
    end_year_population_totals <- read_sans_hxl(file =  here::here("data-raw","end_year_population_totals_residing_world.csv"))
    
    
    # Rename column to have proper Variable names
    end_year_population_totals <- plyr::rename(end_year_population_totals, c("Country of Origin Code"="CountryOriginCode",
                                           "Country of Asylum Code"="CountryAsylumCode", 
                                           "Country of Origin Name"="CountryOriginName",
                                           "Country of Asylum Name"="CountryAsylumName", 
                                           "Refugees"="REF", 
                                           "Internally displaced persons"="IDP", 
                                           "Asylum seekers"="ASY",
                                           "Others of concern to UNHCR"="OOC",
                                           "Stateless Persons"="STA",    
                                          #  "Venezuelans Displaced Abroad"="VDA"
                                           "Host community" = "HCO",
                                           "Other people in need of international protection"="OIP"))
    cat(names(end_year_population_totals))
    
    sinew::makeOxygen(end_year_population_totals, add_fields = "source")
    
    save(end_year_population_totals, file =  here::here("data","end_year_population_totals.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","end_year_population_totals.RData"),compress="bzip2")
    
    cat(paste0("Saving end_year_population_totals_residing_world \n"))
     
    
    
    
    ## Create a long format for the dataset
    
    end_year_population_totals_long <- reshape2::melt(end_year_population_totals,
                                               # ID variables - all the variables to keep but not split apart on
                                               id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                               # The source columns
                                               measure.vars=c("REF","IDP", "ASY","OOC","STA","OIP","HCO"),
                                               # Name of the destination column that will identify the original
                                               # column that the measurement came from
                                               variable.name="Population.type",
                                               value.name="Value")
    
    end_year_population_totals_long <- end_year_population_totals_long[end_year_population_totals_long$Value > 0, ]
    
    end_year_population_totals_long$Population.type.label <- ""
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="IDP"] <- "Internally displaced persons"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern to UNHCR"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OIP"] <- "Other people in need of international protection"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
    end_year_population_totals_long$Population.type.label.short <- ""
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="IDP"] <- "IDPs"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OIP"] <- "In need of int. protect."
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
      
    save(end_year_population_totals_long, file =  here::here("data","end_year_population_totals_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","end_year_population_totals_long.RData"),compress="xz") 
    
    cat(paste0("Saving long format for  end_year_population_totals_residing_world \n"))
    
    
    ## Solutions ##########
    
    solutions_residing <- read_sans_hxl(file =  here::here("data-raw","solutions_residing_world.csv"))
    
    cat(paste0("Reading solutions_residing_world \n"))
    
    sinew::makeOxygen(solutions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    solutions <- plyr::rename(solutions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                                             "Country of Origin Name"="CountryOriginName",
                                                                             "Country of Asylum Name"="CountryAsylumName", 
                                                                             "Resettlement arrivals"="RST",
                                                                             "Refugee returns"="RET",
                                                                             "Naturalisation"="NAT",
                                                                             "IDP returns"="RDP" ))
    
    save(solutions, file =  here::here("data","solutions.RData"))
    sinew::makeOxygen(solutions, add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions.RData"),compress="bzip2")
    
    cat(paste0("Saving solutions_residing_world \n"))
    
    solutions_long <- reshape2::melt(solutions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                                      # The source columns
                                                      measure.vars=c("NAT","RST", "RET","RDP"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Solution.type",
                                                      value.name="Value")
    
    solutions_long <- solutions_long[solutions_long$Value > 0, ]
    
    
    solutions_long$Solution.type.label <- ""
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RST"] <- "Resettlement arrivals"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="NAT"] <- "Naturalisation"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RET"] <- "Refugee returns"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RDP"] <- "IDP returns"
    
    save(solutions_long , file =  here::here("data","solutions_long.RData"))
    sinew::makeOxygen(solutions_long , add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions_long.RData"),compress="xz")
    
    cat(paste0("Saving long format for solutions_residing_world \n"))
    
    ## Demographics ##########
    
    demographics_residing <- read_sans_hxl(file =  here::here("data-raw","demographics_residing_world.csv"))
    
    cat(paste0("Reading demographics_residing_world \n"))
    #names(demographics_residing)
    
    sinew::makeOxygen(demographics_residing, add_fields = "source")
    # Rename column to have proper Variable names
    demographics <- plyr::rename(demographics_residing, c("Country of Origin Code"="CountryOriginCode",
                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                             "Country of Origin Name"="CountryOriginName",
                                                             "Country of Asylum Name"="CountryAsylumName",  
                                                             "Population Type"= "Population.type",
                                                             "Female 0-4"="Female04", 
                                                             "Female 5-11"="Female511", 
                                                             "Female 12-17"="Female1217", 
                                                             "Female 18-59"="Female1859",
                                                             "Female 60 or more"="Female60ormore",
                                                             "Female Unknown"="FemaleUnknown",
                                                             "Female Total"="FemaleTotal", 
                                                             "Male 0-4"="Male04", 
                                                             "Male 5-11"="Male511", 
                                                             "Male 12-17"="Male1217", 
                                                             "Male 18-59"="Male1859",
                                                             "Male 60 or more"="Male60ormore",
                                                             "Male Unknown"="MaleUnknown",
                                                             "Male Total"="MaleTotal")
                                                             )
    
    
    #names(demographics)
    
    demographics$Population.type.label <- ""
    demographics$Population.type.label[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label[demographics$Population.type=="IDP"] <- "Internally displaced persons"
    demographics$Population.type.label[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label[demographics$Population.type=="OOC"] <- "Others of concern to UNHCR"
    demographics$Population.type.label[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label[demographics$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    demographics$Population.type.label[demographics$Population.type=="OIP"] <- "Other people in need of international protection"
    demographics$Population.type.label[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label[demographics$Population.type=="RDP"] <- "IDP returns"
    
    demographics$Population.type.label.short <- ""
    demographics$Population.type.label.short[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label.short[demographics$Population.type=="IDP"] <- "IDPs"
    demographics$Population.type.label.short[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label.short[demographics$Population.type=="OOC"] <- "Others of Concern"
    demographics$Population.type.label.short[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label.short[demographics$Population.type=="VDA"] <- "Venezuelans Abroad"
    demographics$Population.type.label.short[demographics$Population.type=="OIP"] <- "In need of int. protect."
    demographics$Population.type.label.short[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label.short[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label.short[demographics$Population.type=="RDP"] <- "IDP returns"
    
    # names(demographics)
    # table(demographics$location, useNA = "ifany")
    # table(demographics$urbanRural, useNA = "ifany")
    # table(demographics$accommodationType, useNA = "ifany")
    # table(demographics$Population.type.label.short, useNA = "ifany")
    
    save(demographics, file =  here::here("data","demographics.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","demographics.RData"),compress="bzip2")
    
    cat(paste0("Saving demographics_residing_world \n"))
    
    ## RSD Application ########## 
    asylum_applications_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_applications_residing_world.csv"))
    
    cat(paste0("Reading asylum_applications_residing_world \n"))
    sinew::makeOxygen(asylum_applications_residing, add_fields = "source")
    
    # Rename column to have proper Variable names
    asylum_applications <- plyr::rename(asylum_applications_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                        "Country of Asylum Code"="CountryAsylumCode", 
                                                                        "Country of Origin Name"="CountryOriginName",
                                                                        "Country of Asylum Name"="CountryAsylumName", 
                                                                        "Procedure Type"="ProcedureType",                      
                                                                        "Procedure Name"="ProcedureName",                      
                                                                        "Application Type Code"="ApplicationTypeCode",               
                                                                        "Application Type"="ApplicationType",                    
                                                                        "Application Data Type"="ApplicationDataType",               
                                                                        "Application Data"="ApplicationData",                    
                                                                        "Application Average Persons Per Case"="ApplicationAveragePersonsPerCase",
                                                                        "Number of Applications"="NumberApplications" 
    )
    )
    
    asylum_applications$ApplicationType[asylum_applications$ApplicationTypeCode == "V"] <- "Various"
    asylum_applications$ApplicationTypeCode[asylum_applications$ApplicationType == "New and appeal"] <- "NA"
    
    #View(unique(asylum_applications[ ,c("ApplicationTypeCode","ApplicationType")]))
    
    # View(unique(asylum_applications[ ,c("ProcedureType",  "ProcedureName")]))
    # 
    # View(unique(asylum_applications[ ,c("ApplicationDataType","ApplicationData")]))
    
    save(asylum_applications, file =  here::here("data","asylum_applications.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_applications.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_applications_residing_world \n"))
    
    ## RSD Decision ##########
    asylum_decisions_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_decisions_residing_world.csv"))
    
    cat(paste0("Reading asylum_decisions_residing_world \n"))
    
    sinew::makeOxygen(asylum_decisions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    asylum_decisions <- plyr::rename(asylum_decisions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                   "Country of Asylum Code"="CountryAsylumCode", 
                                                                   "Country of Origin Name"="CountryOriginName",
                                                                   "Country of Asylum Name"="CountryAsylumName", 
                                                                   "Procedure Type"="ProcedureType",                    
                                                                   "Procedure Name"="ProcedureName",                    
                                                                   "Decision Type Code"="DecisionTypeCode",                
                                                                   "Decision Data Type"="DecisionDataType",                
                                                                   "Decision Data"="DecisionData",                     
                                                                   "Decisions Average Persons Per Case"= "DecisionsAveragePersonsPerCase",
                                                                   "Complementary Protection"="ComplementaryProtection",          
                                                                   "Otherwise Closed" ="OtherwiseClosed",                
                                                                   "Total Decided" = "TotalDecided"
                                                                   )
    )
    
    
    # View(unique(asylum_decisions[ ,c("ProcedureType",  "ProcedureName")]))
    # View(unique(asylum_decisions[ ,c("DecisionTypeCode")]))
    
    asylum_decisions$DecisionTypeName <- ""
    asylum_decisions$DecisionTypeCode[is.na(asylum_decisions$DecisionTypeCode) ] <- "NA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FI"] <- "First instance"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "AR"] <- "Re-opened/repeat"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FA"] <- "First instance and appeal"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "BL"] <- "BL"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "NA"] <- "New applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "RA"] <- "Repeat/reopened applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "CA"] <- "CA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "EO"] <- "US Executive Office of Immigration Review"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "IN"] <- "US Citizenship and Immigration Services"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TR"] <- "TR"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "JR"] <- "Judicial Review "
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "SP"] <- "Subsidiary protection"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TA"] <- "Temporary asylum"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TP"] <- "Temporary Protection" 
    
    #View(unique(asylum_decisions[ ,c("DecisionTypeCode","DecisionTypeName")])) 
    sinew::makeOxygen(asylum_decisions, add_fields = "source")
    save(asylum_decisions, file =  here::here("data","asylum_decisions.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_decisions_residing_world \n"))
    
    ## RDS Decision Long format ########
    
    #names(asylum_decisions)
    
    asylum_decisions_long <- reshape2::melt(asylum_decisions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode",
                                                                "CountryOriginName","CountryAsylumName",
                                                                "ProcedureType",  "ProcedureName",
                                                                "DecisionTypeCode","DecisionTypeName",
                                                                "DecisionData","DecisionsAveragePersonsPerCase"),
                                                      # The source columns
                                                      measure.vars=c("Recognized","ComplementaryProtection","OtherwiseClosed","Rejected"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Decision.output",
                                                      value.name="Value")
    
    asylum_decisions_long <- asylum_decisions_long[asylum_decisions_long$Value > 0, ]
    
    sinew::makeOxygen(asylum_decisions_long, add_fields = "source")
    save(asylum_decisions_long, file =  here::here("data","asylum_decisions_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions_long.RData"),compress="xz")  
    
    cat(paste0("Saving long format for asylum_decisions_residing_world \n"))
}
```
  
```{r example-update_dataset}
#update_dataset()
```
  
```{r tests-update_dataset}
test_that("update_dataset works", {
  expect_true(inherits(update_dataset, "function")) 
})
```
  


```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library")
pkgdown::build_site()
```

