---
title: "All Plotting functions"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
knitr::opts_chunk$set(
                      comment = "#>",
                      message=FALSE, 
                      warning=FALSE,
                      #fig.retina = 2, 
                      fig.width = 8,
                      fig.asp = 0.618,
                     # fig.align = "center",
                     # dev = "ragg_png",
                      out.width = "90%"
)
unlink(".RData")
library(testthat)
library(ggplot2)
library(unhcrthemes)
# library(extrafont) 
# font_import()
# loadfonts()
# font_install('fontcm')
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```


<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

```



# Country Questions

## Plot Population type per year

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function-plot_ctr_population_type_per_year}
#' Graph of population type per year
#'
#' @param start_year Numeric value of first year  
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#'
#' @export
#'
#'

plot_ctr_population_type_per_year <- function(start_year = 2015,
                                     country_asylum_iso3c = country_asylum_iso3c,
                                     pop_type = Population.type
                                     ) {
  



  cols_poptype <- c("Asylum seekers" = "#18375F",
                    "Refugees" = "#0072BC",
                    #"Venezuelans Displaced Abroad" = "#EF4A60", 
                    "Other people in need of international protection" = "#EF4A60", 
                    "Others of Concern to UNHCR" = "#999999",
                    "Internally displaced persons" = "#00B398",
                    "Stateless Persons" = "#E1CC0D")
  
  
  df <- unhcrdatapackage::end_year_population_totals_long  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year >= start_year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
                  Population.type %in% pop_type #### Parameter
    )  |>  
    group_by(Year, CountryAsylumName, Population.type.label)  |> 
    summarise(Value = sum(Value, na.rm = TRUE)) |> 
    ungroup()
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()
  
  year_breaks <- diff(range(df$Year)) + 1 
  
  p <- ggplot(df) +
    geom_col(aes(x = Year, y = Value, fill = Population.type.label),
             width = 0.7) +
    geom_text(aes(x = Year, 
                  y = Value, 
                  color = Population.type.label, 
                  label = label_number( accuracy = 1,
                                   scale_cut = cut_short_scale())(Value)),
              position = position_stack(vjust = 0.5),
              show.legend = FALSE,
              size = 5) +
    scale_color_manual(values = c("#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF",
                                  "#FFFFFF")) +
    scale_fill_manual(values = cols_poptype,
                      drop = TRUE,
                      limits = force) +
    scale_x_continuous(breaks = scales::breaks_pretty(n = year_breaks)) +
    scale_y_continuous(expand = expansion(c(0, 0.1))) +
    labs(title = paste0(CountryAsylum_name_text, ": Population type per year"), 
         subtitle = "Number of people (thousand)",
         caption = "Source: UNHCR Refugee Data Finder") +
    theme_unhcr(grid = FALSE, axis = "x", axis_title = FALSE, axis_text = "x") +
    stat_summary(fun = sum, aes(x = Year,
                                y = Value, 
                                label = scales::label_number( accuracy = 1,
                                                       scale_cut = cut_short_scale())(..y..), 
                                group = Year), 
                 geom = "text", size = 5,
                 vjust = -0.5) +
    theme(legend.direction = "vertical",
          legend.key.size = unit(0.8, 'cm'),
          text = element_text(size = 20),
          plot.subtitle=element_text(size=19),
          plot.title = element_text(size=23),
          plot.caption = element_text(size=13))
  
  return(p) # print(p)
  }
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples-plot_ctr_population_type_per_year, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_per_year(start_year = 2016,
                         country_asylum_iso3c = "PAN",
                          pop_type = c("REF", 
                                       "ASY", 
                                       "OIP", 
                                       "OOC",
                                       "STA",
                                       "IDP" )
                  )
```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests-plot_ctr_population_type_per_year}


```



## Plot Main country of origin - Absolute value


```{r function-plot_ctr_population_type_abs}
#' Main country of origin - Absolute value
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY,   OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_population_type_abs <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                       #VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <- 
  unhcrdatapackage::end_year_population_totals  |> 
  filter(CountryAsylumCode != "UKN",
                !is.na(CountryAsylumCode),
                (Year == year | Year == year -1),  #### Parameter
                CountryAsylumCode == country_asylum_iso3c, #### Parameter
  )  |>  
  select(Year, CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
  group_by(Year, CountryAsylumName, CountryOriginName) |>
  filter(!!sym(pop_type) != 0) |>
  mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
  ungroup() |>
  group_by(CountryAsylumName, CountryOriginName) |> 
  arrange(Year) |>
  mutate(diff_pop_type_value = percent(((pop_type_value-lag(pop_type_value))/lag(pop_type_value)),
                                                      accuracy = 1.1,
                                                      trim = FALSE
  )) |> 
  ungroup() |>
  filter(Year == year) |> 
  mutate(
    origin_data_prot = forcats::fct_lump_n(
      f = CountryOriginName,
      n = top_n_countries,  #### Parameter
      w = pop_type_value,
      other_level = 'Other nationalities',
      ties.method = "last"
    )
  ) |>
  mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                            'Other nationalities'),
                diff_pop_type_value = case_when(origin_data_prot == 'Other nationalities' ~ "",
                                                TRUE ~ diff_pop_type_value)) |>
  group_by(CountryAsylumName, diff_pop_type_value, origin_data_prot) |>
  summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
  ungroup() |> 
  arrange(desc(pop_type_value)) |>
  filter(pop_type_value != 0L) |>
  mutate(
    origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
    origin_data_prot =  suppressWarnings(
      case_when(
        origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                         "Other nationalities",
                                                                         after = 0),
        TRUE ~ origin_data_prot
      )
    ),
    perc = percent(
      pop_type_value / sum(pop_type_value),
      accuracy = 1,
      trim = TRUE
    )
  )

CountryAsylum_name_text <- df |> 
  distinct(CountryAsylumName) |> 
  pull()


p <-  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                           scale_cut = cut_short_scale())(pop_type_value)
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(pop_type_value)),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  geom_text( # positive diff percentage label
    data = subset(df, with(df, !grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.8,
    vjust = 0.5,
    colour = "grey",
    size = 4
  ) +
  geom_text( # negative diff percentage label
    data = subset(df, with(df, grepl('-', diff_pop_type_value))),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = diff_pop_type_value
    ),
    hjust = -2.5,
    vjust = 0.5,
    colour = "#0472bc",
    size = 4
  ) +
  geom_text( #increase triangle
    data = subset(df, with(df, !grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9650),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0bb498",
    size = 7
  ) +
  geom_text( #decrease triangle
    data = subset(df, with(df, grepl('-', diff_pop_type_value) & origin_data_prot != "Other nationalities")),
    aes(x = pop_type_value,
        y = origin_data_prot),
    label = intToUtf8(9660),
    hjust = -4.8 ,
    vjust = 0.5,
    color = "#0472bc",
    size = 7
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": Main Countries of origin (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = "Number of people",
       caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
  theme_unhcr(grid = FALSE, axis = "y", axis_title = FALSE, axis_text = "y") +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_abs, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 4,
                    pop_type = "REF"
                    ) 

## Same with 9 top countries and asylum seekers included
plot_ctr_population_type_abs(year = 2020,
                    country_asylum_iso3c = "USA",
                    top_n_countries = 9,
                    pop_type = "REF"
                    ) 

```

```{r tests-plot_ctr_population_type_abs}

```



## Plot Main country of origin - Percentage


```{r function-plot_ctr_population_type_perc}
#' Main country of origin - Percentage
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param top_n_countries Numeric value of number of main countries that the graph should display
#' @param pop_type Character value. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_population_type_perc <- function(year = 2021,
                                country_asylum_iso3c = country_asylum_iso3c,
                                top_n_countries = 9,
                                pop_type = "REF"
                              ) {



  cols_poptype <- list(ASY = c("Asylum seekers", "#18375F"),
                       REF = c("Refugees", "#0072BC"),
                      # VDA = c("Venezuelans Displaced Abroad", "#EF4A60"), 
                       OIP = c("Other people in need of international protection", "#EF4A60"), 
                       OOC = c("Others of Concern to UNHCR", "#999999"),
                       IDP = c("Internally displaced persons", "#00B398"),
                       STA = c("Stateless Persons", "#E1CC0D")
  )
  
  
  df <-  
    unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c, #### Parameter
    )  |>  
    select(CountryAsylumName, CountryOriginName,!!sym(pop_type)) |>
    group_by(CountryAsylumName, CountryOriginName) |>
    filter(!!sym(pop_type) != 0) |>
    mutate(pop_type_value = sum(!!sym(pop_type), na.rm=TRUE)) |> 
    ungroup() |>
    mutate(
      origin_data_prot = forcats::fct_lump_n(
        f = CountryOriginName,
        n = top_n_countries,  #### Parameter
        w = pop_type_value,
        other_level = 'Other nationalities',
        ties.method = "last"
      )
    ) |>
    mutate(origin_data_prot = forcats::fct_explicit_na(origin_data_prot,
                                                              'Other nationalities')) |>
    group_by(CountryAsylumName,origin_data_prot) |>
    summarise(pop_type_value = sum(pop_type_value, na.rm = TRUE)) |>
    ungroup() |> 
    arrange(desc(pop_type_value)) |>
    filter(pop_type_value != 0L) |>
    mutate(
      origin_data_prot = forcats::fct_rev(forcats::fct_inorder(origin_data_prot)),
      origin_data_prot =  suppressWarnings(
        case_when(
          origin_data_prot == "Other nationalities" ~ forcats::fct_relevel(origin_data_prot,
                                                                           "Other nationalities",
                                                                           after = 0),
          TRUE ~ origin_data_prot
        )
      ),
      perc = percent(
        pop_type_value / sum(pop_type_value),
        accuracy = 1,
        trim = FALSE
      )
    )
  
  CountryAsylum_name_text <- df |> 
    distinct(CountryAsylumName) |> 
    pull()



p <- 
  ggplot(df) +
  geom_col(aes(x = pop_type_value, y = origin_data_prot),
           fill = cols_poptype[[pop_type]][2],
           width = 0.8) +
  ## Position label differently in the bar in white - outside bar in black
  geom_text(
    data = subset(df, pop_type_value < max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = -0.1 ,
    vjust = 0.5,
    colour = "black",
    size = 5
  ) +
  geom_text(
    data = subset(df, pop_type_value >= max(pop_type_value) / 1.5),
    aes(
      x = pop_type_value,
      y = origin_data_prot,
      label = perc
    ),
    hjust = 1.1 ,
    vjust = 0.5,
    colour = "white",
    size = 5
  ) +
  labs(title = paste0(CountryAsylum_name_text, ": Main Countries of origin (", cols_poptype[[pop_type]][1], ")", " | ",  year),
       subtitle = "Percentage",
       caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency") +
  scale_x_continuous(expand = expansion(c(0, 0.1))) +
 theme_unhcr(grid = FALSE, axis = "y", axis_title = FALSE, axis_text = "y") +
  theme(legend.direction = "vertical",
        legend.key.size = unit(0.8, 'cm'),
        text = element_text(size = 20),
        plot.subtitle=element_text(size=19),
        plot.title = element_text(size=23),
        plot.caption = element_text(size=13))
  return(p) # print(p)
  }
```

```{r examples-plot_ctr_population_type_perc, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}

plot_ctr_population_type_perc(year = 2021,
                    country_asylum_iso3c = "BRA",
                    top_n_countries = 9,
                    pop_type = "REF"  ) 
```

```{r tests-plot_ctr_population_type_perc}

```


## Plot Increases and Decreases in Population Groups


```{r function-plot_ctr_diff_in_pop_groups}
#' Increases and Decreases in Population Groups
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_diff_in_pop_groups <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type
) {



  diff_perc <- function(x){
    x = as.numeric((x - lag(x))/lag(x)) + 0
    
  }
  
  
  df <- unhcrdatapackage::end_year_population_totals  |> 
    filter(CountryAsylumCode != "UKN",
                  !is.na(CountryAsylumCode),
                  (Year == year-1 | Year == year),  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    group_by(Year, CountryAsylumName) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() |> 
    arrange(Year) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName) |> 
    summarise(across(where(is.numeric), 
                                   list(diffabs = diff,
                                        diffperc = diff_perc),
                                   .names = "{.col}_{.fn}")) |> 
    ungroup() |> 
    slice(2) 
  
  df <- replace(df, is.na(df), 0)
  
  df <- df |> 
    tidyr::gather(v, value, REF_diffabs:OIP_diffperc) |> 
    tidyr::separate(v, c("pop_type", "value_type"), sep = "\\_") |> 
    tidyr::spread(key = value_type, value = value) |> 
    mutate(diffper =percent(
      diffperc,
      accuracy = 1,
      trim = FALSE
    ))
  
  
  p <- df |> 
    filter(pop_type %in% pop_type) |>
    ggplot() +
    geom_col(aes(x = pop_type, 
                 y = diffabs,
                 fill = pop_type),
             width = 0.8) +
    scale_fill_manual(
      values = c("ASY" = "#18375F",
                 "REF" = "#0072BC",
                 "OIP" = "#EF4A60", 
                 #"VDA" = "#EF4A60", 
                 "OOC" = "#999999",
                 "IDP" = "#00B398",
                 "STA" = "#E1CC0D"),
      drop= TRUE,
      limits = force,
      guide="none"
    ) +
    scale_x_discrete(labels= c("ASY" = "Asylum seekers",
                               "REF" = "Refugees",
                               #"VDA" = "Venezuelans Displaced\nAbroad", ,
                               "OIP" = "Other people in need\n of international protection", 
                               "OOC" = "Others of Concern\nto UNHCR",
                               "IDP" = "Internally Displaced\nPersons",
                               "STA" = "Stateless Persons"),
                     drop = TRUE,
                     limits = force) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = label_number(accuracy = 1,
                              scale_cut = cut_short_scale())(diffabs) ),
      vjust = -0.5 ,
      colour = "black",
      size = 5
    ) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs < max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = -2.0 ,
      colour = "black",
      size = 5
    ) +
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = label_number(accuracy = 1,
                             scale_cut = cut_short_scale())(diffabs)
      ),
      vjust = 2.7 ,
      colour = "white",
      size = 5
    ) + 
    geom_text(
      data = subset(df, diffabs >= 0 & diffabs >= max(diffabs) / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = 1.2 ,
      colour = "white",
      size = 5
    ) + #################################
  # geom_text(
  #   data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #   aes(
  #     x = pop_type,
  #     y = diffabs,
  #     label = label_number(accuracy = 1,
  #                                  scale_cut = cut_short_scale())(diffabs)
  #   ),
  #   vjust = -2.0 ,
  #   colour = "white",
  #   size = 5
  # )  +
  #   geom_text(
  #     data = subset(df, diffabs < 0 & diffabs <= min(diffabs) / 1.5),
  #     aes(
  #       x = pop_type,
  #       y = diffabs,
  #       label = diffper
  #     ),
  #     vjust = -0.5 ,
  #     colour = "white",
  #     size = 5
  #   ) +
  geom_text(
    data = subset(df, diffabs < 0/ 1.5),
    aes(
      x = pop_type,
      y = diffabs,
      label = label_number(accuracy = 1,
                            scale_cut = cut_short_scale())(diffabs)
    ),
    vjust =  1.2,
    colour = "black",
    size = 5
  ) + 
    geom_text(
      data = subset(df, diffabs < 0  / 1.5),
      aes(
        x = pop_type,
        y = diffabs,
        label = diffper
      ),
      vjust = 2.7,
      colour = "black",
      size = 5
    ) +
    geom_hline(yintercept = 0, color = "black") +
    labs(title = paste0(df |> 
                          distinct(CountryAsylumName) |> 
                          pull(), 
                        ": Increases and Decreases in Population Groups | ",
                        year-1,
                        "-",
                        year),
         subtitle = "Number of people and percentage",
         caption = "Source: UNHCR Refugee Data Finder\n?? UNHCR, The UN Refugee Agency")  + 
    theme_unhcr(grid = FALSE, axis = "x", axis_title = FALSE, axis_text = "x") +
    theme(axis.line.x = element_line(color="white"),
          axis.text.x = element_text(size=10))
  
  return(p) # print(p)
}
```

```{r examples-plot_ctr_diff_in_pop_groups, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_diff_in_pop_groups(year = 2021,
                            country_asylum_iso3c = "USA",
                            pop_type = c("REF", "ASY")
         )

```

```{r tests-plot_ctr_diff_in_pop_groups}

```




## Main Destination from this country


```{r function-plot_ctr_destination}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_origin_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_destination <- function(year = 2021,
                                 country_origin_iso3c = country_origin_iso3c,
                                  pop_type = pop_type) {



  
  
Destination <- left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))  |>
  filter(CountryOriginCode  == country_origin_iso3c  & 
                 Year == year &
                Population.type  %in% as.vector(pop_type)  )  |>  
   mutate(CountryAsylumName = str_replace(CountryAsylumName, " \\(Bolivarian Republic of\\)", ""),
         CountryAsylumName = str_replace(CountryAsylumName, "Iran \\(Islamic Republic of\\)", "Iran"),
         CountryAsylumName = str_replace(CountryAsylumName, "United States of America", "USA"),
         CountryAsylumName = str_replace(CountryAsylumName, "United Kingdom of Great Britain and Northern Ireland", "UK")) |> 
   
   group_by( CountryAsylumName) |>
   summarise(DisplacedAcrossBorders = sum(Value) )  |>
   mutate( DisplacedAcrossBordersRound =  ifelse(DisplacedAcrossBorders > 1000, 
                            paste(label_number( accuracy = .1,
                                   scale_cut = cut_short_scale())(DisplacedAcrossBorders)),
                            as.character(DisplacedAcrossBorders) ) ) |>
   arrange(desc(DisplacedAcrossBorders)) |>
   head(10) |>
   filter(DisplacedAcrossBorders >0)

if( nrow(Destination) ==  0 ){
  cat(paste0("There's no recorded countries of destination for ",country_origin_iso3c ))
  
} else {


#Make plot
p <- ggplot(Destination, aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), ## Reordering country by Value
                           y = DisplacedAcrossBorders)) +
  geom_bar(stat = "identity", 
           position = "identity", 
           fill = "#0072bc") + # here we configure that it will be bar chart+
## Format axis number
  scale_y_continuous( labels = label_number(scale_cut = cut_short_scale())) + 
  
  ## Position label differently in the bar in white - outside bar in black
  geom_label( data = subset(Destination, DisplacedAcrossBorders < max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = -0.1 ,
              vjust = 0.5, 
              colour = "black", 
              fill = NA, 
              label.size = NA, 
              #family = "Lato", 
              size = 4   ) +  

  geom_label( data = subset(Destination, DisplacedAcrossBorders >= max(DisplacedAcrossBorders) / 1.5),
              aes(x = reorder(CountryAsylumName, DisplacedAcrossBorders), 
                  y = DisplacedAcrossBorders,
                  label= DisplacedAcrossBordersRound),
              hjust = 1.1 ,
              vjust = 0.5, 
              colour = "white", 
              fill = NA, 
              label.size = NA, 
              # family = "Lato", 
              size = 4   ) +   
  # Add `coord_flip()` to make your vertical bars horizontal:
  coord_flip() + 
  
  ## and the chart labels
  labs(title = paste0("What are the main destinations for Forcibly Displaced People?" ),
       
       subtitle = paste0("Top Destination Countries - Data as of ",year, " for population from ",country_origin_iso3c ), 
       x = "",
       y = "",
       caption = "Data: UNHCR Refugee Population Statistics Database; Visualisation: UnhcrDataPackage.\n Forced Displacement includes Refugees, Asylym Seekers and Venezuelan Displaced Abroad Population Group.") +
    
  # Style  
  geom_hline(yintercept = 0, size = 1.1, colour = "#333333") +
  theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
  theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
        panel.grid.major.y = element_blank()) ### changing grid line that should appear
  
  return(p) # print(p)
  
  }
}

```

```{r examples-plot_ctr_destination, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_destination(year = 2021,
                     country_origin_iso3c = "COL",
                     pop_type = c("REF", "ASY")
         )

```
    
## Tree Map of Categories

```{r function-plot_ctr_treemap}
#' Tree map of Population Groups within a country
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line 
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace 
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_treemap <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {




  datatree <-  unhcrdatapackage::end_year_population_totals_long  |> 
    filter(Year == year,  #### Parameter
                  CountryAsylumCode == country_asylum_iso3c #### Parameter
    ) |> 
    select(-c(Year)) |> 
    group_by(CountryAsylumName,  Population.type, 
                    Population.type.label, Population.type.label.short) |> 
    summarise(across(where(is.numeric), sum)) |> 
    ungroup() 
  
  treemap <- ggplot(datatree, 
       aes(area = Value, 
           fill = Population.type,
           label = paste0(round(100*Value/sum(Value),1), 
                          "%\n", 
                          Population.type.label))) +
         treemapify::geom_treemap() +
         treemapify::geom_treemap_text(colour = "white",
                           place = "centre", size = 25) +
         scale_fill_manual( values = c(   "IDP" = "#00B398",
                                         # "VDA"="#EF4A60",
                                          "OIP"="#EF4A60",
                                          "ASY" = "#18375F",
                                          "REF" = "#0072BC",
                                          "OOC" ="#8395b9",
                                          "STA"="#E1CC0D")) +
         
      theme_unhcr(font_size = 12, grid = "Y", axis = "x", axis_title = "y", legend = FALSE) +
         theme(legend.position = "none") +
         ## and the chart labels
         labs(title = paste0("Population of Concern in ", country_asylum_iso3c),
              subtitle = paste0("As of ", year, ", a total of ", format(round(sum(datatree$Value), -3),  big.mark=","), " Individuals"),
              x = "",
              y = "",
              caption = "Source: UNHCR.org/refugee-statistics  ")  

print(treemap)
}

```
    
```{r examples-plot_ctr_treemap, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_treemap(year = 2021,
                            country_asylum_iso3c = "USA",
                            pop_type = c("REF", "ASY")
         )

```    
    


## Refugees Age Pyramid

```{r function-plot_ctr_pyramid}
#' Population Pyramid
#'
#' @param year Numeric value of the year (for instance 2020)
#' @param country_asylum_iso3c Character value with the ISO-3 character code of the Country of Asylum
#' @param pop_type Vector of character values. Possible population type (e.g.: REF, IDP, ASY, OIP, OOC, STA)
#' 
#' @importFrom ggplot2  ggplot  aes  coord_flip   element_blank element_line
#'             element_text expansion geom_bar geom_col geom_hline unit stat_summary
#'             geom_label geom_text labs  position_stack  scale_color_manual scale_colour_manual 
#'             geom_text
#'             scale_fill_manual scale_x_continuous scale_x_discrete  scale_y_continuous   sym theme  
#' @importFrom utils  head
#' @importFrom tidyselect where
#' @importFrom stringr  str_replace str_detect
#' @importFrom scales cut_short_scale percent label_number breaks_pretty
#' @importFrom stats  reorder aggregate 
#' @importFrom dplyr  desc select  case_when lag mutate group_by filter summarise ungroup
#'               pull distinct n arrange across slice left_join
#' @importFrom tidyr pivot_longer
#' @importFrom unhcrthemes theme_unhcr
#' 
#' @export
#'

plot_ctr_pyramid <- function(year = 2021,
                     country_asylum_iso3c = country_asylum_iso3c,
                     pop_type = pop_type) {



  
  demographics1 <- unhcrdatapackage::demographics |>
                   left_join( unhcrdatapackage::reference |> 
                                       select(UNHCRBureau, iso_3),  
                                     by = c("CountryAsylumCode" = "iso_3")) |> 
                   filter(CountryAsylumCode  == country_asylum_iso3c &
                               Year == year-1 &
                               Population.type  %in% as.vector(pop_type) ) |>
    
                    mutate ( totGen = FemaleTotal +MaleTotal,
                               totbreak = Female04 + Female511 + Female1217 + 
                                          Female1859 + Female60ormore + FemaleUnknown +
                                          Male04 + Male511 + Male1217 + Male1859 +
                                          Male60ormore + MaleUnknown,
                               
                               hasbreak = ifelse(Total - totGen == 0, "yes", "no" ))



if( nrow(demographics1) ==  0 ){
  cat(paste0("There's no recorded Gender disaggregation for Forcibly Displaced People across Borders in ",country_asylum_iso3c  ))
  
} else {

  tot <- format( sum(demographics1$Total) ,  big.mark=",")
  totprop <-   format( round( sum(demographics1$totGen) / 
      sum(demographics1$Total )  *100,1),  big.mark=",")  
  
  if (totprop == 0 ) {
    cat(paste0("There's no recorded Gender disaggregation for all of the ",tot, " persons in", country_asylum_iso3c  ))
    
  } else {
    #names(demographics)
    pyramid <-  demographics1[ demographics1$Year == max(demographics1$Year),
                              c(
                                  "Female04",
                                  "Female511",
                                  "Female1217",
                                  "Female1859",
                                  "Female60ormore",
                                  "FemaleUnknown",
                                 # "FemaleTotal",
                                  "Male04",
                                  "Male511",
                                  "Male1217",
                                  "Male1859",
                                  "Male60ormore",
                                  "MaleUnknown"#,
                                 # "MaleTotal"       
                                 )]  
    
    pyramid2 <- data.frame(lapply(pyramid, function(x) { as.numeric( gsub("NA", "0", x)) })) |>
      pivot_longer(
        cols = Female04:MaleUnknown,
        names_to = "Class",
        values_to = "Sum",
        values_drop_na = TRUE
      ) 
    
    pyramid3 <- as.data.frame(aggregate(pyramid2$Sum,
                                              by = list(pyramid2$Class#, pyramid2$REGION_UN
                                                        ),
                                              sum))
    names(pyramid3)[1] <- "Class"
    names(pyramid3)[2] <- "Count"
    
    pyramid3 <- pyramid3 |> 
      mutate(gender = case_when(str_detect(Class, "Male") ~ "Male",
                                str_detect(Class, "Female") ~ "Female")) |> 
      mutate(age = case_when(str_detect(Class, "04") ~ "0-4",
                             str_detect(Class, "511") ~ "5-11",
                             str_detect(Class, "1217") ~ "12-17",
                             str_detect(Class, "1859") ~ "18-59",
                             str_detect(Class, "60") ~ "60+",
                             str_detect(Class, "Unknown") ~ "Unknown")) 
    
    pyramid3$pc <- pyramid3$Count / sum(pyramid3$Count) * 100
    pyramid3$age <- factor(pyramid3$age, levels = c("0-4", "5-11",  "12-17",  "18-59", "60+", "Unknown"))
    
    pyramidplot <- ggplot(pyramid3, aes(x = age, 
                         fill = gender,
                          y = ifelse(test = gender == "Female",
                                yes = -pc, no = pc)) ) + 
      geom_bar(stat = "identity") +
      geom_label(aes(x = age,
                     y = ifelse(test = gender == "Female",
                                yes = -pc -5 , no = pc),
                    label =  paste0(format(round(pc, 1),  big.mark=","),"%") 
                    ),
                 hjust = 0,
                 vjust = 0.5,
                 colour = "black",
                 fill = NA,
                 label.size = NA,
                # family = "Lato",
                 size = 4) +
      scale_y_continuous(labels = abs, limits = max(pyramid3$pc) * c(-1,1)) +
      labs(title = paste0("Population Pyramid for Forcibly Displaced People" ),
           
           subtitle = paste0("As of ", year, 
                             ", gender disaggregation is available for ", totprop, " % of the ",tot,
                             " individuals in", country_asylum_iso3c),
           x = "", 
           y = "Percent of population",
           caption =  "Data: UNHCR Refugee Population Statistics Database; Visualisation: UnhcrDataPackage.\n Forced Displacement includes Refugees, Asylym Seekers and Venezuelan Displaced Abroad Population Groups.") +
      scale_colour_manual(values = c("#126db4","#01ab91"), # based on Asia Report
                          aesthetics = c("colour", "fill")) +
      coord_flip()+
      theme_unhcr(font_size = 12)  + ## Insert UNHCR Style
      theme(panel.grid.major.x = element_line(color = "#cbcbcb"), 
                panel.grid.major.y = element_blank())
    
    print(pyramidplot)
 }
 }
}
```

    
```{r examples-plot_ctr_pyramid, fig.retina = 2, fig.width = 8, fig.asp = 0.618, fig.align = "center", dev = "ragg_png", out.width = "90%"}
# 
plot_ctr_pyramid(year = 2021,
                            country_asylum_iso3c = "VEN",
                            pop_type = c("REF", "ASY")
         )

``` 



## Asylum Processing

    
## Refugee Recognition rate

    
## Refugee Status Determination Application

    
## Refugees accessing durable solutions


## Solution Evolution


## Resettlement Trend


## Population origin-destination

    
## Proportion of the population who are refugees, by country of origin

    
## Ratio Refugee Vs Host population

    
## Ratio Refugee Migrant

    
    
--- 

# Regional Questions


## Biggest decrease in Refugee Population

    
## Biggest increase in Refugee Population

    
## Comparison over time by Region

    
## Evolution over time of the different Population of Concern

    
## Evolution by Country of Origin

    
## Refugee Over time

    
## Smootheed Evolution over time

## Mapping Refugee Location 


## Mapping IDP Location  
    
## Map Venezuelan  
    
## Refugee Chart Race
     


--- 

# Template

```{r function-template_CtryFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "Country_Factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param UNHCRBureau Bureau that covers all the countrie factsheet to generate
#' 
#' @export
#'

template_CtryFactsheet <- function(year = 2021,
                      UNHCRBureau) {
 
}

```


```{r function-template_RegFactsheet}
# usethis::use_rmarkdown_template(
#   template_name = "Regional_Factsheet",
#   template_dir = NULL,
#   template_description = "Key Statistical Facts for each Country",
#   template_create_dir = TRUE
# )
#' Generate all country factsheet 
#' 
#' @param year Numeric value of the year (for instance 2020)
#' @param UNHCRBureau Bureau that covers all the countrie factsheet to generate
#' 
#' @export
#'

template_RegFactsheet <- function(year = 2021,
                      UNHCRBureau) {
 
}

```



# Update Dataset
    
```{r function-update_dataset}
#' Update the data on the package
#' 
#' The function pull the data from https://data.humdata.org/dataset/unhcr-population-data-for-world and do a few adjustement before inserting them in the package
#' 
#' @importFrom ckanr   ckanr_setup  package_search
#' @importFrom purrr  pluck  walk
#' @importFrom readr read_csv
#' @importFrom fs path path_file
#' @importFrom here here
#' @importFrom plyr rename
#' @importFrom reshape2 melt
#' @importFrom sinew makeOxygen
#' @importFrom tools resaveRdaFiles
#' 
#' @return nothing just refresh the data .rda
#' 
#' @export
update_dataset <- function(){
  


    ckanr::ckanr_setup("https://data.humdata.org")
    
    ckanr::package_search("name:unhcr-population-data-for-world", as = "table") %>% 
      purrr::pluck("results", "resources", 1, "url") %>% 
      purrr::walk(~ckanr::ckan_fetch(., store = "disk", path = fs::path("data-raw", fs::path_file(.))))
    
    read_sans_hxl <- function(file, ...) {
      hdrs <- readr::read_csv(file, n_max = 0) %>% names()
      
      readr::read_csv(file, col_names = hdrs, skip = 2, ...)
    }



    ## Displaced ##########
    cat(paste0("Reading end_year_population_totals_residing_world \n"))
    end_year_population_totals <- read_sans_hxl(file =  here::here("data-raw","end_year_population_totals_residing_world.csv"))
    
    
    # Rename column to have proper Variable names
    end_year_population_totals <- plyr::rename(end_year_population_totals, c("Country of Origin Code"="CountryOriginCode",
                                           "Country of Asylum Code"="CountryAsylumCode", 
                                           "Country of Origin Name"="CountryOriginName",
                                           "Country of Asylum Name"="CountryAsylumName", 
                                           "Refugees"="REF", 
                                           "Internally displaced persons"="IDP", 
                                           "Asylum seekers"="ASY",
                                           "Others of concern to UNHCR"="OOC",
                                           "Stateless Persons"="STA",    
                                          #  "Venezuelans Displaced Abroad"="VDA"
                                           "Host community" = "HCO",
                                           "Other people in need of international protection"="OIP"))
    cat(names(end_year_population_totals))
    
    sinew::makeOxygen(end_year_population_totals, add_fields = "source")
    
    save(end_year_population_totals, file =  here::here("data","end_year_population_totals.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","end_year_population_totals.RData"),compress="bzip2")
    
    cat(paste0("Saving end_year_population_totals_residing_world \n"))
     
    
    
    
    ## Create a long format for the dataset
    
    end_year_population_totals_long <- reshape2::melt(end_year_population_totals,
                                               # ID variables - all the variables to keep but not split apart on
                                               id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                               # The source columns
                                               measure.vars=c("REF","IDP", "ASY","OOC","STA","OIP","HCO"),
                                               # Name of the destination column that will identify the original
                                               # column that the measurement came from
                                               variable.name="Population.type",
                                               value.name="Value")
    
    end_year_population_totals_long <- end_year_population_totals_long[end_year_population_totals_long$Value > 0, ]
    
    end_year_population_totals_long$Population.type.label <- ""
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="IDP"] <- "Internally displaced persons"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern to UNHCR"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="OIP"] <- "Other people in need of international protection"
    end_year_population_totals_long$Population.type.label[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
    end_year_population_totals_long$Population.type.label.short <- ""
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="REF"] <- "Refugees"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="IDP"] <- "IDPs"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="ASY"] <- "Asylum seekers"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OOC"] <- "Others of concern"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="STA"] <- "Stateless Persons"
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="OIP"] <- "In need of int. protect."
    #end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="VDA"] <- "Venezuelans Abroad"
    end_year_population_totals_long$Population.type.label.short[end_year_population_totals_long$Population.type=="HCO"] <- "Host community"
    
      
    save(end_year_population_totals_long, file =  here::here("data","end_year_population_totals_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","end_year_population_totals_long.RData"),compress="xz") 
    
    cat(paste0("Saving long format for  end_year_population_totals_residing_world \n"))
    
    
    ## Solutions ##########
    
    solutions_residing <- read_sans_hxl(file =  here::here("data-raw","solutions_residing_world.csv"))
    
    cat(paste0("Reading solutions_residing_world \n"))
    
    sinew::makeOxygen(solutions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    solutions <- plyr::rename(solutions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                                             "Country of Origin Name"="CountryOriginName",
                                                                             "Country of Asylum Name"="CountryAsylumName", 
                                                                             "Resettlement arrivals"="RST",
                                                                             "Refugee returns"="RET",
                                                                             "Naturalisation"="NAT",
                                                                             "IDP returns"="RDP" ))
    
    save(solutions, file =  here::here("data","solutions.RData"))
    sinew::makeOxygen(solutions, add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions.RData"),compress="bzip2")
    
    cat(paste0("Saving solutions_residing_world \n"))
    
    solutions_long <- reshape2::melt(solutions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                                      # The source columns
                                                      measure.vars=c("NAT","RST", "RET","RDP"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Solution.type",
                                                      value.name="Value")
    
    solutions_long <- solutions_long[solutions_long$Value > 0, ]
    
    
    solutions_long$Solution.type.label <- ""
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RST"] <- "Resettlement arrivals"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="NAT"] <- "Naturalisation"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RET"] <- "Refugee returns"
    solutions_long$Solution.type.label[solutions_long$Solution.type=="RDP"] <- "IDP returns"
    
    save(solutions_long , file =  here::here("data","solutions_long.RData"))
    sinew::makeOxygen(solutions_long , add_fields = "source")
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","solutions_long.RData"),compress="xz")
    
    cat(paste0("Saving long format for solutions_residing_world \n"))
    
    ## Demographics ##########
    
    demographics_residing <- read_sans_hxl(file =  here::here("data-raw","demographics_residing_world.csv"))
    
    cat(paste0("Reading demographics_residing_world \n"))
    #names(demographics_residing)
    
    sinew::makeOxygen(demographics_residing, add_fields = "source")
    # Rename column to have proper Variable names
    demographics <- plyr::rename(demographics_residing, c("Country of Origin Code"="CountryOriginCode",
                                                             "Country of Asylum Code"="CountryAsylumCode", 
                                                             "Country of Origin Name"="CountryOriginName",
                                                             "Country of Asylum Name"="CountryAsylumName",  
                                                             "Population Type"= "Population.type",
                                                             "Female 0-4"="Female04", 
                                                             "Female 5-11"="Female511", 
                                                             "Female 12-17"="Female1217", 
                                                             "Female 18-59"="Female1859",
                                                             "Female 60 or more"="Female60ormore",
                                                             "Female Unknown"="FemaleUnknown",
                                                             "Female Total"="FemaleTotal", 
                                                             "Male 0-4"="Male04", 
                                                             "Male 5-11"="Male511", 
                                                             "Male 12-17"="Male1217", 
                                                             "Male 18-59"="Male1859",
                                                             "Male 60 or more"="Male60ormore",
                                                             "Male Unknown"="MaleUnknown",
                                                             "Male Total"="MaleTotal")
                                                             )
    
    
    #names(demographics)
    
    demographics$Population.type.label <- ""
    demographics$Population.type.label[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label[demographics$Population.type=="IDP"] <- "Internally displaced persons"
    demographics$Population.type.label[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label[demographics$Population.type=="OOC"] <- "Others of concern to UNHCR"
    demographics$Population.type.label[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label[demographics$Population.type=="VDA"] <- "Venezuelans Displaced Abroad"
    demographics$Population.type.label[demographics$Population.type=="OIP"] <- "Other people in need of international protection"
    demographics$Population.type.label[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label[demographics$Population.type=="RDP"] <- "IDP returns"
    
    demographics$Population.type.label.short <- ""
    demographics$Population.type.label.short[demographics$Population.type=="REF"] <- "Refugees"
    demographics$Population.type.label.short[demographics$Population.type=="IDP"] <- "IDPs"
    demographics$Population.type.label.short[demographics$Population.type=="ASY"] <- "Asylum seekers"
    demographics$Population.type.label.short[demographics$Population.type=="OOC"] <- "Others of Concern"
    demographics$Population.type.label.short[demographics$Population.type=="STA"] <- "Stateless Persons"
    #demographics$Population.type.label.short[demographics$Population.type=="VDA"] <- "Venezuelans Abroad"
    demographics$Population.type.label.short[demographics$Population.type=="OIP"] <- "In need of int. protect."
    demographics$Population.type.label.short[demographics$Population.type=="HCO"] <- "Host community" 
    demographics$Population.type.label.short[demographics$Population.type=="RET"] <- "Refugee returns"
    demographics$Population.type.label.short[demographics$Population.type=="RDP"] <- "IDP returns"
    
    # names(demographics)
    # table(demographics$location, useNA = "ifany")
    # table(demographics$urbanRural, useNA = "ifany")
    # table(demographics$accommodationType, useNA = "ifany")
    # table(demographics$Population.type.label.short, useNA = "ifany")
    
    save(demographics, file =  here::here("data","demographics.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data 
    tools::resaveRdaFiles(here::here("data","demographics.RData"),compress="bzip2")
    
    cat(paste0("Saving demographics_residing_world \n"))
    
    ## RSD Application ########## 
    asylum_applications_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_applications_residing_world.csv"))
    
    cat(paste0("Reading asylum_applications_residing_world \n"))
    sinew::makeOxygen(asylum_applications_residing, add_fields = "source")
    
    # Rename column to have proper Variable names
    asylum_applications <- plyr::rename(asylum_applications_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                        "Country of Asylum Code"="CountryAsylumCode", 
                                                                        "Country of Origin Name"="CountryOriginName",
                                                                        "Country of Asylum Name"="CountryAsylumName", 
                                                                        "Procedure Type"="ProcedureType",                      
                                                                        "Procedure Name"="ProcedureName",                      
                                                                        "Application Type Code"="ApplicationTypeCode",               
                                                                        "Application Type"="ApplicationType",                    
                                                                        "Application Data Type"="ApplicationDataType",               
                                                                        "Application Data"="ApplicationData",                    
                                                                        "Application Average Persons Per Case"="ApplicationAveragePersonsPerCase",
                                                                        "Number of Applications"="NumberApplications" 
    )
    )
    
    asylum_applications$ApplicationType[asylum_applications$ApplicationTypeCode == "V"] <- "Various"
    asylum_applications$ApplicationTypeCode[asylum_applications$ApplicationType == "New and appeal"] <- "NA"
    
    #View(unique(asylum_applications[ ,c("ApplicationTypeCode","ApplicationType")]))
    
    # View(unique(asylum_applications[ ,c("ProcedureType",  "ProcedureName")]))
    # 
    # View(unique(asylum_applications[ ,c("ApplicationDataType","ApplicationData")]))
    
    save(asylum_applications, file =  here::here("data","asylum_applications.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_applications.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_applications_residing_world \n"))
    
    ## RSD Decision ##########
    asylum_decisions_residing <- read_sans_hxl(file =  here::here("data-raw","asylum_decisions_residing_world.csv"))
    
    cat(paste0("Reading asylum_decisions_residing_world \n"))
    
    sinew::makeOxygen(asylum_decisions_residing, add_fields = "source")
    # Rename column to have proper Variable names
    asylum_decisions <- plyr::rename(asylum_decisions_residing, c("Country of Origin Code"="CountryOriginCode",
                                                                   "Country of Asylum Code"="CountryAsylumCode", 
                                                                   "Country of Origin Name"="CountryOriginName",
                                                                   "Country of Asylum Name"="CountryAsylumName", 
                                                                   "Procedure Type"="ProcedureType",                    
                                                                   "Procedure Name"="ProcedureName",                    
                                                                   "Decision Type Code"="DecisionTypeCode",                
                                                                   "Decision Data Type"="DecisionDataType",                
                                                                   "Decision Data"="DecisionData",                     
                                                                   "Decisions Average Persons Per Case"= "DecisionsAveragePersonsPerCase",
                                                                   "Complementary Protection"="ComplementaryProtection",          
                                                                   "Otherwise Closed" ="OtherwiseClosed",                
                                                                   "Total Decided" = "TotalDecided"
                                                                   )
    )
    
    
    # View(unique(asylum_decisions[ ,c("ProcedureType",  "ProcedureName")]))
    # View(unique(asylum_decisions[ ,c("DecisionTypeCode")]))
    
    asylum_decisions$DecisionTypeName <- ""
    asylum_decisions$DecisionTypeCode[is.na(asylum_decisions$DecisionTypeCode) ] <- "NA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FI"] <- "First instance"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "AR"] <- "Re-opened/repeat"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "FA"] <- "First instance and appeal"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "BL"] <- "BL"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "NA"] <- "New applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "RA"] <- "Repeat/reopened applications"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "CA"] <- "CA"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "EO"] <- "US Executive Office of Immigration Review"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "IN"] <- "US Citizenship and Immigration Services"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TR"] <- "TR"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "JR"] <- "Judicial Review "
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "SP"] <- "Subsidiary protection"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TA"] <- "Temporary asylum"
    asylum_decisions$DecisionTypeName[asylum_decisions$DecisionTypeCode == "TP"] <- "Temporary Protection" 
    
    #View(unique(asylum_decisions[ ,c("DecisionTypeCode","DecisionTypeName")])) 
    sinew::makeOxygen(asylum_decisions, add_fields = "source")
    save(asylum_decisions, file =  here::here("data","asylum_decisions.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions.RData"),compress="bzip2")
    
    cat(paste0("Saving asylum_decisions_residing_world \n"))
    
    ## RDS Decision Long format ########
    
    #names(asylum_decisions)
    
    asylum_decisions_long <- reshape2::melt(asylum_decisions,
                                                      # ID variables - all the variables to keep but not split apart on
                                                      id.vars=c("Year", "CountryOriginCode","CountryAsylumCode",
                                                                "CountryOriginName","CountryAsylumName",
                                                                "ProcedureType",  "ProcedureName",
                                                                "DecisionTypeCode","DecisionTypeName",
                                                                "DecisionData","DecisionsAveragePersonsPerCase"),
                                                      # The source columns
                                                      measure.vars=c("Recognized","ComplementaryProtection","OtherwiseClosed","Rejected"),
                                                      # Name of the destination column that will identify the original
                                                      # column that the measurement came from
                                                      variable.name="Decision.output",
                                                      value.name="Value")
    
    asylum_decisions_long <- asylum_decisions_long[asylum_decisions_long$Value > 0, ]
    
    sinew::makeOxygen(asylum_decisions_long, add_fields = "source")
    save(asylum_decisions_long, file =  here::here("data","asylum_decisions_long.RData"))
    # Note: significantly better compression could be obtained
    #by using R CMD build --resave-data
    tools::resaveRdaFiles(here::here("data","asylum_decisions_long.RData"),compress="xz")  
    
    cat(paste0("Saving long format for asylum_decisions_residing_world \n"))
}
```
  
```{r example-update_dataset}
#update_dataset()
```
  
```{r tests-update_dataset}
test_that("update_dataset works", {
  expect_true(inherits(update_dataset, "function")) 
})
```
  


```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library")
```

