---
title: "Adding new Charts in the Librabry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding new Charts in the Librabry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


If you want to add  new Charts in the Library please follow the steps below:  

 1. Start from an High level question

 2. Check that the plot is not there already or check if it is not logged already within [existing issue](https://github.com/Edouard-Legoupil/unhcrdatapackage/issues)

 3.  Create a [new issue](https://github.com/Edouard-Legoupil/unhcrdatapackage/issues/new) in the package to discuss it 

 4. [Fork](https://github.com/Edouard-Legoupil/unhcrdatapackage) the package

 5. Check the dev folder for the dedicated [devnotebook](https://github.com/Edouard-Legoupil/unhcrdatapackage/blob/master/dev/flat_full.Rmd). , develop within the [fusen](https://thinkr-open.github.io/fusen/index.html) 

 6.  Insert a new series of chunk with Fusen Addin

 7. First write your chart as a script and Use the unhcrthemes

 8. Convert it as function with predefined input parameters

 9. Set up an example and  Test everything
 
```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library")
pkgdown::build_site()
```
 

 10.  Add the new chart in the parameterised notebooktemplate 

 11. Submit pull request



