---
title: "Adding new Charts in the Librabry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding new Charts in the Librabry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Start from an Highlevel question

## Check that the plo is not there already

##  Fork the package

## Check the dev folder for the dedeciated Fusen notebook


## Insert a new series of chunk with Fusen Addin


## First write your chart as a script

Use the unhcrthemes

## Convert it as function with predefined nput parameters


## Set up an example

## Add the new chart in the parameterised notebooktemplate 

Adding new Charts in the Library


## Test everything

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Chart Library")
pkgdown::build_site()
```


## Submit a pull equest