---
title: "Refugee Population Region Comparison"
output: 
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Refugee Population Region Comparison}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Note that you can find the source code for all the chart below in the [Repository](https://github.com/unhcr/unhcrdatapackage/tree/master/vignettes).

UNHCR [Population Statistics Database](http://popstats.unhcr.org)  contains data about UNHCR's populations of concern from the year 1951 up to 2014 as well as their general composition by location of residence or origin, their status, their evolution over time.

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      collapse = FALSE,
                      comment = "#>",
                      fig.align = "center")
knitr::opts_chunk$set(fig.width = 9, fig.height = 7)
set.seed(1)
extrafont::loadfonts(quiet=TRUE)
options(scipen = 999) # turn-off scientific notation like 1e+48

### http://web.stanford.edu/~cengel/cgi-bin/anthrospace/great-circles-on-a-recentered-worldmap-in-ggplot
### http://robinlovelace.net/2014/06/22/great-circles-in-rworldmap-ggplot2.html
### http://egallic.fr/maps-with-r/
## https://leonawicz.github.io/gc_animation_example/app_traffic_example.html

## Maybe to be amended with https://github.com/robertgrant/pictogram 

library(maps)
library(geosphere)
library(plyr)

library(sp)
#install.packages("rworldmap")
library(rworldmap)
#install.packages("rgdal")
library(rgdal) 
library(ggplot2) 
library(gpclib)

#library(devtools)
#install_github("dgrtwo/gganimate")
library(gganimate) # https://github.com/dgrtwo/gganimate
library(classInt)
library(tidyverse)
library(RColorBrewer)

# install.packages("ggalluvial")
library(ggalluvial)

library(unhcrdatapackage)
library(unhcRstyle)

```

# Displacement Statistics

## The Population Database

UNHCR's populations of concern status includes:

 *  __Refugees__ include individuals recognized under the 1951 Convention relating to the Status of Refugees; its 1967 Protocol; the 1969 OAU Convention Governing the Specific Aspects of Refugee Problems in Africa; those recognised in accordance with the UNHCR Statute; individuals granted complementary forms of protection; or those enjoying temporary protection. Since 2007, the refugee population also includes people in a refugee-like situation.

 *  __Asylum-seekers__ are individuals who have sought international protection and whose claims for refugee status have not yet been determined, irrespective of when they may have been lodged.

 *  __Internally displaced persons (IDPs)__ are people or groups of individuals who have been forced to leave their homes or places of habitual residence, in particular as a result of, or in order to avoid the effects of armed conflict, situations of generalised violence, violations of human rights, or natural or man-made disasters, and who have not crossed an international border. For the purposes of UNHCR's statistics, this population only includes conflict-generated IDPs to whom the Office extends protection and/or assistance. Since 2007, the IDP population also includes people in an IDP-like situation. For global IDP estimates, see www.internal-displacement.org.

 *  __Returned refugees__ are former refugees who have returned to their country of origin spontaneously or in an organised fashion but are yet to be fully integrated. Such return would normally only take place in conditions of safety and dignity.

 *  __Returned IDPs__ refer to those IDPs who were beneficiaries of UNHCR's protection and assistance activities and who returned to their areas of origin or habitual residence during the year.

 *  __Stateless persons__ are defined under international law as persons who are not considered as nationals by any State under the operation of its law. In other words, they do not possess the nationality of any State. UNHCR statistics refer to persons who fall under the agency’s statelessness mandate because they are stateless according to this international definition, but data from some countries may also include persons with undetermined nationality.

 *  __Others of concern__ refers to individuals who do not necessarily fall directly into any of the groups above, but to whom UNHCR extends its protection and/or assistance services, based on humanitarian or other special grounds.

## Chronogramme

The MENA region have seen a series of conflict over the past 15 years that have generated large scale population displacement. There is currently 4 major conflict in the region and additional ones outside that have or are generating population displacement.


```{r time1, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
wid <- 0.15 # width of annotation bars
wars <- data_frame(
 name = c( "US intervention in Afghanistan", 
           "Iraqi Insurgency",
           "US Surge in Iraq",
           "Iraq Civil War", 
           "Houthi insurgency in Yemen",
           "Yemeni Civil War",
           "Conflict in Syria",
           "First Libyan Civil War", 
           "Factional violence in Libya",
           "Second Libyan Civil War",
           "Northern Mali conflict"),
 start = as.Date(c( "7/10/2001",
                    "20/3/2003",
                    "01/02/2006",
                    "01/11/2011",
                    "18/06/2004", 
                    "06/02/2015",
                    "20/3/2011", 
                    "15/02/2011",
                    "01/11/2011", 
                    "16/05/2014", 
                    "16/01/2012"), 
 format = "%d/%m/%Y"),
 end = as.Date(c("28/12/2014",
                 "01/02/2006",
                 "01/11/2011",
                 "22/08/2018",
                 "06/02/2015", 
                 "22/08/2018",
                 "22/08/2018", 
                 "23/10/2011",
                 "16/05/2014",
                 "22/08/2018",
                 "22/08/2018"),
 format = "%d/%m/%Y"),
 lead = c( "Afghanistan", "Iraq", "Iraq", "Iraq",  "Yemen", "Yemen","Syria", "Libya", "Libya", "Libya", "Mali")
) %>%
 mutate(name_seq = n():1,
 ystart = wid * name_seq + 0.12, 
 yend = ystart + wid )

countries <- c("Afghanistan", "Iraq", "Syria", "Yemen", "Libya", "Mali")
palette <- brewer.pal(6, "Set1")
names(palette) <- countries
 
ggplot() +
 geom_rect(data = wars, aes(xmin = start, xmax = end, ymin = ystart, ymax = yend, fill = lead), alpha = 0.3) +
 geom_text(data = wars, aes(x = end, y = (yend + ystart) / 2, label = name), colour = "black", hjust = 1, nudge_x = 100, size = 3) +
 ggtitle("") +
 labs(x = "", x = "", caption = "") +
 scale_colour_manual(values = palette) +
 scale_fill_manual(values = palette, guide = "none") +
 theme_bw() +
 theme(plot.caption = element_text(colour = "grey50"),
      axis.line = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.y = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank()) + 
 annotate("text", x = as.Date("2001/9/11"),
          y = 0.145, hjust = 0, 
          colour = "grey50", 
          size = 3,
          label = "Chronogram of the conflict that generated the largest displacements since Sept 2001.")

#direct.label(p)

``` 

```{r data1, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}

# Time series
time_series <-  unhcrdatapackage::end_year_population_totals

reference <- unhcrdatapackage::reference

time_series2 <- reshape2::melt(time_series,
                                           # ID variables - all the variables to keep but not split apart on
                                           id.vars=c("Year", "CountryOriginCode","CountryAsylumCode","CountryOriginName","CountryAsylumName" ),
                                           # The source columns
                                           measure.vars=c("REF","IDP", "ASY","OOC","STA","VDA"),
                                           # Name of the destination column that will identify the original
                                           # column that the measurement came from
                                           variable.name="Population.type",
                                           value.name="Value") 
``` 

```{r data2, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}

data <- merge(x = time_series2, by.x="CountryOriginCode", y = reference, by.y= "iso_3", all.x = TRUE)

data <- data[!rowSums(is.na(data["CountryOriginCode"])), ]
data <- data[!rowSums(is.na(data["CountryAsylumCode"])), ]
data <- data[!rowSums(is.na(data["Year"])), ]
data <- data[!rowSums(is.na(data["Value"])), ]
## taking out locations that do not match countries or territories
data <- data[ !(data$CountryOriginName %in% c("","Various/Unknown","Stateless","Tibetan") ) , ]
data <- data[ !(data$CountryAsylumName %in% c("","Various/Unknown","Stateless","Tibetan") ) , ]
``` 

```{r data3, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}

## only arcs representing refugees
#data <- data[  (data$Population.type == "REF") , ]
# 
# #str(data)
# 
# # add latlons from both in and out
# data <- merge(data, ctryall, by.x , by.x = "Origin", by.y = "ctry2" , all.x = TRUE )
# data <- merge(data, ctryall, by.x , by.x = "Asylum", by.y = "ctry2" , all.x = TRUE )
# #rm(ctryall)
# 
# ## Build uniqueID for Arc
# data$arc <- paste("from-",data$Origin,"-to-", data$Asylum, sep = "")
# data$arc2 <- paste("from-",data$Origin,"-to-", data$Asylum, "-for-", data$Population.type , sep = "")
# arc <- unique(data[ c("arc", "longitude.x", "latitude.x", "longitude.y", "latitude.y")])
# 
# #### Create curved routes##############################
# # calculate routes -- Dateline Break FALSE, otherwise we get a bump in the shifted ggplots
# gcircles <- gcIntermediate(arc[,c('longitude.x', 'latitude.x')], arc[,c('longitude.y', 'latitude.y')], 
#                       n = 80, 
#                       breakAtDateLine = FALSE, 
#                       addStartEnd = TRUE, 
#                       sp  = TRUE)
# 
# # http://docs.ggplot2.org/0.9.3.1/fortify.map.html
# gcircles  <- ldply(gcircles@lines, fortify)
# 
# #### merging back with Value for each arc
# arc$id <- as.character(c(1:nrow(arc))) # that rts.ff$id is a char
# gcircles <- merge(gcircles, arc, all.x = TRUE, by = "id") # join attributes, we keep them all, just in case
# 
# 
worldmap <- getMap() # load the map data class(s) # what type of are we dealing with?
## need to merge with MENA dataframe in order to facet the map
# names(worldmap)
# mena$mena.x <- mena$mena
# mena$hcr_subregion <- mena$mena
#worldmap <- merge(x = worldmap , y = mena, by.x = "ISO_A3" , by.y = "ISO3166A3" , all.x = TRUE)

data$Value[data$Value < 0] <- 0

#data$Value.class <- as.factor(findCols(classIntervals(data$Value, n = 7, style = "pretty")))

#data$Value.class <- as.factor(findCols(classIntervals(data$Value, n = 6, style = "fixed", fixedBreaks = c(0, 500, 5000, 10000, 25000,50000, 75000, 100000, 125000,150000,  100000000))))

data$Value.class <- cut(data$Value, breaks = c(0, 1000, 5000,       10000,          25000,           50000,            100000,             200000, 100000000),include.lowest = TRUE)

#                         labels = c("0.to.5000", "5000.to.10000", "10000.to.25000", "25000.to.50000", "50000.to.100000", "100000.to.200000", "over.200000"),
# data$Value.class <- factor(data$Value.class, levels = c("Less.than.5000","5000.to.10000","10000.to.25000","25000.to.50000","50000.to.100000","100000.to.200000","Over.200000") )

```

## from Table to Visualisation

The elements present below have been developed to facilitate the understanding of the statistics generated on displaced population in Middle East & North Africa (MENA). The objective is to identify  the most important trend both in terms of temporal and spatial approach in order to support advocacy. 




# Temporal Analysis 

[Sankey Diagram](https://en.wikipedia.org/wiki/Sankey_diagram) are a specific type of flow diagram, in which the width of the arrows is shown proportionally to the flow quantity. This type of dataviz put a visual emphasis on the __major change of flows profile__ of refugees within multiple countries or regions.

## Asylum Seekers & Refugees in MENA 

```{r sankeyregion, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

popstats <- data %>%
  filter(  Population.type %in% c("REF", "ASY") &
            # UNHCRBureau == "MENA" &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020")
        ) %>%
  group_by( Year, hcr_subregion) %>%
  summarise(refugees = sum(Value))
popstats$hcr_subregion <- as.character(popstats$hcr_subregion)
popstats$hcr_subregion[is.na(popstats$hcr_subregion)] <- "Other regions"

# regions <- c("Other regions", "Middle-East", "North Africa", "Gulf")
# paletteregion <- brewer.pal(4, "Set3")
# names(paletteregion) <- regions


ggplot(data = popstats, 
       aes(x = Year, 
           y = refugees, 
           alluvium = hcr_subregion, 
           stratum = hcr_subregion)) +
  ggtitle("About a third of Global Refugee & Asylum seekers population are in MENA") + 
  geom_alluvium(aes(fill = hcr_subregion),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Region")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character(hcr_subregion), NA),  stat = "stratum", 
                                size = 3, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```



```{r sankey1, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
popstats <- data %>%
  filter( hcr_subregion == "Middle East" & 
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020")
        ) %>%
  group_by( Year, CountryAsylumName) %>%
  summarise(refugees = sum(Value))

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium = CountryAsylumName, stratum = CountryAsylumName)) +
  ggtitle("Syria has been the largest refugee hosting country for 5 years") + 
  geom_alluvium(aes(fill = CountryAsylumName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character(CountryAsylumName), NA),  stat = "stratum", 
                                size = 3, direction = "y", nudge_y = -0.05, vjust = 0.5, segment.size = 0.1)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```



```{r sankeyorigin1, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
popstats <- data %>%
  filter( hcr_subregion == "Middle East" & 
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020") &
          Value > 10000  ) %>%
  group_by( Year, CountryOriginName) %>%
  summarise(refugees = sum(Value))

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium =  CountryOriginName, stratum =  CountryOriginName)) +
  ggtitle("Syria is the the main country of CountryOriginName for Refugees in Middle East") + 
  geom_alluvium(aes(fill =  CountryOriginName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character( CountryOriginName), NA),  stat = "stratum",
                                size = 3, direction = "y", nudge_y = -0.05, vjust = 0.5, segment.size = 0.1)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) +
 annotate("text", x = 2003 , y = -0.6, hjust = 0,  colour = "grey50", size = 3, label = "The chart only displays origin with more than 10,000.")

```





```{r sankey2, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
popstats <- data %>%
  filter( hcr_subregion == "North Africa" & 
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020")
        ) %>%
  group_by( Year, CountryAsylumName) %>%
  summarise(refugees = sum(Value))


ggplot(data = popstats, aes(x = Year, y = refugees, alluvium = CountryAsylumName, stratum = CountryAsylumName)) +
  ggtitle("The impact of the Syria crisis can be observed in North Africa") + 
  geom_alluvium(aes(fill = CountryAsylumName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character(CountryAsylumName), NA),  stat = "stratum", 
                                size = 3, direction = "y", nudge_y = -0.05, vjust = 0.5, segment.size = 0.0)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```

```{r sankeyorigin2, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

popstats <- data %>%
  filter( hcr_subregion == "North Africa" & 
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020") &
          Value > 10000  ) %>%
  group_by( Year, CountryOriginName) %>%
  summarise(refugees = sum(Value))


ggplot(data = popstats, aes(x = Year, y = refugees, alluvium =  CountryOriginName, stratum =  CountryOriginName)) +
  ggtitle("Syria is now the main country of Origin in North Africa") + 
  geom_alluvium(aes(fill =  CountryOriginName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2017, as.character( CountryOriginName), NA),  stat = "stratum", 
                                size = 3, direction = "y", nudge_y = -0.05, vjust = 1, segment.size = 0.1)) +
#  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2006, as.character( CountryOriginName), NA),  stat = "stratum", size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) +
 annotate("text", x = 2003 , y = -10000, hjust = 0,  colour = "grey50", size = 3, label = "The chart only displays origin with more than 10,000 Refugees & Asylum Seekers.")

```



```{r sankey3, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
popstats <- data %>%
  filter(  CountryAsylumName %in% c("Saudi Arabia", "Yemen", "Kuwait") &
           Value > 1000 &
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020")
        ) %>%
  group_by( Year, CountryAsylumName) %>%
  summarise(refugees = sum(Value))

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium = CountryAsylumName, stratum = CountryAsylumName)) +
  ggtitle("In the Gulf, only Yemen is hosting large numbers of refugees") + 
  geom_alluvium(aes(fill = CountryAsylumName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
 # ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character(CountryAsylumName), NA),  stat = "stratum",  size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2008, as.character(CountryAsylumName), NA),  stat = "stratum", 
                                size = 3, direction = "y", nudge_y = -0.05, vjust = 0.5, segment.size = 0.1)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) +
 annotate("text", x = 2003 , y = -10000, hjust = 0,  colour = "grey50", size = 3, label = "The chart only displays asylum countries with more than 1000 Refugees & Asylum Seekers")

```
```{r sankeyorigin3, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
popstats <- data %>%
  filter( CountryAsylumName %in% c("Saudi Arabia", "Yemen", "Kuwait") &
        Population.type %in% c("REF", "ASY") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020") &
          Value > 5000  ) %>%
  group_by( Year, CountryOriginName) %>%
  summarise(refugees = sum(Value))

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium =  CountryOriginName, stratum =  CountryOriginName)) +
  ggtitle("Most Refugees in the Gulf are Somalis") + 
  geom_alluvium(aes(fill =  CountryOriginName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Countries")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2014, as.character( CountryOriginName), NA),  stat = "stratum", 
                                size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2007, as.character( CountryOriginName), NA),  stat = "stratum",
                                size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184"))  +
 annotate("text", x = 2003 , y = -10000, hjust = 0,  colour = "grey50", size = 3, label = "The chart only displays asylum countries with more than 5000 Refugees & Asylum Seekers")

```

## Internally displaced persons (IDPs) in MENA 

```{r sankeyregionidp, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

popstats <- data %>%
  filter(  Population.type == "IDP" &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020")
        ) %>%
  group_by( Year, hcr_subregion) %>%
  summarise(refugees = sum(Value))
popstats$hcr_subregion <- as.character(popstats$hcr_subregion)
popstats$hcr_subregion[is.na(popstats$hcr_subregion)] <- "Other regions"

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium = hcr_subregion, stratum = hcr_subregion)) +
  ggtitle("One quarter of all IDP's worldwide are in the MENA Region") + 
  geom_alluvium(aes(fill = hcr_subregion),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Region")   + 
  #scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
#  ggrepel::geom_text_repel( aes(label = hcr_subregion,  stat = "stratum",                                  size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2016, as.character(hcr_subregion), NA),  stat = "stratum",
                                size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```

```{r sankeycountryidp, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

popstats <- data %>%
  filter(  Population.type == "IDP" &
        UNHCRBureau  %in% c("MENA") &
        Year %in% c("2003","2004","2005","2006","2007","2008","2009","2010",
                    "2011","2012","2013","2014","2015","2016","2017","2018","2019","2020") & 
          Value > 0 ) %>%
  group_by( Year, CountryOriginName) %>%
  summarise(refugees = sum(Value))

ggplot(data = popstats, aes(x = Year, y = refugees, alluvium = CountryOriginName, stratum =  CountryOriginName)) +
  ggtitle("The addition of Syrian & Yemen has trippled the IDP population in MENA") + 
  geom_alluvium(aes(fill =  CountryOriginName),  alpha = .75, color = "white", decreasing = FALSE) +
  scale_y_continuous(labels = format_si()) +
  theme_bw() +
  labs( y = "# of Refugees", fill = "Hosting Region")   + 
 # scale_colour_manual(values = paletteregion) +
  scale_fill_brewer(type = "qual", palette = "Set3") +  #,  guide = FALSE+
#  ggrepel::geom_text_repel( aes(label =  CountryOriginName,  stat = "stratum",                                  size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  ggrepel::geom_text_repel( aes(label = ifelse(Year == 2017, as.character( CountryOriginName), NA),  stat = "stratum",
                                size = 4, direction = "y", nudge_x = .15, hjust = 0, segment.size = 0.2)) +
  theme(legend.position = "none") +
  theme( axis.text.x = element_text( hjust = 0),
         plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
         plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
         legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
         panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```


# From Where ? Spatial Flow Visualisation   



```{r map1, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                     data$CountryOriginName == "Syrian Arab Rep." &
                                     data$Year == "2017" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees from Syria" , subtitle = "", caption = "", x = NULL, y = NULL) +
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   geom_line(aes(long,lat,group = group, size = Value.class, alpha = .75, colour = "white"),
#             arrow = arrow(length = unit(0.05,"cm"), ends = "first", type = "closed"), data = gcircles.2017) + 
#   scale_size_discrete(name = "Magnitude",
#                       labels = c("Less.than.5000","5000.to.10000","10000.to.25000","25000.to.50000","50000.to.100000","100000.to.200000","Over.200000"),
#                       guide = guide_legend( direction = "vertical",  title.position = 'top',  title.hjust = 0.5, label.hjust = 1, nrow = 1, byrow = T, reverse = FALSE )) +
#   guides(alpha= FALSE, color = FALSE ) +
#  # scale_y_continuous(breaks = (-2:2) * 30) +
#  # scale_x_continuous(breaks = (-4:4) * 45) +
#  # coord_map("ortho", orientation = c(30, 30, 10)) +
#   ylim(-20, 90) +
#   xlim(-160, 160) +
#   coord_equal() +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) +
#  annotate("text", x = -20 , y = -160, hjust = 0,  colour = "grey50", size = 3, label = "The chart only displays asylum countries with more than 5000 Refugees & Asylum Seekers")

```


## Map for 2017 to Syria Situation Countries

```{r map11, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                     data$UNHCRBureau == "MENA" &
                                     data$Year == "2020" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees" , subtitle = "", caption = "UNHCR", x = NULL, y = NULL) +
#   
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   
#   # arc
#   geom_line(aes(long,lat,group = group, size = Value.class, color = CountryOriginName ),
#             arrow = arrow(length = unit(0.1,"cm"), ends = "first", type = "closed"), 
#             data = gcircles.2017) + 
#   # , linejoin = 'round mitre'
#   
#   # Adding points asylum - Origin with different color 
#  # geom_point(aes(longitude.x, latitude.x),data = arc[], alpha = 0.8, size = 1, colour = "blue") +
#  # geom_point(aes(longitude.y, latitude.y),data = arc, alpha = 0.8, size = 1, colour = "red") +
#   
#   
#   # set theme as organised above
#   scale_y_continuous(breaks = (-2:2) * 30) +
#   scale_x_continuous(breaks = (-4:4) * 45) +
#   coord_map("ortho", orientation = c(30, 30, 10)) +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```

## Map for 2017 from North Africa Countries

```{r map2, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                     data$mena.x == "North Africa" &
                                     data$Year == "2020" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees" , subtitle = "", caption = "UNHCR", x = NULL, y = NULL) +
#   
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   
#   # arc
#   geom_line(aes(long,lat,group = group, size = Value.class, color = CountryOriginName ),
#             arrow = arrow(length = unit(0.1,"cm"), ends = "first", type = "closed"), 
#             data = gcircles.2017) + 
#   # , linejoin = 'round mitre'
#   
# 
#   
#   # Adding points asylum - Origin with different color 
#  # geom_point(aes(longitude.x, latitude.x),data = arc[], alpha = 0.8, size = 1, colour = "blue") +
#  # geom_point(aes(longitude.y, latitude.y),data = arc, alpha = 0.8, size = 1, colour = "red") +
#   
#   
#   # set theme as organised above
#   scale_y_continuous(breaks = (-2:2) * 30) +
#   scale_x_continuous(breaks = (-4:4) * 45) +
#   coord_map("ortho", orientation = c(30, 30, 10)) +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```

## Map for 2017 from North Africa Countries

```{r map22, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                     data$hcr_subregion == "North Africa" &
                                     data$Year == "2020" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees" , subtitle = "", caption = "UNHCR", x = NULL, y = NULL) +
#   
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   
#   # arc
#   geom_line(aes(long,lat,group = group, size = Value.class, color = CountryOriginName ),
#             arrow = arrow(length = unit(0.1,"cm"), ends = "first", type = "closed"), 
#             data = gcircles.2017) + 
#   # , linejoin = 'round mitre'
#   # Adding points asylum - Origin with different color 
#  # geom_point(aes(longitude.x, latitude.x),data = arc[], alpha = 0.8, size = 1, colour = "blue") +
#  # geom_point(aes(longitude.y, latitude.y),data = arc, alpha = 0.8, size = 1, colour = "red") +
#   
#   
#   # set theme as organised above
#   scale_y_continuous(breaks = (-2:2) * 30) +
#   scale_x_continuous(breaks = (-4:4) * 45) +
#   coord_map("ortho", orientation = c(30, 30, 10)) +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```

## Map for 2017 from Gulf Countries

```{r map3, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                    # data$mena.x == "Gulf" &
                                     data$Year == "2020" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees" , subtitle = "", caption = "UNHCR", x = NULL, y = NULL) +
#   
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   
#   # arc
#   geom_line(aes(long,lat,group = group, size = Value.class, color = CountryOriginName ),
#             arrow = arrow(length = unit(0.1,"cm"), ends = "first", type = "closed"), 
#             data = gcircles.2017) + 
#   # , linejoin = 'round mitre'
#   
# 
#   
#   # Adding points asylum - Origin with different color 
#  # geom_point(aes(longitude.x, latitude.x),data = arc[], alpha = 0.8, size = 1, colour = "blue") +
#  # geom_point(aes(longitude.y, latitude.y),data = arc, alpha = 0.8, size = 1, colour = "red") +
#   
#   
#   # set theme as organised above
#   scale_y_continuous(breaks = (-2:2) * 30) +
#   scale_x_continuous(breaks = (-4:4) * 45) +
#   coord_map("ortho", orientation = c(30, 30, 10)) +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```


## Map for 2017 to Gulf Countries

```{r map33, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}

data.ref.2017.frommena <- data[   which(data$Population.type == "REF" &
                                     data$UNHCRBureau == "MENA" &
                                     data$Year == "2020" &
                                     data$Value > 1000 ) , ]
# gcircles.2017 <- merge(x = gcircles, y = data.ref.2017.frommena, by = "arc", all.y = TRUE )
# 
# ggplot() +
#   labs(title = "Refugees" , subtitle = "", caption = "UNHCR", x = NULL, y = NULL) +
#   
#   geom_polygon(aes(long, lat, group = group), size = 0.3, fill = "#E2C083", colour = "white", data = worldmap) +
#   
#   # arc
#   geom_line(aes(long,lat,group = group, size = Value.class, color = CountryOriginName ),
#             arrow = arrow(length = unit(0.1,"cm"), ends = "first", type = "closed"), 
#             data = gcircles.2017) + 
#   # , linejoin = 'round mitre'
#   
#   # Adding points asylum - Origin with different color 
#  # geom_point(aes(longitude.x, latitude.x),data = arc[], alpha = 0.8, size = 1, colour = "blue") +
#  # geom_point(aes(longitude.y, latitude.y),data = arc, alpha = 0.8, size = 1, colour = "red") +
# 
#   # set theme as organised above
#   scale_y_continuous(breaks = (-2:2) * 30) +
#   scale_x_continuous(breaks = (-4:4) * 45) +
#   coord_map("ortho", orientation = c(30, 30, 10)) +
#   theme_map() + 
#   theme( legend.position = c(0.5, 0.03), legend.text.align = 0, legend.background = element_rect(fill = alpha('white', 0.0)),
#          legend.text = element_text(size = 7, hjust = 0, color = "#4e4d47"), plot.title = element_text(hjust = 0.5, color = "#4e4d47"),
#          plot.subtitle = element_text(hjust = 0.5, color = "#4e4d47", margin = margin(b = -0.1, t = -0.1, l = 2, unit = "cm"), debug = F),
#          legend.title = element_text(size = 8), plot.margin = unit(c(.5,.5,.2,.5), "cm"), panel.spacing = unit(c(-.1,0.2,.2,0.2), "cm"),
#          panel.border = element_blank(), plot.caption = element_text(size = 6, hjust = 0.92, margin = margin(t = 0.2, b = 0, unit = "cm"), color = "#939184")) 

```



# Spatio Temporal Analysis

An animation can be used to present the population movement over time

* This needs still to be adjusted to represent difference in flow betwen years...*

```{r animate, echo=FALSE, warning=FALSE, cache=FALSE, tidy = TRUE, message=FALSE, comment = "",  size="small"}
##################################################################
## Animation 

#frame.to.animate <- ggplot() +
#  geom_polygon(data = world.df, aes(x = long, y = lat, group = group), size = 0.3, fill="#bbdaa4", colour = "grey65") +
#  scale_y_continuous(breaks = (-2:2) * 30) +
#  scale_x_continuous(breaks = (-4:4) * 45) +
#  coord_map("ortho", orientation=c(30, 30, 0))+
#  theme_map() +
#  geom_line(aes(x=long,y=lat,group=group,  color="blue", alpha=0.9, frame = Year),size=Value, data= gcircles) +
#  scale_colour_gradient(low="#fee8c8", high="#e34a33") +
#  geom_point(aes(x=longitude.x, y=latitude.x, frame = Year),data=data.coord, alpha = 0.8, size = 1, colour = "blue") +
#  geom_point(aes(x=longitude.y, y=latitude.y, frame = Year),data=data.coord, alpha = 0.8, size = 1, colour = "red") +
#  geom_text(data = data.coord, aes(x = 28.5, y = 1.5, frame = Year, label = data.coord$Year), color = 'white', size = 12)

# animated.map <- gg_animate(frame.to.animate, interval = 0.005, ani.width = 1200, ani.height = 900, title_frame = FALSE)
# animated.map %>% gg_animate_save("out/animatedmap.gif")
```



