---
title:
output: 
  html_document: 
    code_folding: "hide"
    theme: yeti
    includes:
      before_body: header.html
      after_body: footer.html
---
 

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message=FALSE, 
  warning=FALSE
)

library(tidyverse)
selectedctr <- data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))  %>%
  filter( Year == 2021) %>%
  group_by( UNHCRBureau, SUBREGION, CountryAsylumName) %>%
  summarise(Value2 = sum(Value) ) %>%
 filter( Value2 > 30000) 

## For info, this doc has 3 sub-child with the 7 key charts depending on the level of disaggregation
## ChildWorld.Rmd
## ChildRegion.Rmd
## ChildCountry.Rmd
```


```{r, echo=FALSE, cache = TRUE, message=FALSE, warning=FALSE}
# Population, GDP & GNP per Capita from WorldBank
wb_data <- wbstats::wb( indicator = c("SP.POP.TOTL", "NY.GDP.MKTP.CD", "NY.GDP.PCAP.CD", "NY.GNP.PCAP.CD"),
               startdate = 1990, enddate = 2020, return_wide = TRUE)
# Renaming variables for further matching
names(wb_data)[1] <- "iso_3"
names(wb_data)[2] <- "Year"

wb_data$Year <- as.numeric(wb_data$Year)
```


## Forced Displacement Statistics{.tabset .tabset-pills}

### Intro
<div class="container">
<div class="jumbotron">
<h1 class="title"><span style="color: #0072BC;">__Seven Key Questions__</span></h1>

>  addressed through predefined crafted <span style="color: #0072BC;">__static charts__</span>

</div>
</div> 

  1. How the different __Categories__ of Population of concern to UNHCR are evolving over time?
 
  2. What are the main countries of __Origin__ of Forced Displacement across Borders? 
 
  3. What are the main countries of __Destination__ of Asylum of Forced Displacement across Borders?
  
  4. What are the __Demographics__ profiles of Forcibly Displaced People in relation with the host population? 

  5. Is the asylum __Processing__ capacity in relation with the demand? 
 
  6. What are the trends in terms of __Solutions__? 
  
  7. What is the share of Forcibly Displaced People among total __Migrants__? 

***
Charts can easily be copied as an image as is, or adjusted using a [reproducible source code in R statistical language](https://unhcr-americas.github.io/reproducibility). 

For instance, you can change the title from a _key question_ to a _key message_ or [add annotations](http://www.sthda.com/english/wiki/ggplot2-texts-add-text-annotations-to-a-graph-in-r-software) to __support data storytelling__.

***
The resulting charts can be embedded in reports, fact-sheets, social media or presentations to accompany a narrative / campaign. More information on Forcible Displacement Statistic is available with [UNHCR here](https://www.unhcr.org/refugee-statistics/insights/explainers/forcibly-displaced-pocs.html) and through International Statistical Recommendations on [refugee / asylum seekers](https://unstats.un.org/unsd/demographic-social/Standards-and-Methods/files/Principles_and_Recommendations/International-Migration/2018_1746_EN_08-E.pdf) and [Internally Displaced People](https://www.unhcr.org/statistics/unhcrstats/600188974/international-recommendations-internally-displaced-persons-statistics-iris.html)  

### World{.tabset }
 
```{r message=FALSE, warning=FALSE, output= FALSE}
lastyear <- 2021

``` 


```{r , child = 'ChildWorld.Rmd'}

```

### America{.tabset .tabset-pills}


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Americas"
```


```{r,  echo=FALSE}
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
# as.character(ctr$CountryAsylumName)
 
#  "Dominican Republic"                 "Costa Rica"                        
#  "El Salvador"                        "Guatemala"                         
#  "Honduras"                           "Mexico"                            
#  "Panama"                             "Canada"                            
#  "United States of America"           "Argentina"                         
#  "Brazil"                             "Chile"                             
# "Colombia"                           "Ecuador"                           
#  "Peru"                               "Venezuela (Bolivarian Republic of)"
``` 
 

```{r , child = 'ChildRegion.Rmd'}
```

#### Northern America{.tabset .tabset-pills}

##### Canada{.tabset  }

```{r Canada, message=FALSE, warning=FALSE}
thiscountry <- "Canada"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### USA{.tabset  }

```{r message=FALSE, warning=FALSE}
thiscountry <- "United States of America"
```


```{r , child = 'ChildCountry.Rmd'}
```

#### Central America{.tabset .tabset-pills}

##### Mexico{.tabset }

```{r Mexico, message=FALSE, warning=FALSE}
thiscountry <- "Mexico"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Guatemala{.tabset }

```{r Guatemala, message=FALSE, warning=FALSE}
thiscountry <- "Guatemala"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### El Salvador{.tabset }

```{r Salvador, message=FALSE, warning=FALSE}
thiscountry <- "El Salvador"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Honduras{.tabset }

```{r Honduras, message=FALSE, warning=FALSE}
thiscountry <- "Honduras"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Costa Rica{.tabset }

```{r CostaRica, message=FALSE, warning=FALSE}
thiscountry <- "Costa Rica"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Panama{.tabset }

```{r Panama, message=FALSE, warning=FALSE}
thiscountry <- "Panama"
```

```{r , child = 'ChildCountry.Rmd'}
```


#### Caribean{.tabset .tabset-pills}


##### Dominican Republic{.tabset }

```{r Dominican, message=FALSE, warning=FALSE}
thiscountry <- "Dominican Republic"
```

```{r , child = 'ChildCountry.Rmd'}
```


#### Southern America{.tabset .tabset-pills}

##### Argentina{.tabset }

```{r Argentina, message=FALSE, warning=FALSE}
thiscountry <- "Argentina"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Brazil{.tabset }

```{r Brazil, message=FALSE, warning=FALSE}
thiscountry <- "Brazil"
```


```{r , child = 'ChildCountry.Rmd'}
```




##### Chile{.tabset }

```{r Chile, message=FALSE, warning=FALSE}
thiscountry <- "Chile"
```


```{r , child = 'ChildCountry.Rmd'}
```



##### Colombia{.tabset }

```{r Colombia, message=FALSE, warning=FALSE}
thiscountry <- "Colombia"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Ecuador{.tabset }

```{r Ecuador, message=FALSE, warning=FALSE}
thiscountry <- "Ecuador"
```


```{r , child = 'ChildCountry.Rmd'}
```



##### Peru{.tabset }

```{r Peru, message=FALSE, warning=FALSE}
thiscountry <- "Peru"
```


```{r , child = 'ChildCountry.Rmd'}
```



##### Venezuela{.tabset  }

```{r Venezuela, message=FALSE, warning=FALSE}
thiscountry <- "Venezuela (Bolivarian Republic of)"
```

```{r , child = 'ChildCountry.Rmd'}
```


 
### Asia{.tabset .tabset-pills}

#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Asia"
```

```{r,  echo=FALSE}
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
#  "Australia"                  "Uzbekistan"                 "China"                     
#  "Cambodia"                   "Malaysia"                   "Myanmar"                   
#  "Philippines"                "Thailand"                   "Afghanistan"               
#  "Bangladesh"                 "India"                      "Iran (Islamic Republic of)"
#  "Pakistan"
 
``` 

```{r , child = 'ChildRegion.Rmd'}
```

#### East Asia and the Pacific{.tabset .tabset-pills}


##### Australia {.tabset}

```{r Australia, message=FALSE, warning=FALSE}
thiscountry <- "Australia"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### China {.tabset}

```{r China, message=FALSE, warning=FALSE}
thiscountry <- "China"
```

```{r , child = 'ChildCountry.Rmd'}
```

#### South Asia{.tabset .tabset-pills}

##### India{.tabset}

```{r India, message=FALSE, warning=FALSE}
thiscountry <- "India"
```

```{r , child = 'ChildCountry.Rmd'}
```


#### South East Asia{.tabset .tabset-pills}

##### Thailand{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Thailand"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Bangladesh{.tabset}

```{r Bangladesh, message=FALSE, warning=FALSE}
thiscountry <- "Bangladesh"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Myanmar{.tabset}

```{r Myanmar, message=FALSE, warning=FALSE}
thiscountry <- "Myanmar"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Philippines{.tabset}

```{r Philippines, message=FALSE, warning=FALSE}
thiscountry <- "Philippines"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Cambodia{.tabset}

```{r Cambodia, message=FALSE, warning=FALSE}
thiscountry <- "Cambodia"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Malaysia{.tabset}

```{r Malaysia, message=FALSE, warning=FALSE}
thiscountry <- "Malaysia"
```

```{r , child = 'ChildCountry.Rmd'}
```

#### South West Asia{.tabset .tabset-pills}

##### Iran{.tabset}

```{r Iran, message=FALSE, warning=FALSE}
thiscountry <- "Iran (Islamic Republic of)"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Pakistan {.tabset}

```{r Pakistan, message=FALSE, warning=FALSE}
thiscountry <- "Pakistan"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Afghanistan {.tabset}

```{r Afghanistan, message=FALSE, warning=FALSE}
thiscountry <- "Afghanistan"
```

```{r , child = 'ChildCountry.Rmd'}
```


### Europe{.tabset .tabset-pills}

#### Regional Overview{.tabset}


```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Europe"
```

```{r,  echo=FALSE}

ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
#  [1] "Russian Federation"                                  
#  [2] "Ukraine"                                             
#  [3] "Estonia"                                             
#  [4] "Latvia"                                              
#  [5] "Sweden"                                              
#  [6] "United Kingdom of Great Britain and Northern Ireland"
#  [7] "Bosnia and Herzegovina"                              
#  [8] "Greece"                                              
#  [9] "Italy"                                               
# [10] "Serbia"                                              
# [11] "Spain"                                               
# [12] "Azerbaijan"                                          
# [13] "Georgia"                                             
# [14] "Turkey"                                              
# [15] "Austria"                                             
# [16] "Belgium"                                             
# [17] "Germany"                                             
# [18] "Netherlands"                                         
# [19] "Switzerland"                                         
# [20] "France"                                              
# [21] "Norway" 

```

```{r , child = 'ChildRegion.Rmd'}
```

#### Western Europe{.tabset .tabset-pills}

##### UK {.tabset}

```{r UK, message=FALSE, warning=FALSE}
thiscountry <- "United Kingdom of Great Britain and Northern Ireland"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Germany{.tabset}

```{r Germany, message=FALSE, warning=FALSE}
thiscountry <- "Germany"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### France{.tabset}

```{r France, message=FALSE, warning=FALSE}
thiscountry <- "France"
```

```{r , child = 'ChildCountry.Rmd'}
```



#### Northern Europe{.tabset .tabset-pills}


##### Latvia{.tabset}

```{r Latvia, message=FALSE, warning=FALSE}
thiscountry <- "Latvia"
```

```{r , child = 'ChildCountry.Rmd'}
```



##### Estonia{.tabset}

```{r Estonia, message=FALSE, warning=FALSE}
thiscountry <- "Estonia"
```

```{r , child = 'ChildCountry.Rmd'}
```



##### Norway{.tabset}

```{r Norway, message=FALSE, warning=FALSE}
thiscountry <- "Norway"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Sweden{.tabset}

```{r Sweden, message=FALSE, warning=FALSE}
thiscountry <- "Sweden"
```

```{r , child = 'ChildCountry.Rmd'}
```


#### Southern Europe{.tabset .tabset-pills}

##### Italy{.tabset}

```{r Italy, message=FALSE, warning=FALSE}
thiscountry <- "Italy"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Spain{.tabset}

```{r Spain, message=FALSE, warning=FALSE}
thiscountry <- "Spain"
```

```{r , child = 'ChildCountry.Rmd'}
```

##### Greece{.tabset}

```{r Greece, message=FALSE, warning=FALSE}
thiscountry <- "Greece"
```

```{r , child = 'ChildCountry.Rmd'}
```



#### Eastern Europe{.tabset .tabset-pills}


##### Turkey{.tabset}

```{r Turkey, message=FALSE, warning=FALSE}
thiscountry <- "Turkey"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Georgia{.tabset}

```{r Georgia, message=FALSE, warning=FALSE}
thiscountry <- "Georgia"
```

```{r , child = 'ChildCountry.Rmd'}
```


##### Russian Federation{.tabset}

```{r Russian, message=FALSE, warning=FALSE}
thiscountry <- "Russian Federation"
```

```{r , child = 'ChildCountry.Rmd'}
```




### MENA{.tabset .tabset-pills} 


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "MENA"
```

```{r,  echo=FALSE}

ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)

 # [1] "Algeria"              "Egypt"                "Libya"                "Mauritania"          
 # [5] "Iraq"                 "Jordan"               "Kuwait"               "Lebanon"             
 # [9] "Saudi Arabia"         "Syrian Arab Republic" "Yemen" 
```

```{r , child = 'ChildRegion.Rmd'}
```

#### Northern Africa{.tabset .tabset-pills}


##### Algeria{.tabset}

```{r Algeria, message=FALSE, warning=FALSE}
thiscountry <- "Algeria"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Egypt{.tabset}

```{r Egypt, message=FALSE, warning=FALSE}
thiscountry <- "Egypt"
```


```{r , child = 'ChildCountry.Rmd'}
```

#### Middle East{.tabset .tabset-pills}


##### Jordan{.tabset}

```{r Jordan, message=FALSE, warning=FALSE}
thiscountry <- "Jordan"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Syria {.tabset}

```{r Syria, message=FALSE, warning=FALSE}
thiscountry <- "Syrian Arab Republic"
```


```{r , child = 'ChildCountry.Rmd'}
``` 



### Western Africa{.tabset .tabset-pills}


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "WestAfrica"
```


```{r , child = 'ChildRegion.Rmd'}
```

#### Central Africa {.tabset .tabset-pills}

##### Cameroon{.tabset}

```{r Cameroon, message=FALSE, warning=FALSE}
thiscountry <- "Cameroon"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Chad{.tabset}

```{r Chad, message=FALSE, warning=FALSE}
thiscountry <- "Chad"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Central African Republic{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Central African Republic"
```


```{r , child = 'ChildCountry.Rmd'}
```



#### West Africa{.tabset .tabset-pills}

##### Burkina Faso{.tabset}

```{r Burkina, message=FALSE, warning=FALSE}
thiscountry <- "Burkina Faso"
```


```{r , child = 'ChildCountry.Rmd'}
```




##### Mali{.tabset}

```{r Mali, message=FALSE, warning=FALSE}
thiscountry <- "Mali"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Niger{.tabset}

```{r Niger, message=FALSE, warning=FALSE}
thiscountry <- "Niger"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Nigeria{.tabset}

```{r Nigeria, message=FALSE, warning=FALSE}
thiscountry <- "Nigeria"
```


```{r , child = 'ChildCountry.Rmd'}
```





### Eastern Africa{.tabset .tabset-pills}


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "EastAfrica"
```

```{r,  echo=FALSE}

ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
```


```{r , child = 'ChildRegion.Rmd'}
```

####  Great Lakes {.tabset .tabset-pills}
 

##### Burundi{.tabset}

```{r Burundi, message=FALSE, warning=FALSE}
thiscountry <- "Burundi"
```


```{r , child = 'ChildCountry.Rmd'}
```



##### Rwanda{.tabset}

```{r Rwanda, message=FALSE, warning=FALSE}
thiscountry <- "Rwanda"
```

####  East and Horn {.tabset .tabset-pills}

##### Ethiopia{.tabset}

```{r Ethiopia, message=FALSE, warning=FALSE}
thiscountry <- "Ethiopia"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Kenya{.tabset}

```{r Kenya, message=FALSE, warning=FALSE}
thiscountry <- "Kenya"
```


```{r , child = 'ChildCountry.Rmd'}
```
 

##### Somalia{.tabset}

```{r Somalia, message=FALSE, warning=FALSE}
thiscountry <- "Somalia"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### South Sudan{.tabset}

```{r SouthSudan, message=FALSE, warning=FALSE}
thiscountry <- "South Sudan"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Uganda{.tabset}

```{r Uganda, message=FALSE, warning=FALSE}
thiscountry <- "Uganda"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Tanzania{.tabset}

```{r Tanzania, message=FALSE, warning=FALSE}
thiscountry <- "United Republic of Tanzania"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Zambia{.tabset}

```{r  Zambia, message=FALSE, warning=FALSE}
thiscountry <- "Zambia"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Sudan{.tabset}

```{r Sudan, message=FALSE, warning=FALSE}
thiscountry <- "Sudan"
```


```{r , child = 'ChildCountry.Rmd'}
```
        

### Southern Africa{.tabset .tabset-pills}


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "SouthAfrica"
```

```{r,  echo=FALSE}

ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
```


```{r , child = 'ChildRegion.Rmd'}
```

#### Southern Africa{.tabset .tabset-pills}

##### South Africa{.tabset}

```{r SouthAfrica, message=FALSE, warning=FALSE}
thiscountry <- "South Africa"
```


```{r , child = 'ChildCountry.Rmd'}
```


##### Malawi{.tabset}

```{r Malawi, message=FALSE, warning=FALSE}
thiscountry <- "Malawi"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Mozambique{.tabset}

```{r Mozambique, message=FALSE, warning=FALSE}
thiscountry <- "Mozambique"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Angola{.tabset}

```{r Angola, message=FALSE, warning=FALSE}
thiscountry <- "Angola"
```


```{r , child = 'ChildCountry.Rmd'}
```

#### Central Africa{.tabset .tabset-pills}

##### Democratic Republic of the Congo{.tabset}

```{r DRC, message=FALSE, warning=FALSE}
thiscountry <- "Democratic Republic of the Congo"
```


```{r , child = 'ChildCountry.Rmd'}
```

##### Congo{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Congo"
```


```{r , child = 'ChildCountry.Rmd'}
```
   

## {-}