---
title:  
output: html_document
---
 

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message=FALSE, 
  warning=FALSE,
  echo = FALSE
)

library(tidyverse)
## Loading the stat tables
end_year_population_totals <- unhcrdatapackage::end_year_population_totals
reference <- unhcrdatapackage::reference
end_year_population_totals_long <- unhcrdatapackage::end_year_population_totals_long
end_year_population_totals_long.asy <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))

end_year_population_totals_long.ori <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryOriginCode" = "iso_3"))

demographics <- unhcrdatapackage::demographics
asylum_applications <- unhcrdatapackage::asylum_applications
asylum_decisions <- unhcrdatapackage::asylum_decisions
asylum_decisions_long <- unhcrdatapackage::asylum_decisions_long

solutions <- unhcrdatapackage::solutions
solutions_long <- unhcrdatapackage::solutions_long
solutions_long.asy <- dplyr::left_join( x=  solutions_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))
```

## Country Statistical Focus{.tabset .tabset-pills}

### Intro

Country Focus: __6 key questions for each country addressed through predefined static charts that can easily be copied as an image and embedded in reports, fact-sheets or presentations__ to accompany a narrative.

The charts includes the 6 following topics:

 1. Evolution over time of the different __Categories__ of forcibly displaced population?
 
 2. Evolution of the different Country of __Origin__ of population in need of international protection 
 
 3. What is the __demographics__ profile of population in need of international protection in the country in relation with the host population?
 
 4. Evolution of Country seen as  __source__ country?
 
 5. What are the trends in term of __solutions__ in this  Country?
 
 6. What is the asylum __processing__ capacity in relation with the demand?
 
```{r message=FALSE, warning=FALSE, output= FALSE}
lastyear <- 2021
thisbureau <- "Americas"
``` 

### America{.tabset .tabset-pills}

#### Argentina

```{r message=FALSE, warning=FALSE}
thiscountry <- "Argentina"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Brazil

```{r message=FALSE, warning=FALSE}
thiscountry <- "Brazil"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Canada

```{r message=FALSE, warning=FALSE}
thiscountry <- "Canada"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Chile

```{r message=FALSE, warning=FALSE}
thiscountry <- "Chile"
```


```{r , child = 'CountryChild.Rmd'}
```



#### Colombia

```{r message=FALSE, warning=FALSE}
thiscountry <- "Colombia"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Ecuador

```{r message=FALSE, warning=FALSE}
thiscountry <- "Ecuador"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Mexico

```{r message=FALSE, warning=FALSE}
thiscountry <- "Mexico"
```

```{r , child = 'CountryChild.Rmd'}
```


#### Peru

```{r message=FALSE, warning=FALSE}
thiscountry <- "Peru"
```


```{r , child = 'CountryChild.Rmd'}
```



#### United States of America

```{r message=FALSE, warning=FALSE}
thiscountry <- "United States of America"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Venezuela

```{r message=FALSE, warning=FALSE}
thiscountry <- "Venezuela (Bolivarian Republic of)"
```

```{r , child = 'CountryChild.Rmd'}
```


#### Panama

```{r message=FALSE, warning=FALSE}
thiscountry <- "Panama"
```

```{r , child = 'CountryChild.Rmd'}
```

### Asia

We show the data in this tab.

```{r}
head(mtcars)
```

### Europe{.tabset .tabset-pills}

#### Country A
```{r}
head(mtcars)
```
Sentences.

#### Country B {.active}

We show the data in this tab.

```{r}
head(mtcars)
```


### Northern Africa & Middle-East{.tabset .tabset-pills} 

#### Country A
```{r}
head(mtcars)
```
Sentences.

#### Country B {.active}

We show the data in this tab.

```{r}
head(mtcars)
```


### Western Africa{.tabset .tabset-pills}
#### Country A
```{r}
head(mtcars)
```
Sentences.

#### Country B {.active}

We show the data in this tab.

```{r}
head(mtcars)
```


### Eastern Africa{.tabset .tabset-pills}
```{r}
head(mtcars)
```

### Southern Africa{.tabset .tabset-pills}
```{r}
head(mtcars)
```

 

## {-}

Fee Free to share your comments through [issues ticket](https://github.com/unhcr/unhcrdatapackage/issues/new)
