---
title:
output: 
  html_document: 
    theme: yeti
    includes:
      after_body: footer.html
---
 

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message=FALSE, 
  warning=FALSE,
  echo = FALSE
)

library(tidyverse)
## Loading the stat tables
end_year_population_totals <- unhcrdatapackage::end_year_population_totals
reference <- unhcrdatapackage::reference
end_year_population_totals_long <- unhcrdatapackage::end_year_population_totals_long
end_year_population_totals_long.asy <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))

end_year_population_totals_long.ori <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryOriginCode" = "iso_3"))

demographics <- unhcrdatapackage::demographics
asylum_applications <- unhcrdatapackage::asylum_applications
asylum_decisions <- unhcrdatapackage::asylum_decisions
asylum_decisions_long <- unhcrdatapackage::asylum_decisions_long

solutions <- unhcrdatapackage::solutions
solutions_long <- unhcrdatapackage::solutions_long
solutions_long.asy <- dplyr::left_join( x=  solutions_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))
```

## Country Statistical Focus{.tabset .tabset-pills}

### Intro

Country Focus: __6 key questions for each country addressed through predefined static charts__  

Charts can easily be copied as an image, or adjusted (for instance changing the title to __support a data story__) and embedded in reports, fact-sheets or presentations to accompany a narrative.

The charts includes the 6 following topics:

 1. Evolution over time of the different __Categories__ of [Forcibly Displaced People](https://www.unhcr.org/refugee-statistics/insights/explainers/forcibly-displaced-pocs.html)?
 
 2. Evolution of the different Country of __Origin__ of population in need of international protection 
 
 3. What is the __demographics__ profile of population in need of international protection in the country in relation with the host population?
 
 4. What are the trends in term of __solutions__ in this  Country?
 
 5. What is the asylum __processing__ capacity in relation with the demand?
 
 6. if relevant, evolution of the Country seen as a displacement  __source__ country?
 
```{r message=FALSE, warning=FALSE, output= FALSE}
lastyear <- 2021
``` 

### America{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Americas"
``` 

#### Argentina{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Argentina"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Brazil{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Brazil"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Canada{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Canada"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Chile{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Chile"
```


```{r , child = 'CountryChild.Rmd'}
```



#### Colombia{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Colombia"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Ecuador{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Ecuador"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Mexico{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Mexico"
```

```{r , child = 'CountryChild.Rmd'}
```


#### Peru{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Peru"
```


```{r , child = 'CountryChild.Rmd'}
```



#### USA{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "United States of America"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Venezuela{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Venezuela (Bolivarian Republic of)"
```

```{r , child = 'CountryChild.Rmd'}
```


#### Panama{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Panama"
```

```{r , child = 'CountryChild.Rmd'}
```

### Asia{.tabset .tabset-pills}


```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Asia"
``` 

To come soon...
 

### Europe{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Europe"
```

To come soon...

### MENA{.tabset .tabset-pills} 

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "MENA"
```
To come soon...
 

### Western Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "WestAfrica"
```
To come soon... 

### Eastern Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "EastAfrica"
```
To come soon... 

### Southern Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "SouthAfrica"
```
To come soon... 

## {-}
