---
title:
output: 
  html_document: 
    theme: yeti
    includes:
      before_body: header.html
      after_body: footer.html
---
 

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message=FALSE, 
  warning=FALSE,
  echo = FALSE
)

library(tidyverse)
## Loading the stat tables
end_year_population_totals <- unhcrdatapackage::end_year_population_totals
reference <- unhcrdatapackage::reference
end_year_population_totals_long <- unhcrdatapackage::end_year_population_totals_long
end_year_population_totals_long.asy <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))

end_year_population_totals_long.ori <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryOriginCode" = "iso_3"))

demographics <- unhcrdatapackage::demographics
asylum_applications <- unhcrdatapackage::asylum_applications
asylum_decisions <- unhcrdatapackage::asylum_decisions
asylum_decisions_long <- unhcrdatapackage::asylum_decisions_long

solutions_long.asy <- dplyr::left_join( x=  unhcrdatapackage::solutions_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))

selectedctr <- data <- dplyr::left_join( x= unhcrdatapackage::end_year_population_totals_long, 
                                                     y= unhcrdatapackage::reference, 
                                                     by = c("CountryAsylumCode" = "iso_3"))  %>%
  filter( Year == 2021) %>%
  group_by( UNHCRBureau, SUBREGION, CountryAsylumName) %>%
  summarise(Value2 = sum(Value) ) %>%
 filter( Value2 > 50000) 
```

## Forcible Displacement Statistics{.tabset .tabset-pills}

### Intro
<div class="container">
<div class="jumbotron">
<h1 class="title"><span style="color: #0072BC;">__Seven Key Questions__</span></h1>

     ... addressed through predefined crafted static charts
</div>
</div> 

  1. How the different __Categories__ of Forcibly Displaced People are evolving over time? 
 
  2. What is the main Country of __Origin__ of population in need of international protection 
 
  3. What are the __Demographics__ profile of Forcibly Displaced People in relation with the host population? 
 
  4. What are the trends in term of __Solutions__ in this  Country? 
 
  5. How is the asylum __Processing__ capacity in relation with the demand? 
 

  6. What is the share of in need person of international protection versus regular __Migration__? 
  
  7. If happening, what is the evolution of a country as a displacement __Source__? 

***
Charts can easily be copied as an image as is, or adjusted using a [reproducible source code in R statistical language](https://unhcr-americas.github.io/reproducibility). 

For instance, you can change the title from a _key question_ to a _key message_ to __support data storytelling__.

***
The resulting charts can be embedded in reports, fact-sheets, social media or presentations to accompany a narrative / campaign. More information on [Forcibly Displaced People is available here](https://www.unhcr.org/refugee-statistics/insights/explainers/forcibly-displaced-pocs.html)

 
```{r message=FALSE, warning=FALSE, output= FALSE}
lastyear <- 2021
``` 

### America{.tabset .tabset-pills}


#### Regional Overview{.tabset}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Americas"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
# as.character(ctr$CountryAsylumName)
 
#  [1] "Dominican Republic"                 "Costa Rica"                        
#  [3] "El Salvador"                        "Guatemala"                         
#  [5] "Honduras"                           "Mexico"                            
#  [7] "Panama"                             "Canada"                            
#  [9] "United States of America"           "Argentina"                         
# [11] "Brazil"                             "Chile"                             
# [13] "Colombia"                           "Ecuador"                           
# [15] "Peru"                               "Venezuela (Bolivarian Republic of)"
``` 
 

```{r , child = 'RegionChild.Rmd'}
```

#### Northern America{.tabset}

##### Canada{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Canada"
```


```{r , child = 'CountryChildl1.Rmd'}
```


##### USA{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "United States of America"
```


```{r , child = 'CountryChildl1.Rmd'}
```



#### Meso America{.tabset}

##### Mexico{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Mexico"
```

```{r , child = 'CountryChildl1.Rmd'}
```

##### Guatemala{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Guatemala"
```

```{r , child = 'CountryChildl1.Rmd'}
```


##### El Salvador{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "El Salvador"
```

```{r , child = 'CountryChildl1.Rmd'}
```


##### Honduras{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Honduras"
```

```{r , child = 'CountryChildl1.Rmd'}
```

##### Costa Rica{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Costa Rica"
```

```{r , child = 'CountryChildl1.Rmd'}
```


##### Panama{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Panama"
```

```{r , child = 'CountryChildl1.Rmd'}
```


#### Caribean{.tabset}


##### Dominican Republic{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Dominican Republic"
```

```{r , child = 'CountryChildl1.Rmd'}
```


#### Southern America{.tabset}

##### Argentina{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Argentina"
```

```{r , child = 'CountryChildl1.Rmd'}
```

##### Brazil{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Brazil"
```


```{r , child = 'CountryChildl1.Rmd'}
```




##### Chile{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Chile"
```


```{r , child = 'CountryChildl1.Rmd'}
```



##### Colombia{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Colombia"
```


```{r , child = 'CountryChildl1.Rmd'}
```


##### Ecuador{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Ecuador"
```


```{r , child = 'CountryChildl1.Rmd'}
```



##### Peru{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Peru"
```


```{r , child = 'CountryChildl1.Rmd'}
```



##### Venezuela{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Venezuela (Bolivarian Republic of)"
```

```{r , child = 'CountryChildl1.Rmd'}
```



### Asia{.tabset .tabset-pills}


```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Asia"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
#  [1] "Australia"                  "Uzbekistan"                 "China"                     
#  [4] "Cambodia"                   "Malaysia"                   "Myanmar"                   
#  [7] "Philippines"                "Thailand"                   "Afghanistan"               
# [10] "Bangladesh"                 "India"                      "Iran (Islamic Republic of)"
# [13] "Pakistan"
 
``` 


#### Australia {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Australia"
```

```{r , child = 'CountryChild.Rmd'}
```

#### China {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "China"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Iran{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Iran (Islamic Republic of)"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Pakistan {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Pakistan"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Afghanistan {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Afghanistan"
```

```{r , child = 'CountryChild.Rmd'}
```

### Europe{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "Europe"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
#  [1] "Russian Federation"                                  
#  [2] "Ukraine"                                             
#  [3] "Estonia"                                             
#  [4] "Latvia"                                              
#  [5] "Sweden"                                              
#  [6] "United Kingdom of Great Britain and Northern Ireland"
#  [7] "Bosnia and Herzegovina"                              
#  [8] "Greece"                                              
#  [9] "Italy"                                               
# [10] "Serbia"                                              
# [11] "Spain"                                               
# [12] "Azerbaijan"                                          
# [13] "Georgia"                                             
# [14] "Turkey"                                              
# [15] "Austria"                                             
# [16] "Belgium"                                             
# [17] "Germany"                                             
# [18] "Netherlands"                                         
# [19] "Switzerland"                                         
# [20] "France"                                              
# [21] "Norway" 

```



#### UK {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "United Kingdom of Great Britain and Northern Ireland"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Germany{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Germany"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Russian Federation{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Russian Federation"
```

```{r , child = 'CountryChild.Rmd'}
```

#### France{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "France"
```

```{r , child = 'CountryChild.Rmd'}
```

#### Norway{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Norway"
```

```{r , child = 'CountryChild.Rmd'}
```



### MENA{.tabset .tabset-pills} 

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "MENA"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)

 # [1] "Algeria"              "Egypt"                "Libya"                "Mauritania"          
 # [5] "Iraq"                 "Jordan"               "Kuwait"               "Lebanon"             
 # [9] "Saudi Arabia"         "Syrian Arab Republic" "Yemen" 
```


#### Algeria{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Algeria"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Egypt{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Egypt"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Jordan{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Jordan"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Syria {.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Syrian Arab Republic"
```


```{r , child = 'CountryChild.Rmd'}
``` 

### Western Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "WestAfrica"
```

#### Cameroon{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Cameroon"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Central African Republic{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Central African Republic"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Chad{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Chad"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Burkina Faso{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Burkina Faso"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Côte d'Ivoire{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Côte d'Ivoire"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Mali{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Mali"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Niger{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Niger"
```


```{r , child = 'CountryChild.Rmd'}
```


#### Nigeria{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Nigeria"
```


```{r , child = 'CountryChild.Rmd'}
```




### Eastern Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "EastAfrica"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
```
 

#### Burundi{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Burundi"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Ethiopia{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Ethiopia"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Kenya{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Kenya"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Rwanda{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Rwanda"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Somalia{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Somalia"
```


```{r , child = 'CountryChild.Rmd'}
```
#### South Sudan{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "South Sudan"
```


```{r , child = 'CountryChild.Rmd'}
```
#### Uganda{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Uganda"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Tanzania{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "United Republic of Tanzania"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Zambia{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Zambia"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Sudan{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Sudan"
```


```{r , child = 'CountryChild.Rmd'}
```
         
 

### Southern Africa{.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE, output= FALSE}
thisbureau <- "SouthAfrica"
ctr <- selectedctr  %>%
  filter( UNHCRBureau == thisbureau) %>%
  select(CountryAsylumName)
#as.character(ctr$CountryAsylumName)
```

#### Malawi{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Malawi"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Mozambique{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Mozambique"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Angola{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Angola"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Congo{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Congo"
```


```{r , child = 'CountryChild.Rmd'}
```

#### Democratic Republic of the Congo{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "Democratic Republic of the Congo"
```


```{r , child = 'CountryChild.Rmd'}
```

#### South Africa{.tabset}

```{r message=FALSE, warning=FALSE}
thiscountry <- "South Africa"
```


```{r , child = 'CountryChild.Rmd'}
```

   

## {-}